### 2019-10-18 Manuscript/main.tex
Project report

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Diaz Essay
% LaTeX Template
% Version 2.0 (13/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@LaTeXTemplates.com)
% Nicolas Diaz (nsdiaz@uc.cl)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{diazessay} % Font size (can be 10pt, 11pt or 12pt)

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\title{\textbf{Course: Física Teórica I (CDP7600)} \\[0.2cm] {\Large \textbf{Project}: \hspace{0.2cm}
\textit{Fibration building blocks of information-processing networks}
}}% Title and subtitle

\author{\textbf{Higor da S. Monteiro} \\ \textit{Universidade Federal do Ceará}} % Author and institution

\date{\today} % Date, use \date{} for no date

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title section

%----------------------------------------------------------------------------------------
%	ABSTRACT AND KEYWORDS
%----------------------------------------------------------------------------------------

%\renewcommand{\abstractname}{Summary} % Uncomment to change the name of the abstract to something else

\begin{abstract}
	Fibration building blocks of a network represent the sets of nodes that are symmetric with respect to information processing. Here, we have reproduced important results concerning the identification and classification of the fibration building blocks of directed networks, constructed from real network data. More specifically, using the transcriptional regulatory network data of the \textit{Escherichia Coli} bacteria, we quantify the groups of network nodes that synchronously process equivalent information and then we classify each fiber based on its specific topological features. This way, in order to consistently present the obtained results, in this report we first give a brief description of the theory concerning the graph fibration morphism and its main definitions related to information flow symmetries. Next, we detail the methods adopted to correctly identify and classify the network fibers. More specifically, to establish an optimal framework, I show the implementation details of the Minimal Balanced Coloring algorithm used to find the corresponding fibers in the network, presenting a slightly improvement for the algorithm complexity. At last, showing the proper methods for data preparation, I describe the results obtained concerning the fiber statistics for the specific case of the \textit{Escherichia Coli} regulatory network, to properly compare with the recent results presented at \textit{Morone et. al.} (2019).
\end{abstract}

\hspace*{3.6mm}\textit{Keywords:} Graph Morphism; Biological Networks; Information Processing, Fibration, lectus % Keywords

\vspace{30pt} % Vertical whitespace between the abstract and first section

%----------------------------------------------------------------------------------------
%	ESSAY BODY
%----------------------------------------------------------------------------------------

\section{Brief Introduction}

This statement requires citation \cite{fibration2019}; this one does too \cite{Cardon1982} \cite{Boldi2006} \cite{Tarjan1987} \cite{Stewart2006}. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean dictum lacus sem, ut varius ante dignissim ac. Sed a mi quis lectus feugiat aliquam. Nunc sed vulputate velit. Sed commodo metus vel felis semper, quis rutrum odio vulputate. Donec a elit porttitor, facilisis nisl sit amet, dignissim arcu. Vivamus accumsan pellentesque nulla at euismod. Duis porta rutrum sem, eu facilisis mi varius sed. Suspendisse potenti. Mauris rhoncus neque nisi, ut laoreet augue pretium luctus. Vestibulum sit amet luctus sem, luctus ultrices leo. Aenean vitae sem leo.

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.4]{Figures/ex1.png}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.4]{Figures/ex2.png}
\end{figure}

Nullam semper quam at ante convallis posuere. Ut faucibus tellus ac massa luctus consectetur. Nulla pellentesque tortor et aliquam vehicula. Maecenas imperdiet euismod enim ut pharetra. Suspendisse pulvinar sapien vitae placerat pellentesque. Nulla facilisi. Aenean vitae nunc venenatis, vehicula neque in, congue ligula.

Pellentesque quis neque fringilla, varius ligula quis, malesuada dolor. Aenean malesuada urna porta, condimentum nisl sed, scelerisque nisi. Suspendisse ac orci quis massa porta dignissim. Morbi sollicitudin, felis eget tristique laoreet, ante lacus pretium lacus, nec ornare sem lorem a velit. Pellentesque eu erat congue, ullamcorper ante ut, tristique turpis. Nam sodales mi sed nisl tincidunt vestibulum. Interdum et malesuada fames ac ante ipsum primis in faucibus.

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.4]{Figures/ex1input.png}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.4]{Figures/ex2input.png}
\end{figure}

%------------------------------------------------

\section{\textit{Minimal Balanced Coloring }Algorithm}

\subsection{Algorithm description}

For the proper identification of the fibers on the network we have to construct a graph partition that is equivalent to a coarse grain of the network with respect to the information flow passing through each node.

Aliquam fringilla non diam sed varius. Suspendisse tellus felis, hendrerit non bibendum ut, adipiscing vitae diam. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Nulla lobortis purus eget nisl scelerisque, commodo rhoncus lacus porta. Vestibulum vitae turpis tincidunt, varius dolor in, dictum lectus. Aenean ac ornare augue, ac facilisis purus. Sed leo lorem, molestie sit amet fermentum id, suscipit ut sem. Vestibulum orci arcu, vehicula sed tortor id, ornare dapibus lorem. Praesent aliquet iaculis lacus nec fermentum. Morbi eleifend blandit dolor, pharetra hendrerit neque ornare vel. Nulla ornare, nisl eget imperdiet ornare, libero enim interdum mi, ut lobortis quam velit bibendum nibh.

\begin{itemize}
	\item First bullet point item
	\item Second bullet point item
	\item Third bullet point item
\end{itemize}

\subsection{Data preparation and algorithm implementation}

Morbi tempor congue porta. Proin semper, leo vitae faucibus dictum, metus mauris lacinia lorem, ac congue leo felis eu turpis. Sed nec nunc pellentesque, gravida eros at, porttitor ipsum. Praesent consequat urna a lacus lobortis ultrices eget ac metus. In tempus hendrerit rhoncus. Mauris dignissim turpis id sollicitudin lacinia. Praesent libero tellus, fringilla nec ullamcorper at, ultrices id nulla. Phasellus placerat a tellus a malesuada.

\begin{enumerate}
	\item First numbered list item
	\item Second numbered list item
\end{enumerate}

%------------------------------------------------

\section*{Results}

Fusce in nibh augue. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. In dictum accumsan sapien, ut hendrerit nisi. Phasellus ut nulla mauris. Phasellus sagittis nec odio sed posuere. Vestibulum porttitor dolor quis suscipit bibendum. Mauris risus lectus, cursus vitae hendrerit posuere, congue ac est. Suspendisse commodo eu eros non cursus. Mauris ultrices venenatis dolor, sed aliquet odio tempor pellentesque. Duis ultricies, mauris id lobortis vulputate, tellus turpis eleifend elit, in gravida leo tortor ultricies est. Maecenas vitae ipsum at dui sodales condimentum a quis dui. Nam mi sapien, lobortis ac blandit eget, dignissim quis nunc.

Donec luctus tincidunt mauris, non ultrices ligula aliquam id. Sed varius, magna a faucibus congue, arcu tellus pellentesque nisl, vel laoreet magna eros et magna. Vivamus lobortis elit eu dignissim ultrices. Fusce erat nulla, ornare at dolor quis, rhoncus venenatis velit. Donec sed elit mi. Sed semper tellus a convallis viverra. Maecenas mi lorem, placerat sit amet sem quis, adipiscing tincidunt turpis. Cras a urna et tellus dictum eleifend. Fusce dignissim lectus risus, in bibendum tortor lacinia interdum.

\begin{table}[h] % [h] forces the table to be output where it is defined in the code (it suppresses floating)
	\caption{Example table.}
	\centering
	\begin{tabular}{l l r}
		\toprule
		\multicolumn{2}{c}{Name} \\
		\cmidrule(r){1-2}
		First Name & Last Name & Grade \\
		\midrule
		John & Doe & $7.5$ \\
		Richard & Miles & $5$ \\
		\bottomrule
	\end{tabular}
\end{table}

Fusce eleifend porttitor arcu, id accumsan elit pharetra eget. Mauris luctus velit sit amet est sodales rhoncus. Donec cursus suscipit justo, sed tristique ipsum fermentum nec. Ut tortor ex, ullamcorper varius congue in, efficitur a tellus. Vivamus ut rutrum nisi. Phasellus sit amet enim efficitur, aliquam nulla id, lacinia mauris. Quisque viverra libero ac magna maximus efficitur. Interdum et malesuada fames ac ante ipsum primis in faucibus. Vestibulum mollis eros in tellus fermentum, vitae tristique justo finibus. Sed quis vehicula nibh. Etiam nulla justo, pellentesque id sapien at, semper aliquam arcu. Integer at commodo arcu. Quisque dapibus ut lacus eget vulputate.

\section{Conclusion}

Nullam semper quam at ante convallis posuere. Ut faucibus tellus ac massa luctus consectetur. Nulla pellentesque tortor et aliquam vehicula. Maecenas imperdiet euismod enim ut pharetra. Suspendisse pulvinar sapien vitae placerat pellentesque. Nulla facilisi. Aenean vitae nunc venenatis, vehicula neque in, congue ligula.

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\bibliographystyle{unsrt}

\bibliography{sample.bib}

%----------------------------------------------------------------------------------------

\end{document}

### 2019-10-20 Code/RefineToFiber.c
refinement

@@ -25,21 +25,76 @@
 #include <string.h>
 #include <math.h>
 #include <gsl/gsl_eigen.h>
-#include "utilsforfiber.h"   	// Personal module containing helpful functions to handle with network data and other common operations.
-#define SEQSIZE 500     	// It's possible that the size of the string sequences should be larger for larger networks.
+#include "utilsforfiber.h"   // Personal module containing helpful functions to handle with network data and other common operations.
 
-struct QueueOfBlocks
+int intersection_edges(Graph* graph, int node, BLOCK* Set)
 {
-    int block_index;
-    BLOCK* block;
-    struct QueueOfBlocks* next;
-};
-typedef struct QueueOfBlocks QBLOCK;
+	int i, check;	
+	NodeAdj* Node = graph->array[node].head_in;
+	BLOCK* SetHead = Set->head;
+
+	int n_in = 0;
+	while(Node)
+	{
+		check = doublycheck_element(SetHead, Node->neighbor);
+		if(check==1) n_in++;
+		Node = Node->next;
+	}
+	return n_in;	
+}
+
+void SPLIT(PART** partition, BLOCK* Set, Graph* graph, int N, QBLOCK** head, QBLOCK** tail)
+{	
+	PART* subpart1 = NULL;
+	PART* subpart2 = NULL;
+	PART* temp = partition;
+	BLOCK* tempblock = NULL;	
+	DoublyLinkNode* tempdoublylist;
+	int* nedges = (int*)malloc(N*sizeof(int));
+
+	/*	Given the 'Set' block, now we select all the blocks in the partition that have at 
+		least one inward connection coming from 'Set'. */
+	
+	// 'subpart' will contains all the blocks that have nonzero	pointed nodes from 'Set'.
+	while(temp)
+	{
+		tempdoublylist = temp->block->head;
+		while(tempdoublylist)
+		{
+			int node = tempdoublylist->data;
+			int n_in = intersection_edges(graph, node, Set);
+			nedges[node] = n_in;
+			if(n_in>0) { push_block(&subpart1, temp->block); break; }
+			tempdoublylist = tempdoublylist->next;
+		}
+		temp = temp->next;
+	}
+	
+	temp = subpart1;
+	while(temp) // for each block to be splitted.
+	{
+		tempdoublylist = temp->block->head;
+		while(tempdoublylist)	// for each node in block.
+		{
+			int node = tempdoublylist->data;			
[…]

### 2019-10-20 Code/structforfiber.h

@@ -1,0 +1,66 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <math.h>
+
+// Define a graph containing 'size' nodes
+struct Graph
+{
+	// each node has its adjancency list
+	int size;
+	struct adjList* array;
+};
+typedef struct Graph Graph;
+
+struct adjList
+{
+	struct NodeAdj* head_in;
+    struct NodeAdj* head_out;
+};
+typedef struct adjList AdjList;
+
+// Structure to define the adjacency list of a node
+struct NodeAdj
+{
+	int neighbor;
+    int regulator;
+	struct NodeAdj* next;
+};
+typedef struct NodeAdj NodeAdj;
+
+struct neigh_vector
+{
+	int neigh;
+	int color;
+};
+typedef struct neigh_vector neigh_vector;
+
+struct stack
+{
+	int extn;
+	int node_ID;
+	struct stack *next;
+};
+typedef struct stack Stack;
+
+struct DoublyLinkNode
+{
+    int data;
+    struct DoublyLinkNode* prev;
+    struct DoublyLinkNode* next;
+};
+typedef struct DoublyLinkNode DoublyLinkNode;
+
+struct Block
+{
+    int size;
+    DoublyLinkNode* head;   // The doubly linked list of the block containing the elements on it.
+};
+typedef struct Block BLOCK;
+
+struct QueueOfBlocks
+{
+    BLOCK* block;
+    struct QueueOfBlocks* next;
+};
+typedef struct QueueOfBlocks QBLOCK;

### 2019-10-20 Code/utilsforfiber.h

@@ -9,6 +9,7 @@
 #include <stdlib.h>
 #include <string.h>
 #include <math.h>
+//#include "structforfiber.h"
 
 ////////////////////////////////////////////////////////////////////
 /// Structures to create and define a directed, unweighted graph ///
@@ -353,12 +354,59 @@ struct DoublyLinkNode
 };
 typedef struct DoublyLinkNode DoublyLinkNode;
 
-struct Block
+// The doubly linked list of the block containing the elements on it
+struct BLOCK
 {
     int size;
-    DoublyLinkNode* head;   // The doubly linked list of the block containing the elements on it.
+	int index;
+    DoublyLinkNode* head;
 };
-typedef struct Block BLOCK;
+typedef struct BLOCK BLOCK;
+
+struct Partition
+{
+	BLOCK* block;
+	struct Partition* prev;
+	struct Partition* next;
+};
+typedef struct Partition PART;
+///////////////////////////////////////////////////////////
+
+extern int nblock(PART** head)
+{
+	if(*head==NULL) return 0;
+	
+	int i = 0;	
+	PART* temp = *head;
+	while(temp)
+	{
+		i++;
+		temp = temp->next;
+	}
+	return i;
+}
+
+extern void push_block(PART** head, BLOCK* insertion)
+{
+    PART* new_node = (PART*)malloc(sizeof(PART));
+    
+    new_node->block = insertion;
+    new_node->next = (*head);
+    new_node->prev = NULL;
+    if((*head)!=NULL) (*head)->prev = new_node;
+    (*head) = new_node;
+}
+
+extern int doublycheck_element(DoublyLinkNode* head, int element)
+{
+	DoublyLinkNode* temp = head;
+	while(temp)
+	{
+		if(temp->data==element) return 1;
+		temp = temp->next;
+	}
+	return 0;
+}
 
 extern void push_doublylist(DoublyLinkNode** head, int insertion)
 {
@@ -449,4 +497,50 @@ void printBlock(BLOCK* P)
         List = List->next;
     }
 }
-//////////////////////////////////////////////////////////////////////////////////
+
+void printBlockSize(BLOCK* P)
+{
+	printf("Size: %d\n", P->size);
+}
+/////////////////////////////////////////////////////////////
+
[…]

### 2019-10-21 Code/RefineToFiber.c
...

@@ -27,147 +27,165 @@
 #include <gsl/gsl_eigen.h>
 #include "utilsforfiber.h"   // Personal module containing helpful functions to handle with network data and other common operations.
 
+void Upgrade_partition(PART** new_blocks, PART** old_blocks, PART** partition)
+{
+	BLOCK* tempblock = NULL;	
+	PART* temp_old = *old_blocks;
+	PART* temp_new = *new_blocks;
+	while(temp_old) { deletePart(old_blocks, *old_blocks); }
+	
+}
+
+void push_on_block(int node, int n_in, PART** phead)
+{
+	BLOCK* tempblock = NULL;
+	PART* parttemp = *phead;
+	while(parttemp)
+	{
+		tempblock = parttemp->block;
+		if(tempblock->index==n_in) { add_to_block(&tempblock, node); return; }
+	}
+	// If the function reaches this line, it didnt find any block. So we create a new one.
+	BLOCK* newblock = (BLOCK*)malloc(sizeof(BLOCK));
+	newblock->index = n_in;
+	newblock->size = 0;
+	add_to_block(&newblock, node);
+	push_block(phead, newblock);
+}
+
 int intersection_edges(Graph* graph, int node, BLOCK* Set)
 {
 	int i, check;	
 	NodeAdj* Node = graph->array[node].head_in;
-	BLOCK* SetHead = Set->head;
 
 	int n_in = 0;
 	while(Node)
 	{
-		check = doublycheck_element(SetHead, Node->neighbor);
+		check = doublycheck_element(Set->head, Node->neighbor);
 		if(check==1) n_in++;
 		Node = Node->next;
 	}
 	return n_in;	
 }
 
-void SPLIT(PART** partition, BLOCK* Set, Graph* graph, int N, QBLOCK** head, QBLOCK** tail)
+void S_SPLIT(PART** partition, BLOCK* Set, Graph* graph, int N, QBLOCK** head, QBLOCK** tail)
 {	
 	PART* subpart1 = NULL;
 	PART* subpart2 = NULL;
-	PART* temp = partition;
 	BLOCK* tempblock = NULL;	
+	PART* temp_part = *partition;
 	DoublyLinkNode* tempdoublylist;
-	int* nedges = (int*)malloc(N*sizeof(int));
 
 	/*	Given the 'Set' block, now we select all the blocks in the partition that have at 
 		least one inward connection coming from 'Set'. */
-	
[…]

### 2019-10-21 Code/utilsforfiber.h

@@ -420,6 +420,12 @@ extern void push_doublylist(DoublyLinkNode** head, int insertion)
     (*head) = new_node;
 }
 
+extern void add_to_block(BLOCK** block, int node)
+{
+	push_doublylist(&(*block)->head, node);
+	(*block)->size++;
+}
+
 extern void insertAfter(DoublyLinkNode* prev_node, int insertion)
 {
     if (prev_node == NULL) return; 
@@ -465,9 +471,53 @@ extern void append(DoublyLinkNode** head, int new_data)
     return; 
 }
 
+void check_equalBlock(Block* block1, Block* block2)
+{
+	if(block1->size!=block2->size) return -1;
+	
+	DoublyLinkNode* head1 = block1->head;
+	DoublyLinkNode* head2 = block2->head;	
+	while(head1)
+	{
+		if(head1->data!=head2->data) return -1;
+		head1 = head1->next;
+		head2 = head2->next;
+	}
+	return 1;
+}
+
 void deleteNode(DoublyLinkNode** head_ref, DoublyLinkNode* del) 
 { 
     /* base case */
+    if (*head_ref == NULL || del == NULL) 
+        return; 
+  
+    /* If node to be deleted is head node */
+    if (*head_ref == del) 
+        *head_ref = del->next; 
+  
+    /* Change next only if node to be deleted is NOT the last node */
+    if (del->next != NULL) 
+        del->next->prev = del->prev; 
+  
+    /* Change prev only if node to be deleted is NOT the first node */
+    if (del->prev != NULL) 
+        del->prev->next = del->next; 
+  
+    /* Finally, free the memory occupied by del*/
+    free(del); 
+    return; 
+}
+
+void deletePart(PART** head_ref, PART* del) 
+{ 
+	BLOCK* tempblock = del->block;    
+	if(tempblock!=NULL)	// First delete all the nodes of the block.
+	{
+		DoublyLinkNode* temp = tempblock->head;
+		while(temp) { deleteNode(&temp, temp); }
+	}
+  
     if (*head_ref == NULL || del == NULL) 
         return; 
   
@@ -495,6 +545,16 @@ void printBlock(BLOCK* P)
     {
         printf("%d ", List->data);
         List = List->next;
+    }
+}
+
+void printPartition(PART* P)
+{
+    PART* part = P;
+    while(part)
+    {
+        printf("%d ", part->block->index);
+        part = part->next;
     }
 }
 

### 2019-10-29 Manuscript/main.tex
Finishing process

@@
 
-\maketitle % Print the title section
+%\maketitle % Print the title section
+
+\begin{center}	
+	{\LARGE \textbf{Project Report: Física Teórica I}}\\[0.25cm]
+	{ $\bullet$ }\\
+	\vspace{0.25cm}
+	{\large \textbf{Identification and classification of information-processing building blocks on genetic regulatory network}}\\[0.25cm]
+	{ Higor da S. Monteiro }\\
+	{ $\bullet$ }\\
+	{ Departament of Physics - Universidade Federal do Ceará(UFC) }\\
+	{ Fortaleza, Ceará }\\
+	{ October, 25, 2019 }\\[0.75cm]
+	{\textbf{Abstract}}
+
+\end{center}
+
+Fibration building blocks of a information flow network represent the sets of nodes that are symmetric with respect to the processing of information, that is, the sets of nodes that process equivalent information.
+Here, we have reproduced important results concerning the identification and classification of the fibration building blocks of directed networks, constructed from real network data.
+More specifically, using the transcriptional regulatory network data of the \textit{Escherichia Coli} bacteria, we quantify the clusters of nodes that synchronously process equivalent information and then we classify these clusters, called network fibers, based on its specific topological features.
+This way, in order to consistently present the obtained results, in this report we first give a brief description of the theory concerning the graph fibration morphism and its main definitions related to information flow symmetries.
+Next, we detail the methods adopted to correctly identify and classify the network fibers.
+More specifically, to establish an optimal framework, I show the implementation details of the Minimal Balanced Coloring algorithm used to find the corresponding fibers in the network, presenting a slightly improvement for the algorithm complexity and its implementation.
+At last, showing the proper methods for data preparation, I describe the results obtained concerning the fiber statistics for the specific case of the \textit{Escherichia Coli} regulatory network, to properly compare with the recent results presented at \textit{Morone et.
+al.} (2019).
 
@@
 
-\begin{abstract}
-	Fibration building blocks of a network represent the sets of nodes that are symmetric with respect to information processing.
+%\begin{abstract}
+%	Fibration building blocks of a information flow network represent the sets of nodes that are symmetric with respect to the processing of information, that is, the sets of nodes that process equivalent information.
 Here, we have reproduced important results concerning the identification and classification of the fibration building blocks of directed networks, constructed from real network data.
-More specifically, using the transcriptional regulatory network data of the \textit{Escherichia Coli} bacteria, we quantify the groups of network nodes that synchronously process equivalent information and then we classify each fiber based on its specific topological features.
+More specifically, using the transcriptional regulatory network data of the \textit{Escherichia Coli} bacteria, we quantify the clusters of nodes that synchronously process equivalent information and then we classify these clusters, called network fibers, based on its specific topological features.
 This way, in order to consistently present the obtained results, in this report we first give a brief description of the theory concerning the graph fibration morphism and its main definitions related to information flow symmetries.
 Next, we detail the methods adopted to correctly identify and classify the network fibers.
-More specifically, to establish an optimal framework, I show the implementation details of the Minimal Balanced Coloring algorithm used to find the corresponding fibers in the network, presenting a slightly improvement for the algorithm complexity.
+More specifically, to establish an optimal framework, I show the implementation details of the Minimal Balanced Coloring algorithm used to find the corresponding fibers in the network, presenting a slightly improvement for the algorithm complexity and its implementation.
 At last, showing the proper methods for data preparation, I describe the results obtained concerning the fiber statistics for the specific case of the \textit{Escherichia Coli} regulatory network, to properly compare with the recent results presented at \textit{Morone et.
 al.} (2019).
-\end{abstract}
-
-\hspace*{3.6mm}\textit{Keywords:} Graph Morphism; Biological Networks; Information Processing, Fibration, lectus % Keywords
+%\end{abstract}
 
@@
 
-\section{\textit{Minimal Balanced Coloring }Algorithm}
+\section{\textit{Coarsest Refinement Partitioning }Algorithm}
+
+In order to identify the correct distribution of network fibers we have to find a efficient procedure to split the network in different disjoint partitions, in which all nodes from a same partition should receive information from the same other partitions.
+To do that, we treat our problem as the same of find the coarsest relational refinement partitioning for the given network.
+In this section, we detail the optimal algorithm used to find this coarsest partitioning in a context of graph fibrations and show the relative simple implementation of this method.
 
@@
 
-For the proper identification of the fibers on the network we have to construct a graph partition that is equivalent to a coarse grain of the network with respect to the information flow passing through each node.
+The algorithm used in this project is a slightly modified version of the algorithm presented by Paige and Tarjan \cite{Tarjan1987}, \ having a time complexity of $O(M\log N)$, being very efficient for sparse networks.
+This algorithm has the same runtime order than the algorithm from Cardon and Crushemore \cite{Cardon1982}, but it has a simpler implementation and smaller prefactors, exhibiting a better approach to our problem.
+Even though the algorithm applies for general situations, here we give the details of the algorithm to its application for a network, so we introduce the necessary definitions within this context.
 
-Aliquam fringilla non diam sed varius.
-Suspendisse tellus felis, hendrerit non bibendum ut, adipiscing vitae diam.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Nulla lobortis purus eget nisl scelerisque, commodo rhoncus lacus porta.
-Vestibulum vitae turpis tincidunt, varius dolor in, dictum lectus.
-Aenean ac ornare augue, ac facilisis purus.
-Sed leo lorem, molestie sit amet fermentum id, suscipit ut sem.
-Vestibulum orci arcu, vehicula sed tortor id, ornare dapibus lorem.
-Praesent aliquet iaculis lacus nec fermentum.
-Morbi eleifend blandit dolor, pharetra hendrerit neque ornare vel.
-Nulla ornare, nisl eget imperdiet ornare, libero enim interdum mi, ut lobortis quam velit bibendum nibh.
+A network $G$ is completely defined as $G(V, E)$ by the sets of nodes $V$ and of the connections $E$.
+The network has then $N = |V|$ nodes that can have connections with one another defined by the set $E$ containing $M = |E|$ ordered pair of nodes, denoting the directed connections between the network nodes.
+Over the network, we can define a graph partition $P$ of $V$ as a set of pairwise disjoints subsets of $V$ whose union is all $V$
+\begin{equation}
+	P = \cup_{i=1}^{N_P} P_i
+\end{equation}
+where $P_i$ are the elements of the partition $P$, in which we call it blocks.
+Within this context, if we consider an additional graph partition $Q$ that has the property that all the block of $Q$ is contained in a block of $P$, we say that $Q$ is a refinement partition of $P$.
 
-\begin{itemize}
-	\item First bullet point item
-	\item Second bullet point item
-	\item Third bullet point item
-\end{itemize}
+Considering a block $B$ in $P$, we say that the block $B$ is stable with respect with a set $S$ if or all elements of $B$ connects an element of $S$ or none element of $B$ points to any element of $S$.
+By that we define that a graph partition $P$ of $V$ is stable if it is stable with respect with its own blocks.
+Having defined that, the graph coarsest partition problem is that of finding, for a given set of connections $E$ and initial partition $P$ over $V$, the coarsest stable refinement of $P$.
+
+Considering all that, for the proper identification of the fibers on the network we have to construct a stable graph partition that is equivalent to the coarsest (minimal number of blocks) refinement of the network with respect to the information flow passing through each node.
+For that, we need to extend the concept of stability over the partition for one that accounts for the information received by each block of the partition.
+Thus, in order to identify the clusters with isomorphic input-tree for all their nodes, we require that the partition should be not only stable but input-tree stable.
+That means that for a subset $S \subseteq$ $V$, a graph partition $P$ over the network $G(V, E)$ is input-tree stable with respect to $S$ if for all the block $B \in P$, the equality
+\begin{equation}
+	| E^{-1}(\{x\}) \cap S | = | E^{-1}(\{y\}) \cap S |
+\end{equation}
+is satisfied for all the elements $x$, $y \in B$.
+
+This way, we can benefit from the stability properties \cite{Tarjan1987} to construct a refinement algorithm step that can obtains, through a finite number of steps, a input-tree stable partition from an initial unstable partitioning of the network.
+With this, given a subset $S \subseteq V$, the refinement step has the effect to refine the current partition, unstable with respect to $S$, by replacing it for a new partition now stable with $S$.
+For that, we define a split function \textit{I-split($S$, $P$)} that receive as input the current partition and a set $S$ and results as output a new input-tree stable partition with respect to $S$.
+That function benefits from two major properties of stability (and input-tree stability): the stability inheritance by refinement and by union of sets.
+Since this refinement inheritance, a given set $S$ can be used only once by the function \textit{I-split}, for which after all other refinement will be stable with respect to $S$.
+Moreover, since stability is inherited under union of sets $S$, after sets are used in \textit{I-split}, their union cannot be used for the function.
+With all this considered, the essence of the algorithm can be stated as
+
+\begin{quotation}
+	Find a set $S$ in which the current partition $P$ is input-tree unstable.
+Replace $P$ by the output of \textit{I-split($S$,$P$)}.
+Guarantees that the set $S$ or unions of used sets never be used again.
+\end{quotation}
+
+Since the finest partitioning possible is the one in which every node is itself a block, the refinement step can be proceeded at most $N-1$ times, guaranting that the algorithm terminates with the correct answer, since stability is inherited by the refinement process.
+However, to guarantees that the algorithm has a optimal runtime we have to find a efficient way to select the appropriate sets to the refinement step, without choosing repeated sets.
+Fortanately, this can be easily done for the construction of a input-tree stable partition.
+
+Given a set $S$ of nodes from the network $G$ and a given input-tree unstable graph partition $Q$, the blocks $B \in Q$ that are input-tree unstable with respect to $S$ can be splitted in several blocks $B_j$ to have a stable input-tree for $S$.
+Then, each splitted block will have the property defined by
+\begin{equation}
+	B_j = \{ x \in B : | E^{-1}(\{x\}) \cap S | = j \}
+\end{equation}
+where the number of splitted block must be larger than one to a proper split process take place.
+Then, for each unstable block $B \in Q$ all the splitted block, except the largest one, can be put a queue to be used ahead in the algorithm as a refinement set.
+This ensures that none repeated sets or union of repeated sets can be used during the algorithm exeecution.
+
+Having said all that, the complete algorithm to find the correct network fibers of a network $G(V, E)$ consists in initializing a graph partition $Q$ over all nodes from $V$ except the nodes that do not receive information from any other node, in which each one of these will be defined as isolated fibers already in the beginning of the algorithm.
+The partition $Q$ is defined as one block containing all the other nodes in the network.
+The algorithm maintains a queue $L$ of possible refinement sets, initially containing the single block of $Q$ and all the isolated blocks defined at the beginning.
+Then, we proceed as
+\begin{quotation}
+	Remove from $L$ its first set $S$. Replace $Q$ by the \textit{I-split($S$, $Q$)}. Whenever a block $B \in Q$ splits into two or more nonempty blocks, add all but the largest to the back of $L$.
+\end{quotation}
+And this process is repeated until the queue $L$ is empty.
+At this point, the resulted partition $Q$ represent the coarsest input-tree stable partitioning of the network $G(V, E)$, where each block represents a network fiber with all its nodes having isomorphic input-trees.
+
+% faltou o preprocessing.
 
@@
 
-Morbi tempor congue porta.
-Proin semper, leo vitae faucibus dictum, metus mauris lacinia lorem, ac congue leo felis eu turpis.
-Sed nec nunc pellentesque, gravida eros at, porttitor ipsum.
-Praesent consequat urna a lacus lobortis ultrices eget ac metus.
-In tempus hendrerit rhoncus.
-Mauris dignissim turpis id sollicitudin lacinia.
-Praesent libero tellus, fringilla nec ullamcorper at, ultrices id nulla.
-Phasellus placerat a tellus a malesuada.
+We apply the above algorithm in the genetic regulatory network of the \textit{Escherichia Coli} bacteria.
+We obtain the genetic E.
+Coli network through its transcriptional regulatory interactions data, where each gene is regulated by a transcription factor protein.
+Since a transcription factor production in the cell is regulated by a gene, we can define a directed connection between two genes if a gene regulates the production of a transcriptional factor, which it regulates another gene.
+Since a transcription factor can be either an activator(positive) or repressor(negative), or even behaves as both(dual), the links between genes can carry different types of messages.
+Because of that, it is important that the partitioning algorithm accounts the type of message to construct appropriate input-trees for the network fibers partition.
+Therefore, for a proper application of the algorithm on the \textit{Escherichia Coli} genetic network, we label each node uniquely, either as number or string names, and also each link with the type of connection between genes.
 
-\begin{enumerate}
-	\item First numbered list item
-	\item Second numbered list item
-\end{enumerate}
+Considering this context, we explain now how the algorithm should proper be implemented to have an optimal perfomance concerning its runtime complexity.
+After discussing the data structures necessary to deal correctly with data, we design an algorithm recipe to show all the main steps of the process explained above.
+Also, anyone can acess our own personal implementation for genetic regulatory networks in the link \url{https://github.com/higorsmonteiro/fiberblocks} on github platform.
+
+Given a directed network $G(V, E)$ to be partitioned in fibers, it is very important for the correctness of the algorithm that the nodes that do not receive any information, that is, the nodes that do not have any inward connections, be preprocessing as isolated blocks.
+This means that the initial graph partition $P$ is divided in two different partition $P'$ e $P''$, the first one contained all the single-node blocks containing the solitaire nodes $v$ in which $| E^{-1}(\{v\}) | = 0$, and the second one containing initialing a single block containing all the other nodes $w$ in which $| E^{-1}(\{w\}) | \geq 1$.
+The importance of this preprocessing is to guarantee that solitaire nodes do not be put on the same fibers during the refinement steps.
+Even though the blocks of $P'$ are used as refinement sets, $P'$ is not used by the algorithm.
+Thus, the final partition is the union of $P'$ and the result of the refinement partitioning of $P''$.
+
+After the above preprocessing we define the data structures for the partition $Q$ for its blocks $B$.
+A partition is a doubly linked list of blocks, which allows that deletion of blocks be made in constante time $O(1)$ as long we have the block memory address during the procedure.
+A block is just a structure containing indexing data along with a doubly linked list containg all the nodes that belongs to it.
+Together with a queue of blocks $L$, these constructions are the main data structures necessary for an efficient implementation of the refinement partitioning algorithm.
+At the beginning of the algorithm, we enqueue all the blocks of $P'$ e $P''$ to $L$.
+Then, we start the algorithm initializing a partition $Q = P''$ and by removing the top element set $S$ of $L$, then we apply the \textit{I-split($S$, $Q$)} to identify the input-tree unstable blocks of $Q$ and split them into input-tree stable blocks with respect to  $S$.
+This way, all the splitted blocks are push to the end of $L$, with exception the largest resulted blocks for each splitted block.
+As we have mentioned, the algorithm terminates when there is no more sets in $L$.
+Even though this is the whole algorithm, the implementation of the \textit{I-split} function is not so straightforward, since a given block $B$ can be splitted into an arbitrary number of blocks.
+So, we detail the implementation of this function below.
+
+In the algorithm recipe below, the structures $U$ and $S$ are initially empty partitions and are used to store, respectively, all the input-tree unstable blocks of $Q$ and all the splitted blocks from $U$.
+
+\begin{algorithm}
+   \caption{Input-tree split function}
+    \begin{algorithmic}[1]
+      \Function{\textit{I-split}}{$S, Q$}
+        \State Initialize the empties partitions $U, T$
+        \For{$\forall B \in Q$}
+			\For{$\forall x \in B$}
+            	\State Calculates $| E^{-1}(\{x\})\cap S |$
+			\EndFor 
+			\If {$| E^{-1}(\{x\})\cap S | \neq | E^{-1}(\{y\})\cap S |$} \Comment{$x, y \in B$}
+				\State insert block $B$ in $U$.
+			\EndIf       
+		\EndFor
+        \For{$\forall B \in U$}
+			%\State defines an empty partition $Z$
+			\For{$\forall x \in B$}
+				\If{$\exists \ X \in T : | E^{-1}(\{x\})\cap S | = T(E)$ }
+					\State insert $x$ in $X$
+				\Else				
+					\State create a new block $X$
+					\State insert $x$ in $X$
+					\State $X(E) \leftarrow | E^{-1}(\{x\})\cap S |$
+					\State insert block $X$ in $T$ 
+				\EndIf
+			\EndFor
+			\State enqueue all blocks $X \in T$ to $L$, except $Larger(T)$
+        \EndFor
+       \EndFunction
+
+\end{algorithmic}
+\end{algorithm}
 

### 2019-10-29 Code/RefineToFiber.c

@@ -16,7 +16,7 @@
 	file ('ARG1edgelist.dat') containing all the directed links between nodes (3 columns: "%d\t%d\t%s\n" -> Pointing Node/ Pointed Node/ 
 	Type of regulation). For gene regulatory networks, the type of the regulation can be positive, negative or dual.
 
-	The result is stored in two arrays: 'nodecolor' and 'edgecolor'. Each array store the color of each component (node or 
+	The result is stored in two arrays: 'nodefiber'. Each array store the color of each component (node or 
 	link) and, thus, gives all the information needed, together with the files, for the base graph construction.
 
 	Author: Higor da S. Monteiro
@@ -35,64 +35,64 @@
 /////////////////////////////////////////////////////////////////////////////////////////
 #define SENTINEL -96
 
+
+/*	Calculates the fundamental class number. For that, for each fiber block, we select
+	all the nodes belonging to the block and all the external nodes that regulates that 
+	same fiber.	After that, construct the adjacency matrix for that set and obtain its
+	largest eigenvalue. */
 void CALCULATE_FUNDAMENTAL(PART** partition, Graph* graph)
 {
 	int i, j, k;
-	int neigh, index, nn;
-	int nregulators;
-	int n_nodes;
+	int check, index, nn;
+	int all_nodes;	
+	int number_fnodes;
+	int number_regulators;
 
-	int* temp_index;
-	double* temp_adjmatrix;
+	int* temp_index;			// Temporary indexation for each node in the circuit set.
+	double* temp_adjmatrix;		// n*n array to define the adjacency matrix.
 
-	int h = 0;
 	PART* current_part;
 	NODELIST* nodelist;
+	// Loop over all the fiber blocks.
 	for(current_part=(*partition); current_part!=NULL; current_part=current_part->next)
 	{
-		n_nodes = current_part->block->size;
-		nregulators = current_part->number_regulators;
-		nn = n_nodes+nregulators;
+		number_fnodes = current_part->block->size;
+		number_regulators = current_part->number_regulators;
+		all_nodes = number_fnodes+number_regulators;
 
 		index = 0;
[…]

### 2019-10-29 Code/bacdata.py

@@ -5,7 +5,7 @@ from collections import defaultdict
 
 name_relation = defaultdict(list)
 #table = pd.read_csv("../Data/rawData/interactions_bacilus.txt", sep=" ", names=['Source', 'Target'])
-table = pd.read_csv("../Data/Ecoli/Ecoli.txt", sep=" ", names=['Source', 'Target', 'Regulation'])
+table = pd.read_csv("../Data/Ecoli.txt", sep=" ", names=['Source', 'Target', 'Regulation'])
 
 destname = "../Data/ECOLINgenes.dat"
 edgelistname = "../Data/ECOLIedgelist.dat"
@@ -18,6 +18,7 @@ targets = list(table['Target'][:])
 types = list(table['Regulation'][:])
 sources = sources + targets
 sources = list(set(sources))
+sources.sort()
 
 print(set(types))
 
@@ -33,6 +34,11 @@ for index, row in table.iterrows():
     edgelist[index, 1] = labels[sources.index(dest)]
     type_reg.append(types[index])
 
+file = open("../Data/ECOLInameID.dat", "w")
+for index, name_str in enumerate(sources):
+	file.write("%s\t%d\n" % (name_str, labels[index]))
+file.close()
+
 file = open(destname, "w")
 file.write("%d\n" % ngenes)
 file.close()
@@ -41,3 +47,4 @@ file = open(edgelistname, "w")
 for index, type_str in enumerate(type_reg):
     file.write("%d\t%d\t%s\n" % (edgelist[index,0], edgelist[index,1], type_str))
 file.close()
+

### 2019-10-29 Code/structforfiber.h

@@ -17,6 +17,7 @@ typedef struct Graph Graph;
 
 struct adjList
 {
+	char gene_name[60];	
 	struct NodeAdj* head_in;
     struct NodeAdj* head_out;
 };
@@ -142,6 +143,14 @@ void printBlock(BLOCK* P)
 	printf("\n");
 }
 
+void printBlockGene(BLOCK* P, Graph* graph)
+{
+    NODELIST* List = P->head;
+	for(List=P->head; List!=NULL; List=List->next)
+		printf("%s, ", graph->array[List->data].gene_name);
+	printf("\n");
+}
+
 void printBlockSize(BLOCK* P)
 {
 	printf("Size: %d\n", P->size);
@@ -157,6 +166,20 @@ void printAllPartition(PART* head)
 		aux_block = temp->block;
 		printf("Block %d with size %d: ", aux_block->index, aux_block->size);
 		printBlock(aux_block);
+		temp = temp->next;
+	}
+}
+
+void printGenesPartition(PART* head, Graph* graph)
+{
+	if(head==NULL) printf("EMPTY\n");	
+	PART* temp = head;
+	BLOCK* aux_block = NULL;
+	while(temp)
+	{
+		aux_block = temp->block;
+		printf("Block %d with size %d: ", aux_block->index, aux_block->size);
+		printBlockGene(aux_block, graph);
 		temp = temp->next;
 	}
 }

### 2019-10-29 Code/utilsforfiber.h

@@ -29,7 +29,7 @@ NodeAdj* createNode(int neigh, int type_link)
 	return newnode;
 }
 
-extern Graph* createGraph(int N)
+extern Graph* createGraph(int N, char* nodenames)
 {
 	Graph* graph = (Graph*)malloc(sizeof(Graph));
 	graph->size = N;
@@ -38,7 +38,21 @@ extern Graph* createGraph(int N)
 	graph->array = (AdjList*)malloc(N*sizeof(AdjList));
 
 	int j;
-	for(j=0; j<N; j++) { graph->array[j].head_in = NULL; graph->array[j].head_out = NULL; }
+	for(j=0; j<N; j++)
+	{ 
+		graph->array[j].head_in = NULL; 
+		graph->array[j].head_out = NULL; 
+	}
+
+	int nodeID;
+	char tempname[60];
+	FILE* NAMES = fopen(nodenames, "r");
+	for(j=0; j<N; j++)
+	{		
+		fscanf(NAMES, "%s\t%d\n", &tempname, &nodeID);
+		strcpy(graph->array[nodeID].gene_name, tempname);
+	}
+	fclose(NAMES);
 	return graph;
 }
 
@@ -133,6 +147,15 @@ extern int GETNin(Graph* graph, int node)
 	int n_in = 0;	
 	NodeAdj* NODE;
 	for(NODE=graph->array[node].head_in; NODE!=NULL; NODE=NODE->next) n_in++;
+	return n_in;	
+}
+
+extern int GETinType(Graph* graph, int node, int type)
+{
+	int n_in = 0;	
+	NodeAdj* NODE;
+	for(NODE=graph->array[node].head_in; NODE!=NULL; NODE=NODE->next)
+		if(NODE->type_link==type) n_in++;
 	return n_in;	
 }
 

### 2019-10-30 Manuscript/main.tex
Draft

@@
 %\renewcommand{\abstractname}{Summary} % Uncomment to change the name of the abstract to something else
-
-%\begin{abstract}
-%	Fibration building blocks of a information flow network represent the sets of nodes that are symmetric with respect to the processing of information, that is, the sets of nodes that process equivalent information.
-Here, we have reproduced important results concerning the identification and classification of the fibration building blocks of directed networks, constructed from real network data.
-More specifically, using the transcriptional regulatory network data of the \textit{Escherichia Coli} bacteria, we quantify the clusters of nodes that synchronously process equivalent information and then we classify these clusters, called network fibers, based on its specific topological features.
-This way, in order to consistently present the obtained results, in this report we first give a brief description of the theory concerning the graph fibration morphism and its main definitions related to information flow symmetries.
-Next, we detail the methods adopted to correctly identify and classify the network fibers.
-More specifically, to establish an optimal framework, I show the implementation details of the Minimal Balanced Coloring algorithm used to find the corresponding fibers in the network, presenting a slightly improvement for the algorithm complexity and its implementation.
-At last, showing the proper methods for data preparation, I describe the results obtained concerning the fiber statistics for the specific case of the \textit{Escherichia Coli} regulatory network, to properly compare with the recent results presented at \textit{Morone et.
-al.} (2019).
-%\end{abstract}
 
@@
 \begin{equation}
-	P = \cup_{i=1}^{N_P} P_i
+	P = \bigcup_{i} P_i
 \end{equation}
@@
 As we have mentioned, the algorithm terminates when there is no more sets in $L$.
-Even though this is the whole algorithm, the implementation of the \textit{I-split} function is not so straightforward, since a given block $B$ can be splitted into an arbitrary number of blocks.
-So, we detail the implementation of this function below.
+Even though this is the whole algorithm, the implementation of the \textit{I-split} function might not be so straightforward, since a given block $B$ can be splitted into an arbitrary number of blocks.
+In respect to that below we propose the following implementation construction to the splitting function:
 
-In the algorithm recipe below, the structures $U$ and $S$ are initially empty partitions and are used to store, respectively, all the input-tree unstable blocks of $Q$ and all the splitted blocks from $U$.
+\begin{algorithm}[h]
+	\SetAlgoLined
+	\SetKwInOut{Input}{Input}
+    \SetKwInOut{Output}{Output}
+	\Input{A set $S$ and a partition $\bar{Q}$}
+    \Output{Input tree stable partition $\bar{Q}$ with respect to $S$}
+	%\KwResult{}
+	Initialize $\bar{U}$ as an empty partition\;
+	\For{$\forall B \in \bar{Q}$}
+	{
+		\If{$\exists \ \{ w_i, w_j \} \subseteq B : | E^{-1}(\{w_i\})\cap S | \neq | E^{-1}(\{w_j\})\cap S |$}
+		{
+			\textit{push} $B$ to $\bar{U}$\;
+			Initialize $\bar{T}$ as an empty partition\;
+			\For{$\forall w_i \in B$}
+			{
+				\eIf{$\exists \ X \in \bar{T} : | E^{-1}(\{w_i\})\cap S | = X(E)$ }
+				{
+					insert $w_i$ in $X$\;
 
-\begin{algorithm}
-   \caption{Input-tree split function}
-    \begin{algorithmic}[1]
-      \Function{\textit{I-split}}{$S, Q$}
-        \State Initialize the empties partitions $U, T$
-        \For{$\forall B \in Q$}
-			\For{$\forall x \in B$}
-            	\State Calculates $| E^{-1}(\{x\})\cap S |$
-			\EndFor 
-			\If {$| E^{-1}(\{x\})\cap S | \neq | E^{-1}(\{y\})\cap S |$} \Comment{$x, y \in B$}
-				\State insert block $B$ in $U$.
-			\EndIf       
-		\EndFor
-        \For{$\forall B \in U$}
-			%\State defines an empty partition $Z$
-			\For{$\forall x \in B$}
-				\If{$\exists \ X \in T : | E^{-1}(\{x\})\cap S | = T(E)$ }
-					\State insert $x$ in $X$
-				\Else				
-					\State create a new block $X$
-					\State insert $x$ in $X$
-					\State $X(E) \leftarrow | E^{-1}(\{x\})\cap S |$
-					\State insert block $X$ in $T$ 
-				\EndIf
-			\EndFor
-			\State enqueue all blocks $X \in T$ to $L$, except $Larger(T)$
-        \EndFor
-       \EndFunction
+				}
+				{
+					create a new block $X$\;
+					insert $w_i$ in $X$\;
+					$X(E) \leftarrow | E^{-1}(\{w_i\})\cap S |$\;
+					push block $X$ to $\bar{T}$ 
+				}
+			}
+		}
+		\textit{enqueue} all blocks $X \in \bar{T}$ in $L$, except the largest one\;
+		\textit{push} all blocks $X \in \bar{T}$ to $\bar{Q}$\;
+	}
+	\textit{delete} all blocks $B \in \bar{U}$ in $\bar{Q}$
+	\caption{\textit{I-split} $(S,\bar{Q}, L)$}
+\end{algorithm}
 
-\end{algorithmic}
+In the algorithm recipe above, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output.
+Besides its list of nodes, a block $X$ has another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$.
+This way, a node $w$ belonging to the block to be splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm above.
+
+Finally, considering all the discussion above, we can explicit the complete algorithm in just a few steps.
+
+\begin{algorithm}[h]
+	\SetAlgoLined
+	\SetKwInOut{Input}{Input}
+	\Input{A network $G(V, E)$}
+	%\KwResult{}
+	Initialize $S$ as an empty set\;
+	Initialize $L$ as an empty queue\;
+	Initialize $\bar{P}$, $\bar{P'}$, $\bar{P''}$, $\bar{Q}$ as empty partitions\;
+	$B' = \{ \{ w \} \in V : |E^{-1}(\{w\})|=0 \}$\;
+	$B'' = \{ v \in V : |E^{-1}(\{v\})| \geq 1 \}$\;
+	\textit{push} all $B'$ to $\bar{P'}$\;
+	\textit{push} $B''$ to $\bar{P''}$\;
+	\textit{enqueue} $B'' \in \bar{P''}$ to $L$\;
+	\textit{enqueue} all blocks $B' \in \bar{P'}$ to $L$\;
+	$\bar{Q} \leftarrow \bar{P''}$\;
+	\While{$|L| \neq 0$}
+	{
+		$S \leftarrow \text{\textit{dequeue}}(L)$\;
+		$\bar{Q} \leftarrow \text{\textit{I-input}}(S, \bar{Q}, L)$
+	}
+	\caption{Coarsest Refinement Graph Partitioning}
 \end{algorithm}
+
+A concrete implementation of the algorithm in a programming language is presented at the link \url{https://github.com/higorsmonteiro/fiberblocks} together with \textit{E.
+Coli} prepared data and another examples.
+Further information about the application of the codes in other genetic regulatory network data can be found at the same link given.
 
@@
 
-Fusce in nibh augue.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-In dictum accumsan sapien, ut hendrerit nisi.
-Phasellus ut nulla mauris.
-Phasellus sagittis nec odio sed posuere.
-Vestibulum porttitor dolor quis suscipit bibendum.
-Mauris risus lectus, cursus vitae hendrerit posuere, congue ac est.
-Suspendisse commodo eu eros non cursus.
-Mauris ultrices venenatis dolor, sed aliquet odio tempor pellentesque.
-Duis ultricies, mauris id lobortis vulputate, tellus turpis eleifend elit, in gravida leo tortor ultricies est.
-Maecenas vitae ipsum at dui sodales condimentum a quis dui.
-Nam mi sapien, lobortis ac blandit eget, dignissim quis nunc.
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.3]{Figures/result1.png}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.3]{Figures/result1-1.png}
+\end{figure}
 
-Donec luctus tincidunt mauris, non ultrices ligula aliquam id.
-Sed varius, magna a faucibus congue, arcu tellus pellentesque nisl, vel laoreet magna eros et magna.
-Vivamus lobortis elit eu dignissim ultrices.
-Fusce erat nulla, ornare at dolor quis, rhoncus venenatis velit.
-Donec sed elit mi.
-Sed semper tellus a convallis viverra.
-Maecenas mi lorem, placerat sit amet sem quis, adipiscing tincidunt turpis.
-Cras a urna et tellus dictum eleifend.
-Fusce dignissim lectus risus, in bibendum tortor lacinia interdum.
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.3]{Figures/result2.png}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.3]{Figures/result2-1.png}
+\end{figure}
 
-\begin{table}[h] % [h] forces the table to be output where it is defined in the code (it suppresses floating)
-	\caption{Example table.}
+\begin{figure}[h]
 	\centering
-	\begin{tabular}{l l r}
-		\toprule
-		\multicolumn{2}{c}{Name} \\
-		\cmidrule(r){1-2}
-		First Name & Last Name & Grade \\
-		\midrule
-		John & Doe & $7.5$ \\
-		Richard & Miles & $5$ \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Fusce eleifend porttitor arcu, id accumsan elit pharetra eget.
-Mauris luctus velit sit amet est sodales rhoncus.
-Donec cursus suscipit justo, sed tristique ipsum fermentum nec.
-Ut tortor ex, ullamcorper varius congue in, efficitur a tellus.
-Vivamus ut rutrum nisi.
-Phasellus sit amet enim efficitur, aliquam nulla id, lacinia mauris.
-Quisque viverra libero ac magna maximus efficitur.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Vestibulum mollis eros in tellus fermentum, vitae tristique justo finibus.
-Sed quis vehicula nibh.
-Etiam nulla justo, pellentesque id sapien at, semper aliquam arcu.
-Integer at commodo arcu.
-Quisque dapibus ut lacus eget vulputate.
+	\includegraphics[scale=0.3]{Figures/result3.png}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.3]{Figures/result3-1.png}
+\end{figure}
 

### 2019-10-30 Manuscript/main.tex
Finishing process

@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.3]{Figures/result1.png}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.3]{Figures/result1-1.png}
-\end{figure}
+Using the algorithm above, we applied it to a set of networks examples before its proper application on the \textit{Escherechia Coli} genetic regulatory network data.
+The reason for that is merely to show that the not just the algorithmic approach chosen is consistent but the written code per si is correctly implementated.
+For each network, we have a adjacency list containing all the directed connections between the nodes and for each connection we have a string defining the type of regulation of a specific link, where here, considering the genetic regulation context, the types can be positive, negative or dual.
+The first three examples are all small networks, containing at most $48$ nodes, and so all can be used to test the correctness of the algorithm applied.
+For that three examples we show the network drawing and their fibers distribution identified as the result of the algorithm.
+
+The first example is showed at the figure \ref{fig:result1}.
+This network is disconnected, containing two main weakly connected components, and contains only positive regulation between the interactions between the genes, showing the simpler case where the connections between nodes in a network are all of the same type.
+In this case, we find five non-trivial fibers, that is, fibers with size larger than one.
 
@@
 	\centering
+	\subfloat[]{{\includegraphics[scale=0.3]{Figures/result1.png}}}
+	\qquad
+	\subfloat[]{{\includegraphics[scale=0.3]{Figures/result1-1.png}}}
+	\caption{}
+	\label{fig:result1}
+\end{figure}
+
+At the end of the algorithm, all the fibers identified are input-tree stable with respect to all fibers in the network, including the fiber itself.
+Then, labelling each fiber by an index or color we can then construct the fibration building blocks through the calculation of the fundamental class number $n$ and through the subclass number $l$.
+Again, a fibration building block is defined as the nodes inside the fiber as well as the $l$ external nodes that directly regulates at least one node of the current fiber.
+By that, we calculate the fundamental class number $n_k$ of the fiber $k$ by constructing the adjacency matrix $A_{ij}^{k}$ of its fibration building block and then calculating the largest eigenvalue of it.
+The value of $n$ quantifies the information loops of the fibration building blocks and can be either a integer or fractal golden ration.
+
+Labelling the resulted fiber distribution, we obtain the following fibration classification for each fibratiion buuilding block of the network containing more than one node:
+
+\begin{figure}[!ht]
+    \centering
+    \subfloat[]{{\includegraphics[scale=0.22]{Figures/result1-label.png}}}
+    \qquad
+    \begin{tabular}[b]{cc}\hline
+      Table head & Table head \\ \hline
+      Some values & Some values \\
+      Some values & Some values \\
+      Some values & Some values \\
+      Some values & Some values \\
+      Some values & Some values \\
+      Some values & Some values \\ \hline
+    \end{tabular}
+    %\captionlistentry[table]{A table beside a figure}
+    %\captionsetup{labelformat=andtable}
+    %\caption{A table beside a figure}
+\end{figure}
+
+The second example exhibits a connected component containing $N = 21$ nodes, where all the three type of regulation are present.
+For this network we find the total of eleven fibers, where just six are fibers containing more than one node in it.
+As we can notice, for two arbitrary nodes be in the same fiber they must not just receive the same number of inward connections but the same number of each type of inward connections, this way receive the equivalent information from the rest of the network.
+We can see this for the example of the fibers $4$ e $5$, where even though both receives two links from the same central node, the fibers receives different types of information from that node, meaning that they are not the equivalent fibers.
+
+\begin{figure}[H]
+	\centering
 	\includegraphics[scale=0.3]{Figures/result2.png}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
-	\includegraphics[scale=0.3]{Figures/result2-1.png}
+	\includegraphics[scale=0.3]{Figures/result2-label.png}
 \end{figure}
 
-\begin{figure}[h]
+If we consider the fiber $3$, besides the inner autoregulation loop we have a loop information going outside the fiber and going back through an external regulator inside the fiber $1$.
+In cases like this the branching ratio of the fiber has a fractal value represented by a golden ratio $\phi_d$ resulted a loop information represented by a fibonacci sequence.
+This way, fiber $3$ can be classified by the values $| \phi_d, l = 2 \rangle$ where the fiber has two external regulator nodes.
+The fibration classification for the non-trivial fibers is showed in the table \ref{asdas}.
+
+\begin{table}
 \centering
-	\includegraphics[scale=0.3]{Figures/result3.png}
+\begin{tabular}[b]{cc}\hline
+	Table head & Table head \\ \hline
+	Some values & Some values \\
+	Some values & Some values \\
+	Some values & Some values \\
+	Some values & Some values \\
+	Some values & Some values \\
+	Some values & Some values \\ \hline
+  \end{tabular}
+\end{table}
+
+Before applying the algorithm for the whole network, we chose, for the finality of visualization and testing, to apply first the algorithm for a weakly connected component of the \textit{E.
+Coli} network.
+The same network is showed at the supplementary information from \cite{fibration2019}.
+The fiber distribution found is consistent with the one presented at \cite{fibration2019}, presenting the total of fifteen non-trivial fiber groups as shown in figure \ref{fig:result3-1}.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.27]{Figures/result3.png}
+	\caption{}
+	\label{fig:result3}
 \end{figure}
-\begin{figure}[h]
+\begin{figure}[H]
 	\centering
-	\includegraphics[scale=0.3]{Figures/result3-1.png}
+	\includegraphics[scale=0.27]{Figures/result3-1.png}
+	\caption{}
+	\label{fig:result3-1}
 \end{figure}
+
+The connected component showed at the figure \ref{fig:result3} is a representation of a component in the whole regulatory network of the \textit{Escherichia Coli} bacteria and the resulted fibers shows just a portion of the whole fibers pattern.
+In the table X we give the classification for each fibration building block obtained for the whole bacteria network, including of course the fibers presented in the figure \ref{fig:result3-1}.
+In total, we have found $84$ non-trivial fiber groups containing a total of 462 nodes, obtaining a characteristic fiber statistics for the \textit{Escherichia Coli} network data.
+To guarantee the correctness of the fiber distribution found we calculate after the application of the refinement partitioning algorithm the information received for each node inside a fiber and compares if each one process equivalent information.
+
+The statistics concerning the number of each fibration block on the network is given in the table X, showing \textcolor{red}{describe the pattern of the statistics of the table that concerns the bacteria fiber statistics}.
 

### 2019-10-30 Code/FiberColor.c

@@ -1,529 +1,0 @@
-/*  The code given here has the aim to determine the minimal balanced color classes to identify
-    the fibration building blocks of a directed network. The theory concerning the graph fibration
-    morphism and its application on biological networks are detailed, respectively, mainly in the
-    paper of Boldi and Vigna (2001) and in the paper of Morone et. al. (2019, to be published). Concerning
-    the algorithm reproduced in this code, one should refer to the work of Cardon and Crochemore (1982).
-
-    The resulted fibers represent, for each fiber, the set of nodes that are isomorphic under a graph
-    fibration morphism, i. e., all nodes belonging to the same fiber has the same information input-tree.
-
-    -----------------------------------------------------------------------------------------------------
-
-    The code has one command line argument, requiring the common identifier for two files: one single-line file 
-	containing a integer number representing the number of nodes in the network, and a 'ARGedgelist.dat' file containing 
-	all the directed links between nodes (3 columns -> Pointing Node/ Pointed Node/ Type of regulation).
-
-    The result is stored in two arrays: 'nodecolor' and 'edgecolor'. Each array store the color of each
-    component (node or link) and, thus, gives all the information needed, together with the files, for the
-    base graph construction.
-
-    Author: Higor da S. Monteiro - Departament of Physics/Universidade Federal do Ceará (UFC)
-*/
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <math.h>
-#include <gsl/gsl_eigen.h>
-#include "graphdef.h"   	// Personal module containing helpful functions to handle with network data and other common operations.
-#define SEQSIZE 500     	// It's possible that the size of the string sequences should be larger for larger networks.
-
-int nfibers;
-
-////////////////////////////////////////////////////////////////
-struct strseq
-{
-    int node;
-    char strseq[SEQSIZE];
-	//char colorseq[SEQSIZE];       
-};
-typedef struct strseq STRSEQ;
-
-struct colorseq
-{
-    int color_index;
-    char strseq[SEQSIZE];
-};
-typedef struct colorseq COLORSEQ;
-
[…]

### 2019-10-30 Code/RefineToFiber.c

@@ -409,28 +409,27 @@ void PREPROCESSING(BLOCK** P, BLOCK** NonP, PART** Null_Part, Graph* graph, int 
 int main(int argv, char** argc) 
 { 
 	int N, M;                         	// Number of nodes and edges of the network.
-	char netsize[100] = "../Data/";     // File containing (one line) the number of nodes in the network.
 	char net_edges[100] = "../Data/";   // File containing all the directed links in the network.
 	char nodename[100] = "../Data/";	// File containing all the nodes name.
-	strcat(netsize, argc[1]);
-	strcat(netsize, "Ngenes.dat");
 	strcat(net_edges, argc[1]);
 	strcat(net_edges, "edgelist.dat");
 	strcat(nodename, argc[1]);
 	strcat(nodename, "nameID.dat");
-                                                          
-    // Defines the size of the network.
-	FILE* UTIL = fopen(netsize, "r");
-	if(UTIL==NULL) printf("ERROR IN FILE READING\n");
-	fscanf(UTIL, "%d\n", &N);
-	fclose(UTIL);
-    ///////////////////////////////////////////////////
+
+	// From the edgelist get the number of nodes in the network.
+	N = GetNodeNumber(net_edges);
+
+	//// Check if it is necessary to check for the file containing names for the nodes ////
+	int nodename_bool;
+	if(strcmp(argc[2], "-y")==0) nodename_bool = 1;
+	else nodename_bool = 0;
+	///////////////////////////////////////////////////////////////////////////////////////
 
     // Creates the network for N nodes and defines its structure with the given 'edgelist.dat' file.
 	int** edges;
-	Graph* graph = createGraph(N, nodename);
+	Graph* graph = createGraph(N, nodename, nodename_bool);
 	edges = defineNetwork(edges, graph, net_edges);
-	printf("%d\n", graph->size);
+	//printf("%d\n", graph->size);
 	///////////////////////////////////////////////////////////////////////////////////////
 
 	/////////////////////// COARSEST REFINEMENT PARTITION ALGORITHM ////////////////////////
@@ -460,15 +459,13 @@ int main(int argv, char** argc)
 		S_SPLIT(&partition, CurrentSet, graph, &qhead, &qtail);
 	}
 	int size = GetPartitionSize(partition) + GetPartitionSize(null_partition);
-	int nfibers = GetFiberNumber1(partition, null_partition);
[…]

### 2019-10-30 Code/graphdef.h

@@ -1,571 +1,0 @@
-/*	This module contains a compilation of utility functions of some
-	type of situations. Specially, here we define the functions necessary
-	to construct directed and undirected networks. 
-
-	Author: Higor da S. Monteiro - Universidade Federal do Ceará
-*/
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <math.h>
-
-////////////////////////////////////////////////////////////////////
-/// Structures to create and define a directed, unweighted graph ///
-////////////////////////////////////////////////////////////////////
-
-// Define a graph containing 'size' nodes
-struct Graph
-{
-	// each node has its adjancency list
-	int size;
-	struct adjList* array;
-};
-typedef struct Graph Graph;
-
-struct adjList
-{
-	struct NodeAdj* head_in;
-    struct NodeAdj* head_out;
-};
-typedef struct adjList AdjList;
-
-// Structure to define the adjacency list of a node
-struct NodeAdj
-{
-	int neighbor;
-    int regulator;
-	struct NodeAdj* next;
-    //struct NodeAdj* next_out;
-};
-typedef struct NodeAdj NodeAdj;
-
-NodeAdj* createNode(int neigh, int type_link)
-{
-	NodeAdj* newnode = (NodeAdj*)malloc(sizeof(NodeAdj));
-	newnode->neighbor = neigh;
-	newnode->next = NULL;
-    newnode->regulator = type_link;
-    //newnode->next_out = NULL;
-	return newnode;
-}
-
-extern Graph* createGraph(int N)
-{
-	Graph* graph = (Graph*)malloc(sizeof(Graph));
-	graph->size = N;
-
-	// Array of NodeAdj's
-	graph->array = (AdjList*)malloc(N*sizeof(AdjList));
-
-	int j;
-	for(j=0; j<N; j++) { graph->array[j].head_in = NULL; graph->array[j].head_out = NULL; }
-	return graph;
-}
-
-void addEdges(int** edges, Graph* graph, int* regulator, int nE)
-{
-	int index, j, node1, node2, reg;
-	
-	for(j=0; j<nE; j++)
-	{
-		// 'node1' -> 'node2' directed link.
-        node1 = edges[j][0];
-		node2 = edges[j][1];
-		reg = regulator[j];
-
[…]

### 2019-10-30 Code/structforfiber.h

@@ -91,7 +91,7 @@ extern void PrintInNeighbors(Graph* graph, int node, int N)
 	printf("Node %d: ", node);
 	while(Inode)
 	{
-		printf("%d ", Inode->neighbor);
+		printf("%d(type:%d) ", Inode->neighbor, Inode->type_link);
 		Inode = Inode->next;
 	}
 	printf("\n");

### 2019-10-30 Code/testdatast.c

@@ -1,63 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <math.h>
-#include <gsl/gsl_eigen.h>
-#include "graphdef.h"   	// Personal module containing helpful functions to handle with network data and other common operations.
-#define SEQSIZE 500     	// It's possible that the size of the string sequences should be larger for larger networks.
-
-int nfibers;
-
-struct aux
-{
-	int color;
-	int number;
-};
-typedef struct aux AUX;
-
-struct strseq
-{
-    int node;
-    Node* strseq;       
-};
-typedef struct strseq STRSEQ;
-
-STRSEQ* INITSEQ(STRSEQ* seqlist, int N)
-{
-	int i;
-	for(i=0; i<N; i++) seqlist[i].strseq = NULL;
-	return seqlist;
-}
-
-int main(int argv, char** argc) 
-{ 
-    int N, i;                              // Number of nodes in the network.
-                                                          
-	Node* List = NULL;
-	STRSEQ* seqlist = (STRSEQ*)malloc(10*sizeof(STRSEQ));
-	seqlist = INITSEQ(seqlist, 10);
-
-	int arr[] = {5, 3, 2, 9, 4, 1, 8, 6, 7, 0};
-
-	for(i=0; i<10; i++)
-	{
-		List = push_data(List, arr[i]);
-		seqlist[i].node = i;
-	}
-	
-	Node* temp = List;
-	while(temp)
-	{
-		printf("%d ", temp->data);
-		temp = temp->next;
-	}
-
-	SelectionSort(List);
-	temp = List;	
-	while(temp)
-	{
-		printf("%d ", temp->data);
-		temp = temp->next;
-	}
-
-}

### 2019-10-30 Code/utilsforfiber.h

@@ -29,7 +29,7 @@ NodeAdj* createNode(int neigh, int type_link)
 	return newnode;
 }
 
-extern Graph* createGraph(int N, char* nodenames)
+extern Graph* createGraph(int N, char* nodenames, int name_bool)
 {
 	Graph* graph = (Graph*)malloc(sizeof(Graph));
 	graph->size = N;
@@ -46,13 +46,16 @@ extern Graph* createGraph(int N, char* nodenames)
 
 	int nodeID;
 	char tempname[60];
-	FILE* NAMES = fopen(nodenames, "r");
-	for(j=0; j<N; j++)
-	{		
-		fscanf(NAMES, "%s\t%d\n", &tempname, &nodeID);
-		strcpy(graph->array[nodeID].gene_name, tempname);
+	if(name_bool==1)
+	{
+		FILE* NAMES = fopen(nodenames, "r");
+		for(j=0; j<N; j++)
+		{			
+			fscanf(NAMES, "%s\t%d\n", &tempname, &nodeID);
+			strcpy(graph->array[nodeID].gene_name, tempname);
+		}
+		fclose(NAMES);
 	}
-	fclose(NAMES);
 	return graph;
 }
 
@@ -112,10 +115,73 @@ extern int** defineNetwork(int** edges, Graph* graph, char* filename)
     
     return edges;
 }
+
+extern int GetNodeNumber(char* edgefile)
+{
+	FILE *EDGE_FILE = fopen(edgefile, "r");
+	if(EDGE_FILE==NULL) printf("ERROR in file reading");
+
+	int max = -1;
+	int i, j;
+	char type[20];
+	int r = 1;
+	int nlink = 0; // number of links.
+	while(r) // Calculates the number of lines in the file
+	{
+		r = fscanf(EDGE_FILE, "%d\t%d\t%s\n", &i, &j, &type);
+		if(r==EOF) break;
+		if(i>max && i>j) max = i;
+		else if(j>max && j>i) max = j;
+	}
+	return (max+1);
+}
 ///////////////////////////////////////////////////////////////////////////////
 ///////////////////////////////////////////////////////////////////////////////
 
 /////////////////////////// GRAPH OPERATIONS ////////////////////////////////
+int cmpfunc (const void * a, const void * b) {
+   return ( *(int*)a - *(int*)b );
+}
+
+struct storetype
+{
+	int node;
+	int type;
+};
[…]

### 2019-10-31 Manuscript/main.tex
final art

@@
 
-Fibration building blocks of a information flow network represent the sets of nodes that are symmetric with respect to the processing of information, that is, the sets of nodes that process equivalent information.
-Here, we have reproduced important results concerning the identification and classification of the fibration building blocks of directed networks, constructed from real network data.
-More specifically, using the transcriptional regulatory network data of the \textit{Escherichia Coli} bacteria, we quantify the clusters of nodes that synchronously process equivalent information and then we classify these clusters, called network fibers, based on its specific topological features.
-This way, in order to consistently present the obtained results, in this report we first give a brief description of the theory concerning the graph fibration morphism and its main definitions related to information flow symmetries.
-Next, we detail the methods adopted to correctly identify and classify the network fibers.
-More specifically, to establish an optimal framework, I show the implementation details of the Minimal Balanced Coloring algorithm used to find the corresponding fibers in the network, presenting a slightly improvement for the algorithm complexity and its implementation.
-At last, showing the proper methods for data preparation, I describe the results obtained concerning the fiber statistics for the specific case of the \textit{Escherichia Coli} regulatory network, to properly compare with the recent results presented at \textit{Morone et.
+Fibration building blocks of information-processing networks represent the sets of nodes that are symmetrical with respect to the processing of input signals received from the rest of the network, defining this way the classes of nodes that process equivalent information.
+In this report, I reproduced relevant results concerning the identification and classification of the fibration building blocks of directed networks, constructed from real systems data.
+More specifically, using the transcriptional regulatory network data from the \textit{Escherichia Coli} bacteria, I quantify the clusters of nodes in the network that synchronously process equivalent information, and then I classify these clusters, called fibers, based on its specific topological features.
+Here, to consistently present the obtained results, I briefly introduce the theory concerning the graph fibration morphism and its main definitions related to information processing symmetries.
+Then, I detail the computational methods adopted to the identification of the network fibers, presenting a slightly different algorithmic approach for the problem in hand, based on the general relational refinement partitioning algorithms described by Paige and Tarjan in 1987.
+After defining the implementation details of the graph refinement algorithm I lastly apply the method for trial network examples and then for the constructed genetic regulatory network of \textit{Escherichia Coli}, noticing a visible discrepancy between the results obtained by the methods described in this report and the results exhibited in the most recent literature given at \textit{Morone et.
 al.} (2019).
+The results showed in this report, concerning the fibers distribution over the network, are tested and verified to support the assertion that the algorithm used captures the correct minimal fibration.
 
@@
 
-In order to identify the correct distribution of network fibers we have to find a efficient procedure to split the network in different disjoint partitions, in which all nodes from a same partition should receive information from the same other partitions.
-To do that, we treat our problem as the same of find the coarsest relational refinement partitioning for the given network.
-In this section, we detail the optimal algorithm used to find this coarsest partitioning in a context of graph fibrations and show the relative simple implementation of this method.
+To identify the correct distribution of fibers over the network it is necessary to define an efficient procedure to split the nodes into different disjoint partitions, from which all nodes inside the same partition must receive equivalent information from all other partitions.
+To do that, we treat our problem as the same as finding the coarsest relational refinement partitioning of a set of elements that have a binary relation between them.
+Since a network is completely defined by a set of node elements and a set of edges that comprehend all the binary relations, this approach can be used.
+Therefore, in this section, I detail the optimal algorithm used to find this coarsest partitioning in the context of graph fibrations and show the relatively simple implementation of this method.
+
+The algorithm used in this project is a slightly modified version of the algorithm presented by Paige and Tarjan \cite{Tarjan1987}, \ having a runtime complexity of $\mathcal{O}(M\log N)$, where $M$ and $N$ are, respectively, the number of edges and nodes in the network, being almost linear with the size of the network.
+It is important to note that this algorithm has the same runtime order than the algorithm from Cardon and Crushemore \cite{Cardon1982}, in which the algorithm of minimal fibration from \cite{fibration2019} is based.
+However, the algorithm presented by Paige and Tarjan has a simpler implementation and smaller prefactors, exhibiting a better approach to our problem.
+Even though the algorithm has wider general applications, here I give the details of the algorithm implementation to the application for a network, so that I introduce the necessary definitions within this context.
 
@@
 
-The algorithm used in this project is a slightly modified version of the algorithm presented by Paige and Tarjan \cite{Tarjan1987}, \ having a time complexity of $O(M\log N)$, being very efficient for sparse networks.
-This algorithm has the same runtime order than the algorithm from Cardon and Crushemore \cite{Cardon1982}, but it has a simpler implementation and smaller prefactors, exhibiting a better approach to our problem.
-Even though the algorithm applies for general situations, here we give the details of the algorithm to its application for a network, so we introduce the necessary definitions within this context.
+A network $G(V, E)$ is completely defined by the sets of the nodes elements $V$ and the set of the edges $E$.
+The network has $N = |V|$ nodes that can have connections with one another defined by the set $E$, which contains $M = |E|$ ordered pair of nodes, denoting the directed links between the network nodes.
+Considering the network, we can define a graph partition $\bar{P}$ over $V$ as a set of pairwise disjoints subsets of $V$ whose union is all $V$, that is
+\begin{equation}
+	\bar{P} = \bigcup_{i} P_i
+\end{equation}
+where $P_i$ are the elements of the partition $\bar{P}$, called blocks.
+Considering this, if we take an additional graph partition $\bar{Q}$ that has the property that all of its blocks are contained in a block of $\bar{P}$, we say that $\bar{Q}$ is a refinement partition of $\bar{P}$.
 
-A network $G$ is completely defined as $G(V, E)$ by the sets of nodes $V$ and of the connections $E$.
-The network has then $N = |V|$ nodes that can have connections with one another defined by the set $E$ containing $M = |E|$ ordered pair of nodes, denoting the directed connections between the network nodes.
-Over the network, we can define a graph partition $P$ of $V$ as a set of pairwise disjoints subsets of $V$ whose union is all $V$
-\begin{equation}
-	P = \bigcup_{i} P_i
-\end{equation}
-where $P_i$ are the elements of the partition $P$, in which we call it blocks.
-Within this context, if we consider an additional graph partition $Q$ that has the property that all the block of $Q$ is contained in a block of $P$, we say that $Q$ is a refinement partition of $P$.
+Moreover, for a block $B \in \bar{P}$, we say that the block $B$ is stable with respect with a set $S$ if either all elements of $B$ connects with an element of $S$ or none element of $B$ points to any element of $S$.
+The stability partition concept is central to the problem of relational coarsest refinement partitioning and can be easily extended to graph problems, where the coarsest graph partition problem is that of finding, for a given set of connections $E$ and an initial partition $\bar{P}$ over $V$, the coarsest stable refinement of $\bar{P}$, i.
+e., the minimal number of disjoint blocks subsets of $V$ that forms a stable refinement of $\bar{P}$.
 
-Considering a block $B$ in $P$, we say that the block $B$ is stable with respect with a set $S$ if or all elements of $B$ connects an element of $S$ or none element of $B$ points to any element of $S$.
-By that we define that a graph partition $P$ of $V$ is stable if it is stable with respect with its own blocks.
-Having defined that, the graph coarsest partition problem is that of finding, for a given set of connections $E$ and initial partition $P$ over $V$, the coarsest stable refinement of $P$.
-
-Considering all that, for the proper identification of the fibers on the network we have to construct a stable graph partition that is equivalent to the coarsest (minimal number of blocks) refinement of the network with respect to the information flow passing through each node.
-For that, we need to extend the concept of stability over the partition for one that accounts for the information received by each block of the partition.
-Thus, in order to identify the clusters with isomorphic input-tree for all their nodes, we require that the partition should be not only stable but input-tree stable.
-That means that for a subset $S \subseteq$ $V$, a graph partition $P$ over the network $G(V, E)$ is input-tree stable with respect to $S$ if for all the block $B \in P$, the equality
+Considering the stability of partitions, for a proper identification of the network fibers as defined in the above section we ought to construct a stable graph partition that is equivalent to the coarsest refinement of the network (minimal number of blocks) with respect to the information processing of each node.
+For that goal, we need to extend the concept of stability over partitions for the case that accounts for the information processed by each block of the partition.
+Therefore, to identify the group of nodes with isomorphic input-tree, we require that the partition should be not only stable but \textbf{input-tree stable}.
+That means that for a subset $S \subseteq$ $V$, a graph partition $\bar{P}$ over the network $G(V, E)$ is input-tree stable with respect to $S$ if for all the block $B \in \bar{P}$, the following equality is satisfied for all the elements $x$, $y \in B$:
 \begin{equation}
@@
 \end{equation}
-is satisfied for all the elements $x$, $y \in B$.
+where $E(\{x\})$ and $E^{-1}(\{x\})$ represents, respectively, the set of nodes that directly receives information from $x$, and the set of nodes that sends information, via a direct link, to $x$.
 
-This way, we can benefit from the stability properties \cite{Tarjan1987} to construct a refinement algorithm step that can obtains, through a finite number of steps, a input-tree stable partition from an initial unstable partitioning of the network.
-With this, given a subset $S \subseteq V$, the refinement step has the effect to refine the current partition, unstable with respect to $S$, by replacing it for a new partition now stable with $S$.
-For that, we define a split function \textit{I-split($S$, $P$)} that receive as input the current partition and a set $S$ and results as output a new input-tree stable partition with respect to $S$.
-That function benefits from two major properties of stability (and input-tree stability): the stability inheritance by refinement and by union of sets.
-Since this refinement inheritance, a given set $S$ can be used only once by the function \textit{I-split}, for which after all other refinement will be stable with respect to $S$.
+This way, we can benefit from the stability properties \cite{Tarjan1987} to construct a refinement algorithm step that can achieve, through a finite number of steps, a input-tree stable partition from an initial unstable partitioning of the network.
+This way, given a subset $S \subseteq V$, the refinement step has the effect to refine the current partition, input-tree unstable with respect to $S$, by replacing it for a new partition, now input-tree stable for $S$.
+With that objective, we define a split function \textit{I-split($S$, $\bar{P}$)} that receive as input the current partition and a set $S$ and returns as output a new input-tree stable partition with respect to $S$.
+Favorably, that function benefits from two major properties of stability (and input-tree stability): the stability inheritance by refinement and by union of sets.
+By reason of this refinement inheritance, a given set $S$ can be used only once by the function \textit{I-split}, guaranting that the partition, after all other refinement steps, will maintain as stable with respect to $S$.
 Moreover, since stability is inherited under union of sets $S$, after sets are used in \textit{I-split}, their union cannot be used for the function.
-With all this considered, the essence of the algorithm can be stated as
+Considering all these properties, the essence of the refinement algorithm can be stated as
 
 \begin{quotation}
-	Find a set $S$ in which the current partition $P$ is input-tree unstable.
-Replace $P$ by the output of \textit{I-split($S$,$P$)}.
+	\textbf{Refinement Algorithm}: Find a set $S$ in which the current partition $\bar{P}$ is input-tree unstable.
+Replace $\bar{P}$ by the output of \textit{I-split($S$,$\bar{P}$)}.
 Guarantees that the set $S$ or unions of used sets never be used again.
@@
 
-Since the finest partitioning possible is the one in which every node is itself a block, the refinement step can be proceeded at most $N-1$ times, guaranting that the algorithm terminates with the correct answer, since stability is inherited by the refinement process.
-However, to guarantees that the algorithm has a optimal runtime we have to find a efficient way to select the appropriate sets to the refinement step, without choosing repeated sets.
-Fortanately, this can be easily done for the construction of a input-tree stable partition.
+Since the finest partitioning possible is the one in which every node is itself a block, the refinement step may be proceeded at most $N-1$ times, guaranting that the algorithm terminates with the correct answer, since stability is inherited by the refinement process.
+However, to guarantees that the algorithm has a optimal runtime we have to find a efficient way to select the appropriate sets to the refinement step, without choosing repeated ones.
+Fortunately, this can be easily done for the construction of a input-tree stable partition.
 
-Given a set $S$ of nodes from the network $G$ and a given input-tree unstable graph partition $Q$, the blocks $B \in Q$ that are input-tree unstable with respect to $S$ can be splitted in several blocks $B_j$ to have a stable input-tree for $S$.
+Given a set $S$ of nodes from the network $G(V, E)$ and a given input-tree unstable graph partition $\bar{P}$, the blocks $B \in \bar{P}$ that are input-tree unstable with respect to $S$ can be splitted into several blocks $B_j$ that will be stable input-tree with respect to $S$.
 Then, each splitted block will have the property defined by
@@
 \end{equation}
-where the number of splitted block must be larger than one to a proper split process take place.
-Then, for each unstable block $B \in Q$ all the splitted block, except the largest one, can be put a queue to be used ahead in the algorithm as a refinement set.
+where the number of splitted block must be larger than one to a proper splitting process take place.
+Then, for each unstable block $B \in \bar{P}$ all the splitted block, except the largest one, can be put at the back of a queue to be used ahead in the algorithm as a refinement set.
 This ensures that none repeated sets or union of repeated sets can be used during the algorithm exeecution.
 
-Having said all that, the complete algorithm to find the correct network fibers of a network $G(V, E)$ consists in initializing a graph partition $Q$ over all nodes from $V$ except the nodes that do not receive information from any other node, in which each one of these will be defined as isolated fibers already in the beginning of the algorithm.
-The partition $Q$ is defined as one block containing all the other nodes in the network.
-The algorithm maintains a queue $L$ of possible refinement sets, initially containing the single block of $Q$ and all the isolated blocks defined at the beginning.
+Finally, having said all that, the complete algorithm to find the correct network fibers of a network $G(V, E)$ consists in initializing a graph partition $\bar{P}$ over all nodes from $V$ except the nodes that do not receive information from any other node, in which each one of these will be defined as isolated fibers already in the beginning of the algorithm.
+The partition $\bar{P}$ is defined as one block containing all the other nodes in the network.
+The algorithm maintains a queue $L$ of possible refinement sets, initially containing the single block of $\bar{Q}$ and all the isolated blocks defined at the beginning.
 Then, we proceed as
 \begin{quotation}
-	Remove from $L$ its first set $S$. Replace $Q$ by the \textit{I-split($S$, $Q$)}. Whenever a block $B \in Q$ splits into two or more nonempty blocks, add all but the largest to the back of $L$.
+	\textbf{Coarsest Refinement Algorithm}: Remove from $L$ its first set $S$.
+Replace $Q$ by the \textit{I-split($S$, $Q$)}.
+Whenever a block $B \in Q$ splits into two or more nonempty blocks, add all but the largest to the back of $L$.
 \end{quotation}
 And this process is repeated until the queue $L$ is empty.
-At this point, the resulted partition $Q$ represent the coarsest input-tree stable partitioning of the network $G(V, E)$, where each block represents a network fiber with all its nodes having isomorphic input-trees.
+At this point, the resulted partition $\bar{P}$ represents the coarsest input-tree stable partitioning of the network $G(V, E)$, where each block represents a network fiber with all its nodes having isomorphic input-trees.
 

### 2019-10-31 Code/minimalfiber.c

@@ -9,30 +9,39 @@
 	that receive equivalent information from other fibers on the network. Moreover, after the proper identification of the 
 	building blocks, we classify each one based on specific topological features, represented by two parameter: |n,l>.
 
-	---------------------------------------------------------------------------------------------------------------
+	----------------------------------------------------------------------------------------------------------------------------
 
-	The code receives ONE command line argument, that is the common identifier for two required files: one single-line 
-	file containing a integer number "%d\n" representing the number of nodes in the network ('ARG1Ngenes.dat'), and a edgelist 
-	file ('ARG1edgelist.dat') containing all the directed links between nodes (3 columns: "%d\t%d\t%s\n" -> Pointing Node/ Pointed Node/ 
-	Type of regulation). For gene regulatory networks, the type of the regulation can be positive, negative or dual.
+	The code receives TWO commands line arguments. The first one is the string identifier for the edgelist file 
+	('ARG1edgelist.dat') containing all the directed links between nodes (3 columns: "%d\t%d\t%s\n" -> Pointing Node/ 
+	Pointed Node/ Type of regulation). For gene regulatory networks, the type of the regulation can be 'positive', 'negative' 
+	or 'dual'. The second argument is a flag used to signal the code to properly get the gene names of each node number. For 
+	that, it is necessary an auxiliary file called 'ARG1genename.dat' containing two columns (formatted as "%s\t%d\n" -> Gene 
+	name/ Gene ID number). Thus, if there is a gene name file, the code will properly link all the node numbers with their 
+	corresponding name if 'ARG2' is passed as '-y', otherwise just the node numbers is stored for each node.
 
-	The result is stored in two arrays: 'nodefiber'. Each array store the color of each component (node or 
-	link) and, thus, gives all the information needed, together with the files, for the base graph construction.
+	The result is stored in the 'partition' and 'null_partition' structures, together with the 'graph' structure. To check 
+	which data each one of this structures stores the user can refer to the 'structforfiber.h' module. In general, a partition 
+	stores all the fiber blocks and each block stores the list of node that belongs to it. The values of n and l are stored in 
+	'partition' and 'null_partition' for each block.
+
+	------------------------------------------------------------------------------------------------------------------------------
 
 	Author: Higor da S. Monteiro
 	Email: higor.monteiro@fisica.ufc.br
[…]

### 2019-10-31 Manuscript/main.tex
fundamental class calculation

@@
 
-A network $G(V, E)$ is completely defined by the sets of the nodes elements $V$ and the set of the edges $E$.
+A network $G(V, E)$ is completely defined by the sets of the nodes elements $V$ and the set of the arcs $E$.
 The network has $N = |V|$ nodes that can have connections with one another defined by the set $E$, which contains $M = |E|$ ordered pair of nodes, denoting the directed links between the network nodes.
@@
 
-Finally, having said all that, the complete algorithm to find the correct network fibers of a network $G(V, E)$ consists in initializing a graph partition $\bar{P}$ over all nodes from $V$ except the nodes that do not receive information from any other node, in which each one of these will be defined as isolated fibers already in the beginning of the algorithm.
+Finally, the complete algorithm to find the correct network fibers of a network $G(V, E)$ consists in initializing a graph partition $\bar{P}$ over all nodes from $V$ except the nodes that do not receive information from any other node, in which each one of these will be defined as isolated fibers already in the beginning of the algorithm.
 The partition $\bar{P}$ is defined as one block containing all the other nodes in the network.
-The algorithm maintains a queue $L$ of possible refinement sets, initially containing the single block of $\bar{Q}$ and all the isolated blocks defined at the beginning.
+The algorithm maintains a queue $L$ of possible refinement sets, initially containing the single block of $\bar{P}$ and all the isolated blocks defined at the beginning.
 Then, we proceed as
@@
 	\textbf{Coarsest Refinement Algorithm}: Remove from $L$ its first set $S$.
-Replace $Q$ by the \textit{I-split($S$, $Q$)}.
-Whenever a block $B \in Q$ splits into two or more nonempty blocks, add all but the largest to the back of $L$.
+Replace $\bar{P}$ by the \textit{I-split($S$, $\bar{P}$)}.
+Whenever a block $B \in \bar{P}$ splits into two or more nonempty blocks, add all but the largest to the back of $L$.
 \end{quotation}
@@
 At this point, the resulted partition $\bar{P}$ represents the coarsest input-tree stable partitioning of the network $G(V, E)$, where each block represents a network fiber with all its nodes having isomorphic input-trees.
+The figure \ref{fig:split} displays the splitting operation at the beginning of the refinement algorithm for a small network example.
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.3]{Figures/test.png}
+	\caption{A refinement step for the split function.
+Receiving the input partition $\bar{P}$ and a refinement set $S$, we identify the input-tree unstable blocks and split them into input-tree blocks with respect to $S$.
+Due to the refinement inheritance stability property, refining the resulted partition $\bar{P}$ with respect to other sets $S'$, that are not equal to $S$ or a union of already used sets $S$, guarantees the input-tree stability to $S$ during all the following algorithm steps.}
+	\label{fig:split}
+\end{figure}
 
@@
 
-We apply the above algorithm in the genetic regulatory network of the \textit{Escherichia Coli} bacteria.
-We obtain the genetic E.
-Coli network through its transcriptional regulatory interactions data, where each gene is regulated by a transcription factor protein.
-Since a transcription factor production in the cell is regulated by a gene, we can define a directed connection between two genes if a gene regulates the production of a transcriptional factor, which it regulates another gene.
-Since a transcription factor can be either an activator(positive) or repressor(negative), or even behaves as both(dual), the links between genes can carry different types of messages.
-Because of that, it is important that the partitioning algorithm accounts the type of message to construct appropriate input-trees for the network fibers partition.
-Therefore, for a proper application of the algorithm on the \textit{Escherichia Coli} genetic network, we label each node uniquely, either as number or string names, and also each link with the type of connection between genes.
+Next, I apply the above algorithm for the genetic regulatory network of the \textit{Escherichia Coli} bacteria.
+The obtention of this genetic network is through the transcriptional regulatory interaction data, where each gene is regulated by a transcription factor protein.
+Since a transcription factor in the cell is produced by a gene, it is possible to define directed relations between two genes if a gene is responsible for the production of a transcriptional factor, which regulates the other gene.
+Considering that a transcription factor can be either an activator(positive) or repressor(negative), or even behaves as both(dual), the directed links between genes can carry different types of information.
+Because of that, the partitioning algorithm must account for the type of message signals to construct appropriate stable input-trees for the network fibers.
+Therefore, for a proper application of the algorithm on the \textit{Escherichia Coli} genetic network, we label each node uniquely, either as numbers or string names, and also we do the same for each link with the type of connection between two genes.
 
-Considering this context, we explain now how the algorithm should proper be implemented to have an optimal perfomance concerning its runtime complexity.
-After discussing the data structures necessary to deal correctly with data, we design an algorithm recipe to show all the main steps of the process explained above.
-Also, anyone can acess our own personal implementation for genetic regulatory networks in the link \url{https://github.com/higorsmonteiro/fiberblocks} on github platform.
+Given the regulatory directed network $G(V, E)$ to be partitioned in fibers, it is very important for the correctness of the algorithm that the nodes that do not receive any information, that is, the nodes that do not have any inward connections, be preprocessing as isolated blocks in a different partition.
+This means that the initial graph partition $\bar{P}$ must be divided in two different partitions $\bar{P'}$ e $\bar{P''}$, where the first one should contains all the single-node blocks containing the solitaire nodes $v$ for which $| E^{-1}(\{v\}) | = 0$, and the second contains at the beginning of the algorithm a single block containing all the other nodes $w$ in which $| E^{-1}(\{w\}) | \geq 1$.
+The importance of this preprocessing is to guarantee that solitaire nodes do not be put on the same fibers during the refinement steps, since for any subset $S \subseteq V$, the solitaire nodes satisfies the equality $| E^{-1}(\{v\}) \cap S | = 0$.
+Furthermore, even though the blocks of $\bar{P'}$ are used as refinement sets, $\bar{P'}$ is not used by the split function in any step.
+This way, the final graph partition of $G(V, E)$ is the union of $\bar{P'}$ and the result of the refinement partitioning of $\bar{P''}$, that is, the coarsest or minimal input-tree stable partition of $G$.
 
-Given a directed network $G(V, E)$ to be partitioned in fibers, it is very important for the correctness of the algorithm that the nodes that do not receive any information, that is, the nodes that do not have any inward connections, be preprocessing as isolated blocks.
-This means that the initial graph partition $P$ is divided in two different partition $P'$ e $P''$, the first one contained all the single-node blocks containing the solitaire nodes $v$ in which $| E^{-1}(\{v\}) | = 0$, and the second one containing initialing a single block containing all the other nodes $w$ in which $| E^{-1}(\{w\}) | \geq 1$.
-The importance of this preprocessing is to guarantee that solitaire nodes do not be put on the same fibers during the refinement steps.
-Even though the blocks of $P'$ are used as refinement sets, $P'$ is not used by the algorithm.
-Thus, the final partition is the union of $P'$ and the result of the refinement partitioning of $P''$.
+After preprocessing the solitaire nodes, we have to define the data structures for the partition $\bar{Q}$ and its blocks $B$.
+We should define the implementation of a partition by a doubly-linked list of blocks, which allows that deletion of blocks be done in constante time $O(1)$ as long we have the block memory address during the procedure.
+A block is just a structure record containing indexing data along with a doubly-linked list containing all the nodes that belongs to it.
+Together with the queue of blocks $L$, these constructions are the main data structures necessary for an efficient implementation of the refinement partitioning algorithm.
+At the beginning of the algorithm, we enqueue all the blocks of $\bar{P'}$ e $\bar{P''}$ to $L$ (order is not important for the output correctness).
+Then, we start the algorithm initializing a partition $\bar{Q} = \bar{P''}$ and by removing the first element set $S$ of $L$, and we apply the \textit{I-split($S$, $\bar{Q}$)} function to identify the input-tree unstable blocks of $\bar{Q}$ and to split them into input-tree stable blocks with respect to $S$.
+After that, all the splitted blocks are pushed to the end of $L$, with exception the largest resulted blocks for each splitted block.
+As we have mentioned, the algorithm terminates when there is no more sets in $L$.
+This is the whole algorithm, even though the implementation of the \textit{I-split} function might not be so straightforward, since a given block $B$ can be splitted into an arbitrary number of blocks of different sizes.
+Considering this, I propose in the pseudocode \ref{alg:split} an efficient implementation construction to the splitting function.
 
-After the above preprocessing we define the data structures for the partition $Q$ for its blocks $B$.
-A partition is a doubly linked list of blocks, which allows that deletion of blocks be made in constante time $O(1)$ as long we have the block memory address during the procedure.
-A block is just a structure containing indexing data along with a doubly linked list containg all the nodes that belongs to it.
-Together with a queue of blocks $L$, these constructions are the main data structures necessary for an efficient implementation of the refinement partitioning algorithm.
-At the beginning of the algorithm, we enqueue all the blocks of $P'$ e $P''$ to $L$.
-Then, we start the algorithm initializing a partition $Q = P''$ and by removing the top element set $S$ of $L$, then we apply the \textit{I-split($S$, $Q$)} to identify the input-tree unstable blocks of $Q$ and split them into input-tree stable blocks with respect to  $S$.
-This way, all the splitted blocks are push to the end of $L$, with exception the largest resulted blocks for each splitted block.
-As we have mentioned, the algorithm terminates when there is no more sets in $L$.
-Even though this is the whole algorithm, the implementation of the \textit{I-split} function might not be so straightforward, since a given block $B$ can be splitted into an arbitrary number of blocks.
-In respect to that below we propose the following implementation construction to the splitting function:
-
-\begin{algorithm}[h]
+\begin{algorithm}[t]
 	\SetAlgoLined
@@
     \Output{Input tree stable partition $\bar{Q}$ with respect to $S$}
-	%\KwResult{}
 	Initialize $\bar{U}$ as an empty partition\;
@@
 		\textit{enqueue} all blocks $X \in \bar{T}$ in $L$, except the largest one\;
-		\textit{push} all blocks $X \in \bar{T}$ to $\bar{Q}$\;
+		\textit{copy} all blocks $X \in \bar{T}$ to $\bar{Q}$\;
 	}
@@
 	\caption{\textit{I-split} $(S,\bar{Q}, L)$}
+	\label{alg:split}
 \end{algorithm}
 
-In the algorithm recipe above, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output.
-Besides its list of nodes, a block $X$ has another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$.
-This way, a node $w$ belonging to the block to be splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm above.
+In the algorithm \ref{alg:split} above, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output.
+Besides its list of nodes, a block $X$ should have another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$.
+This way, a node $w$ belonging to the block splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm \ref{alg:split}.
+In cases where the type of connections are non-trivial, i.
+e., there is more than one type of message signal, the attribute $X(E)$ can be replaced by a list $X(E(i))$ for each type $i$ of message presented in the network.
+For that situation, the conditional line $7$ must be verified for all types of connnections: $\exists \ X \in \bar{T} : | E_k^{-1}(\{w_i\})\cap S | = X(E(k))$.
 
-Finally, considering all the discussion above, we can explicit the complete algorithm in just a few steps.
+Finally, considering all the discussion and implementation presented above, we can explicit the complete algorithm in just a few basic steps in algorithm \ref{alg:partitioning}.
+
+A concrete implementation of the algorithm in a programming language is presented at the link \url{https://github.com/higorsmonteiro/fiberblocks} together with \textit{E.
+Coli} prepared data and another trial network examples.
+Further information about the application of the codes in other genetic regulatory network data can be found at the same link given.
 
@@
 	\caption{Coarsest Refinement Graph Partitioning}
+	\label{alg:partitioning}
 \end{algorithm}
-
-A concrete implementation of the algorithm in a programming language is presented at the link \url{https://github.com/higorsmonteiro/fiberblocks} together with \textit{E.
-Coli} prepared data and another examples.
-Further information about the application of the codes in other genetic regulatory network data can be found at the same link given.
 
@@
 
-Using the algorithm above, we applied it to a set of networks examples before its proper application on the \textit{Escherechia Coli} genetic regulatory network data.
-The reason for that is merely to show that the not just the algorithmic approach chosen is consistent but the written code per si is correctly implementated.
-For each network, we have a adjacency list containing all the directed connections between the nodes and for each connection we have a string defining the type of regulation of a specific link, where here, considering the genetic regulation context, the types can be positive, negative or dual.
-The first three examples are all small networks, containing at most $48$ nodes, and so all can be used to test the correctness of the algorithm applied.
-For that three examples we show the network drawing and their fibers distribution identified as the result of the algorithm.
+Using the algorithm above, I applied it to a set of trial networks examples before its proper application to the \textit{Escherechia Coli} genetic regulatory network data.
+The reason for that is merely to show that the not just the algorithmic approach chosen is consistent but the written code per se is correctly implemented.
+For each network, I defined a adjacency list file containing all the directed connections between the nodes/genes and for each arc I have a string name defining the type of regulation of that specific link, where here, considering the genetic regulation context, the string types can be ''positive``, ''negative`` or ''dual``.
+The three trial examples are all small networks, the largest one containing a total of $48$ nodes and $77$ arcs, so that all can be used to test the correctness of the algorithmic approach applied.
+For these three examples we show the network drawing representation and their fibers distribution identified as the result of the refiniment partition.
 
 The first example is showed at the figure \ref{fig:result1}.
-This network is disconnected, containing two main weakly connected components, and contains only positive regulation between the interactions between the genes, showing the simpler case where the connections between nodes in a network are all of the same type.
+This network is disconnected, containing two main weakly connected components, and in addition contains only positive regulation between the interactions between the genes, showing the simpler case where the connections between nodes in a network are all of the same type.
 In this case, we find five non-trivial fibers, that is, fibers with size larger than one.
@@
 	\subfloat[]{{\includegraphics[scale=0.3]{Figures/result1-1.png}}}
-	\caption{}
+	\caption{First trial network example.
+Containing a total of $N = 17$ nodes and $M = 22$ arcs, the network has two weakly connected components, defined as the connected networks when we treat all the directed arcs as undirected edges.
+For each non-trivial fiber I give the same color for the nodes belonging to it.}
 	\label{fig:result1}
@@
 
-At the end of the algorithm, all the fibers identified are input-tree stable with respect to all fibers in the network, including the fiber itself.
-Then, labelling each fiber by an index or color we can then construct the fibration building blocks through the calculation of the fundamental class number $n$ and through the subclass number $l$.
-Again, a fibration building block is defined as the nodes inside the fiber as well as the $l$ external nodes that directly regulates at least one node of the current fiber.
-By that, we calculate the fundamental class number $n_k$ of the fiber $k$ by constructing the adjacency matrix $A_{ij}^{k}$ of its fibration building block and then calculating the largest eigenvalue of it.
-The value of $n$ quantifies the information loops of the fibration building blocks and can be either a integer or fractal golden ration.
+At the end of the algorithm, all the identified fibers are input-tree stable with respect to all fibers in the network, including the fiber itself.
+Then, by labelling each fiber with an index or color we can then construct the fibration building blocks through the calculation of the fundamental class number $n$ and through the subclass number $\ell$.
+Again, a fibration building block is defined as the nodes belonging to a fiber and all the $\ell$ external nodes that directly regulates at least one node of the current fiber.
+With that, we calculate the fundamental class number $n_k$ of the fiber $k$ by building the adjacency matrix $\mathbf{A}^{k}$ of its fibration building block and then calculating the largest eigenvalue of it.
+The value of $n$ quantifies the information cycles of the fibration building blocks and it can be either represent integer branching ratios or fractal golden ration of their input-tree topology class.
 
-Labelling the resulted fiber distribution, we obtain the following fibration classification for each fibratiion buuilding block of the network containing more than one node:
+Labelling the resulted fiber distribution for the first example in figure \ref{fig:result1}, we obtain the following fibration classification for each fibratiion building block of the network containing more than one node:
 
@@
     \begin{tabular}[b]{cc}\hline
-      Table head & Table head \\ \hline
-      Some values & Some values \\
-      Some values & Some values \\
-      Some values & Some values \\
-      Some values & Some values \\
-      Some values & Some values \\
-      Some values & Some values \\ \hline
+      Fiber & $| n, \ell \rangle$  \\ \hline
+      1 & $| 0, 2 \rangle$ \\
+      2 & $| 0, 1 \rangle$ \\
+      3 & $| 0, 1 \rangle$ \\ 
+      4 & $| 0, 1 \rangle$ \\
+      5 & $| 0, 2 \rangle$ \\ \hline
 	\end{tabular}
-    %\captionlistentry[table]{A table beside a figure}
+	\captionlistentry[table]{A table beside a figure}
     %\captionsetup{labelformat=andtable}
-    %\caption{A table beside a figure}
+    \caption{A table beside a figure}
 \end{figure}
@@
 The second example exhibits a connected component containing $N = 21$ nodes, where all the three type of regulation are present.
-For this network we find the total of eleven fibers, where just six are fibers containing more than one node in it.
-As we can notice, for two arbitrary nodes be in the same fiber they must not just receive the same number of inward connections but the same number of each type of inward connections, this way receive the equivalent information from the rest of the network.
-We can see this for the example of the fibers $4$ e $5$, where even though both receives two links from the same central node, the fibers receives different types of information from that node, meaning that they are not the equivalent fibers.
+For this network I find the total of eleven fibers, where only six are fibers containing more than one node in it.
+Important to note that for two arbitrary nodes be in the same fiber they must not just receive the same number of inward connections but the same number of each type of inward connections, receiving, this way, equivalent information from the rest of the network.
+We can see this for the example of the fibers $4$ e $5$, where even though both receives two links from the same central node, the fibers receives different types of information from that node, meaning that they are not equivalent fibers.
+
+If we consider the fiber $3$, besides the inner autoregulation loop we have a loop information going outside the fiber and going back through an external regulator inside the fiber $1$.
+In cases like this the branching ratio of the fiber has a fractal value represented by a golden ratio $\phi_d$ resulted by a cycle of information represented by a fibonacci sequence.
+This way, fiber $3$ can be classified by the values $| \phi_d, \ell = 2 \rangle$ where the fiber has two external regulator nodes.
+The fibration classification for the non-trivial fibers is showed in the table \ref{tab:r2}.
+
+%\begin{figure}[H]
+%	\centering
+%	\subfloat[]{{\includegraphics[scale=0.25]{Figures/result2.png}}}
+%	\qquad
+%	\subfloat[]{{\includegraphics[scale=0.25]{Figures/result2-label.png}}}
+%	\caption{First trial network example.
+Containing a total of $N = 17$ nodes and $M = 22$ arcs, the network has two weakly connected %components, defined as the connected networks when we treat all the directed arcs as undirected edges.
+For each non-trivial fiber I %give the same color for the nodes belonging to it.}
+%	\label{fig:result2}
+%\end{figure}
 
@@
 \end{figure}
+
 \begin{figure}[H]
@@
 
-If we consider the fiber $3$, besides the inner autoregulation loop we have a loop information going outside the fiber and going back through an external regulator inside the fiber $1$.
-In cases like this the branching ratio of the fiber has a fractal value represented by a golden ratio $\phi_d$ resulted a loop information represented by a fibonacci sequence.
-This way, fiber $3$ can be classified by the values $| \phi_d, l = 2 \rangle$ where the fiber has two external regulator nodes.
-The fibration classification for the non-trivial fibers is showed in the table \ref{asdas}.
-
-\begin{table}
+\begin{table}[H]
 \centering
 \begin{tabular}[b]{cc}\hline
-	Table head & Table head \\ \hline
-	Some values & Some values \\
-	Some values & Some values \\
-	Some values & Some values \\
-	Some values & Some values \\
-	Some values & Some values \\
-	Some values & Some values \\ \hline
+	Fiber & $| n, \ell \rangle$  \\ \hline
+	1 & $| 0, 1 \rangle$ \\
+	2 & $| 0, 1 \rangle$ \\
+	3 & $| 0, 1 \rangle$ \\ 
+	4 & $| 0, 1 \rangle$ \\
+	5 & $| 0, 2 \rangle$ \\
+	6 & $| 0, 2 \rangle$ \\ \hline
   \end{tabular}
+  \caption{}
+  \label{tab:r2}
 \end{table}
 
-Before applying the algorithm for the whole network, we chose, for the finality of visualization and testing, to apply first the algorithm for a weakly connected component of the \textit{E.
+Before applying the algorithm for the whole \textit{Escherichia Coli} network, I chose, for the finality of visualization and testing, to apply first the algorithm for a weakly connected component of the \textit{E.
 Coli} network.
-The same network is showed at the supplementary information from \cite{fibration2019}.
-The fiber distribution found is consistent with the one presented at \cite{fibration2019}, presenting the total of fifteen non-trivial fiber groups as shown in figure \ref{fig:result3-1}.
+The same network is showed at the supplementary information of \cite{fibration2019}.
+The fiber distribution found is consistent with the one presented at \cite{fibration2019}, presenting the total of fifteen non-trivial fiber groups as shown in the figure \ref{fig:result3-1}.
 
@@
 
-The connected component showed at the figure \ref{fig:result3} is a representation of a component in the whole regulatory network of the \textit{Escherichia Coli} bacteria and the resulted fibers shows just a portion of the whole fibers pattern.
-In the table X we give the classification for each fibration building block obtained for the whole bacteria network, including of course the fibers presented in the figure \ref{fig:result3-1}.
-In total, we have found $84$ non-trivial fiber groups containing a total of 462 nodes, obtaining a characteristic fiber statistics for the \textit{Escherichia Coli} network data.
-To guarantee the correctness of the fiber distribution found we calculate after the application of the refinement partitioning algorithm the information received for each node inside a fiber and compares if each one process equivalent information.
+The connected component showed at the figure \ref{fig:result3} is a subset representation of the nodes of the regulatory network of the \textit{Escherichia Coli} bacteria and the resulted fibers shows just a portion of the whole fibers pattern.
+In the table X I provide the classification for each fibration building block obtained for the whole bacteria network, including, of course, the fibers presented in the figure \ref{fig:result3-1}.
+In total, I have found $84$ non-trivial fiber groups containing a total of $462$ nodes, obtaining a characteristic fiber statistics for the \textit{Escherichia Coli} network data.
+To guarantee the correctness of the fiber distribution found I calculated, after the refinement algorithm, the information received for each node inside the fibers and compares if each one process equivalent information.
+The result of this calculation is stored in the data file given at \url{https://github.com/higorsmonteiro/fiberblocks/blob/master/Data/fiberVerification.dat}, where for each node in a non-trivial fiber block I give the list of the nodes that sends information messages to the current node along with their fiber indexes and type of link values.
+Even though the algorithm implementation and the provided data above support the correctness of the results of this report, they shows a discrepancy comparing with the results exhibited at \cite{fibration2019} for the same regulatory network data.
 
-The statistics concerning the number of each fibration block on the network is given in the table X, showing \textcolor{red}{describe the pattern of the statistics of the table that concerns the bacteria fiber statistics}.
-
-\section{Conclusion}
-
-Nullam semper quam at ante convallis posuere.
-Ut faucibus tellus ac massa luctus consectetur.
-Nulla pellentesque tortor et aliquam vehicula.
-Maecenas imperdiet euismod enim ut pharetra.
-Suspendisse pulvinar sapien vitae placerat pellentesque.
-Nulla facilisi.
-Aenean vitae nunc venenatis, vehicula neque in, congue ligula.
+The statistics concerning the fundamental class number and the external regulators of each fibration block on the network is given in the table X, showing \textcolor{red}{describe the pattern of the statistics of the table that concerns the bacteria fiber statistics}.
 

### 2019-10-31 Code/minimalfiber.c

@@ -505,10 +505,12 @@ int main(int argv, char** argc)
 	}
 	//////////////////////////////////////////////////////////////////////////
 
+	ShowMainInfo(partition);
+	
 	int n;
 	STORETYPE* tempx;
 	int* temp;
-	printf("%d\n", total_nodes);
+	printf("%d\n", nontrivial_fibers);
 	//for(current_part=partition; current_part!=NULL; current_part=current_part->next)
 	//{
 	//	if(current_part->block->size==1) continue;

### 2019-10-31 Code/structforfiber.h

@@ -37,11 +37,10 @@ typedef struct NodeAdj NodeAdj;
 ////////////////////// STACK DATA STRUCTURE ///////////////////////
 struct stack
 {
-	int extn;
 	int node_ID;
 	struct stack *next;
 };
-typedef struct stack Stack;
+typedef struct stack STACK;
 /////////////////////////////////////////////////////////////////////
 
 ////////////////// DOUBLE LINKED LIST DATA STRUCTURE //////////////////
@@ -219,6 +218,7 @@ void ShowMainInfo(PART* partition)
 	for(current_part=partition; current_part!=NULL; current_part=current_part->next)
 	{
 		printf("Fiber %d: Size %d - Fundamental Class %lf - Subclass %d\n", current_part->block->index, current_part->block->size, current_part->fundamental_number, current_part->number_regulators);
+		printBlock(current_part->block);
 	}
 }
 #endif

### 2019-10-31 Code/utilsforfiber.h

@@ -207,6 +207,8 @@ extern int* GET_OUTNEIGH(Graph* graph, int node)
 	int* in_neighbors = (int*)malloc(n_in*sizeof(int));
 	for(NODE=graph->array[node].head_out; NODE!=NULL; NODE=NODE->next)
 		in_neighbors[n_index++] = NODE->neighbor;
+	
+	qsort(in_neighbors, n_in, sizeof(int), cmpfunc);
 	return in_neighbors; 
 }
 
@@ -252,6 +254,53 @@ extern int CHECKLINK(Graph* graph, int pointing_node, int pointed_node)
 	return 0;
 }
 
+extern void KosajaruSCC(NODELIST** nodes_in_scc, int root, Graph* graph)
+{
+	int i, j, v;
+	int N = graph->size;
+	int* visited = (int*)malloc(N*sizeof(int));
+	int* ivisited = (int*)malloc(N*sizeof(int));
+	for(i=0; i<N; i++) { visited[i] = 0; ivisited[i] = 0; }
+
+	STACK* nodetocheck = NULL;
+	
+	// DFS process in the network starting from the root node.
+	push(&nodetocheck, root);
+	while(nodetocheck)
+	{
+		v = pop(&nodetocheck);
+		if(visited[i]==0)
+		{
+			visited[i] = 1;
+			int n = GETNout(graph, v);
+			int* neigh_out = GET_OUTNEIGH(graph, v);
+			for(j=0; j<n; j++) push(&nodetocheck, neigh_out[j]);
+		}
+	}
+
+	// DFS process in the transpose network from the root node.
+	push(&nodetocheck, root);
+	while(nodetocheck)
+	{
+		v = pop(&nodetocheck);
+		if(visited[v]==1)
+		{
+			int check = doublycheck_element(*nodes_in_scc, v);
+			if(check==0) push_doublylist(nodes_in_scc, v); // it is in the root SCC.
+		}
+		if(ivisited[v]==0)
+		{
+			ivisited[v] = 1;
+			int n = GETNin(graph, v);
+			int* neigh_in = GET_INNEIGH(graph, v);
+			for(j=0; j<n; j++) push(&nodetocheck, neigh_in[j]);
+		}
+	}
+
+	// 'nodes_in_scc' contains all the nodes that are in the same SCC than root.
+	//return nodes_in_scc;
+}
+
 
 ////////////////////////////////////////////////////////////////////
[…]

### 2019-10-31 Code/minimalfiber.c
fundamental class

@@ -62,21 +62,23 @@ void CALCULATE_FUNDAMENTAL(PART** partition, Graph* graph)
 
 	PART* current_part;
 	NODELIST* nodelist;
+	NODELIST* scc_nodes;
 	// Loop over all the fiber blocks.
 	for(current_part=(*partition); current_part!=NULL; current_part=current_part->next)
 	{
-		number_fnodes = current_part->block->size;
-		number_regulators = current_part->number_regulators;
-		all_nodes = number_fnodes+number_regulators;
+		//temp_index = (int*)malloc(all_nodes*sizeof(int));
+    	//temp_adjmatrix = (double*)malloc(all_nodes*all_nodes*sizeof(double));
 
-		index = 0;
-		temp_index = (int*)malloc(all_nodes*sizeof(int));
-    	temp_adjmatrix = (double*)malloc(all_nodes*all_nodes*sizeof(double));
-		// Get the correct nodes.		
+		scc_nodes = NULL;
+		// Get the correct nodes.
 		for(nodelist=current_part->block->head; nodelist!=NULL; nodelist=nodelist->next)
-			temp_index[index++] = nodelist->data;
-		for(nodelist=current_part->regulators; nodelist!=NULL; nodelist=nodelist->next)
-			temp_index[index++] = nodelist->data;
+		{
+			push_doublylist(&scc_nodes, nodelist->data);
+			KosajaruSCC(&scc_nodes, nodelist->data, graph);
+		}
+			
+		//for(nodelist=current_part->regulators; nodelist!=NULL; nodelist=nodelist->next)
+		//	temp_index[index++] = nodelist->data;
 		
 		//Now we construct the current circuit fiber adjacency matrix to calculate its eigenvalues.
 		for(j=0; j<all_nodes; j++)

### 2019-11-01 Code/fibrationf.h
org

@@ -1,0 +1,345 @@
+#ifndef FIBRATIONF_H
+#define FIBRATIONF_H
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <math.h>
+#include <gsl/gsl_eigen.h>
+#include "utilsforfiber.h"
+#include "structforfiber.h"
+#define SENTINEL -96
+
+extern double GET_EIGMAX(NODELIST* scc_nodes, Graph* graph)
+{
+	int i, j, k;
+	int nn = GetListSize(scc_nodes);
+	int* temp_index = (int*)malloc(nn*sizeof(int));
+    double* temp_adjmatrix = (double*)malloc(nn*nn*sizeof(double));
+
+	int index = 0;
+	NODELIST* nodelist;
+	for(nodelist=scc_nodes; nodelist!=NULL; nodelist=nodelist->next)
+		temp_index[index++] = nodelist->data;
+
+	for(j=0; j<nn; j++)
+    {
+		for(k=0; k<nn; k++)
+		{
+			int check = CHECKLINK(graph, temp_index[k], temp_index[j]); // A_{jk} = 1 if j -> k
+			if(check==1) temp_adjmatrix[k*nn + j] = 1.0;
+			else temp_adjmatrix[k*nn + j] = 0.0;
+		}
+	}
+
+	/////////// GSL PACKAGE ROUTINES TO EIGENSYSTEMS PROBLEMS ////////////
+    gsl_matrix_view m = gsl_matrix_view_array(temp_adjmatrix, nn, nn);
+    // 'eval' will gonna stores all the 'nn' eigenvalues of the fiber adjacency matrix.
+    gsl_vector_complex *eval = gsl_vector_complex_alloc (nn);
+
+    gsl_eigen_nonsymm_workspace* w = gsl_eigen_nonsymm_alloc(nn);
+    gsl_eigen_nonsymm(&m.matrix, eval, w);
+    gsl_eigen_nonsymm_free(w);
+    //////////////////////////////////////////////////////////////////////
+
+    double temp;
+    double eigmax = gsl_vector_get(eval, 0);
+    for(j=1; j<nn; j++) { temp = gsl_vector_get(eval, j); if(temp>eigmax) eigmax = temp; }
+	free(temp_index);
+	free(temp_adjmatrix);
+	return eigmax;
+}
+
+/*	Calculates the fundamental class number. For that, for each fiber block, we select
[…]

### 2019-11-01 Code/minimalfiber.c

@@ -39,385 +39,13 @@
 // Used fot the calculation of the eigenvalues for each fibration block adjacency matrix.
 #include <gsl/gsl_eigen.h>
 // Separated personal constructed modules for graph data and graph fibration specific functions.
+#include "fibrationf.h"
 #include "utilsforfiber.h"
 #include "structforfiber.h"
 ////////////////////////////////////////////////////////////////////////////////////////////////
-#define SENTINEL -96
+//#define SENTINEL -96
 
-
-/*	Calculates the fundamental class number. For that, for each fiber block, we select
-	all the nodes belonging to the block and all the external nodes that regulates that 
-	same fiber.	After that, construct the adjacency matrix for that set and obtain its
-	largest eigenvalue. */
-void CALCULATE_FUNDAMENTAL(PART** partition, Graph* graph)
-{
-	int i, j, k;
-	int check, index, nn;
-	int all_nodes;	
-	int number_fnodes;
-	int number_regulators;
-
-	int* temp_index;			// Temporary indexation for each node in the circuit set.
-	double* temp_adjmatrix;		// n*n array to define the adjacency matrix.
-
-	PART* current_part;
-	NODELIST* nodelist;
-	NODELIST* scc_nodes;
-	// Loop over all the fiber blocks.
-	for(current_part=(*partition); current_part!=NULL; current_part=current_part->next)
-	{
-		//temp_index = (int*)malloc(all_nodes*sizeof(int));
-    	//temp_adjmatrix = (double*)malloc(all_nodes*all_nodes*sizeof(double));
-
-		scc_nodes = NULL;
-		// Get the correct nodes.
-		for(nodelist=current_part->block->head; nodelist!=NULL; nodelist=nodelist->next)
-		{
-			push_doublylist(&scc_nodes, nodelist->data);
-			KosajaruSCC(&scc_nodes, nodelist->data, graph);
-		}
-			
-		//for(nodelist=current_part->regulators; nodelist!=NULL; nodelist=nodelist->next)
-		//	temp_index[index++] = nodelist->data;
-		
-		//Now we construct the current circuit fiber adjacency matrix to calculate its eigenvalues.
-		for(j=0; j<all_nodes; j++)
-    	{
-			for(k=0; k<all_nodes; k++)
-			{
[…]

### 2019-11-01 Code/structforfiber.h

@@ -212,6 +212,14 @@ void printPartitionReg(PART* part)
 		if(temp->block->size>1) printf("Number of external regulators of block %d: %d\n", temp->block->index, temp->number_regulators);
 }
 
+void printList(NODELIST* list)
+{
+	NODELIST* current;
+	for(current=list; current!=NULL; current=current->next)
+		printf("%d ", current->data);
+	printf("\n");
+}
+
 void ShowMainInfo(PART* partition)
 {
 	PART* current_part;

### 2019-11-01 Code/utilsforfiber.h

@@ -254,61 +254,13 @@ extern int CHECKLINK(Graph* graph, int pointing_node, int pointed_node)
 	return 0;
 }
 
-extern void KosajaruSCC(NODELIST** nodes_in_scc, int root, Graph* graph)
-{
-	int i, j, v;
-	int N = graph->size;
-	int* visited = (int*)malloc(N*sizeof(int));
-	int* ivisited = (int*)malloc(N*sizeof(int));
-	for(i=0; i<N; i++) { visited[i] = 0; ivisited[i] = 0; }
-
-	STACK* nodetocheck = NULL;
-	
-	// DFS process in the network starting from the root node.
-	push(&nodetocheck, root);
-	while(nodetocheck)
-	{
-		v = pop(&nodetocheck);
-		if(visited[i]==0)
-		{
-			visited[i] = 1;
-			int n = GETNout(graph, v);
-			int* neigh_out = GET_OUTNEIGH(graph, v);
-			for(j=0; j<n; j++) push(&nodetocheck, neigh_out[j]);
-		}
-	}
-
-	// DFS process in the transpose network from the root node.
-	push(&nodetocheck, root);
-	while(nodetocheck)
-	{
-		v = pop(&nodetocheck);
-		if(visited[v]==1)
-		{
-			int check = doublycheck_element(*nodes_in_scc, v);
-			if(check==0) push_doublylist(nodes_in_scc, v); // it is in the root SCC.
-		}
-		if(ivisited[v]==0)
-		{
-			ivisited[v] = 1;
-			int n = GETNin(graph, v);
-			int* neigh_in = GET_INNEIGH(graph, v);
-			for(j=0; j<n; j++) push(&nodetocheck, neigh_in[j]);
-		}
-	}
-
-	// 'nodes_in_scc' contains all the nodes that are in the same SCC than root.
-	//return nodes_in_scc;
-}
-
-
 ////////////////////////////////////////////////////////////////////
 ////////////////////////////////////////////////////////////////////
 
 ////////////////////////////////
 ////// STACK OPERATIONS ///////
 // To insert an element in the stack.
-extern void push(STACK** top, int node)
+extern void dopush(STACK** top, int node)
 {
 	STACK *ptr;
 	ptr = (STACK*)malloc(sizeof(STACK));
[…]

### 2019-11-01 Code/fibrationf.h
NEW BUG: ALONE AUTORREGULATED NODES

@@ -1,10 +1,17 @@
 #ifndef FIBRATIONF_H
 #define FIBRATIONF_H
 
+/*  
+    The code here represents the central module for the implementation of the coarsest
+    refinement graph partitioning algorithm, containing the functions used in the main
+    code. The necessary comments are given at the beginning of each function (to do).
+ */
+
 #include <stdio.h>
 #include <stdlib.h>
 #include <string.h>
 #include <math.h>
+///////////////////
 #include <gsl/gsl_eigen.h>
 #include "utilsforfiber.h"
 #include "structforfiber.h"
@@ -54,7 +61,7 @@ extern double GET_EIGMAX(NODELIST* scc_nodes, Graph* graph)
 	all the nodes belonging to the block and all the external nodes that regulates that 
 	same fiber.	After that, construct the adjacency matrix for that set and obtain its
 	largest eigenvalue. */
-extern void CALCULATE_FUNDAMENTAL(PART** partition, Graph* graph)
+extern void DEF_BRANCH_RATIO(PART** partition, Graph* graph)
 {
 	PART* current_part;
 	NODELIST* nodelist;

### 2019-11-01 Code/minimalfiber.c

@@ -15,7 +15,7 @@
 	('ARG1edgelist.dat') containing all the directed links between nodes (3 columns: "%d\t%d\t%s\n" -> Pointing Node/ 
 	Pointed Node/ Type of regulation). For gene regulatory networks, the type of the regulation can be 'positive', 'negative' 
 	or 'dual'. The second argument is a flag used to signal the code to properly get the gene names of each node number. For 
-	that, it is necessary an auxiliary file called 'ARG1genename.dat' containing two columns (formatted as "%s\t%d\n" -> Gene 
+	that, it is necessary an auxiliary file called 'ARG1nameID.dat' containing two columns (formatted as "%s\t%d\n" -> Gene 
 	name/ Gene ID number). Thus, if there is a gene name file, the code will properly link all the node numbers with their 
 	corresponding name if 'ARG2' is passed as '-y', otherwise just the node numbers is stored for each node.
 
@@ -43,7 +43,6 @@
 #include "utilsforfiber.h"
 #include "structforfiber.h"
 ////////////////////////////////////////////////////////////////////////////////////////////////
-//#define SENTINEL -96
 
 void main(int argv, char** argc) 
 { 
@@ -77,9 +76,9 @@ void main(int argv, char** argc)
 	BLOCK* P = (BLOCK*)malloc(sizeof(BLOCK));
 	BLOCK* NonP = (BLOCK*)malloc(sizeof(BLOCK));
 	
+	// Define the initial partition as one block containing all operating nodes. 
 	PART* null_partition = NULL;
 	PREPROCESSING(&P, &NonP, &null_partition, graph, N);
-	// Define the initial partition as one block containing all operating nodes. 
 	PART* partition = NULL;    
 	push_block(&partition, P);	// Push initial block to the partition.
 	
@@ -115,48 +114,39 @@ void main(int argv, char** argc)
 	// Defines number of external regulators and set list of external regulators for each block.
 	CALCULATE_REGULATORS(&partition, graph);
 	CALCULATE_REGULATORS(&null_partition, graph);
-	// Calculates fundamental class number for each fiber block.
-	CALCULATE_FUNDAMENTAL(&partition, graph);
+	// Calculates branch ratio number for each fiber block.
+	DEF_BRANCH_RATIO(&partition, graph);
 	//////////////////////////////////////////////////////////////////////////////////////////
[…]

### 2019-11-01 Code/structforfiber.h

@@ -2,6 +2,8 @@
 #define FSTRUCTS_H
 
 #include <stdio.h>
+#include <stdlib.h>
+#include "utilsforfiber.h"
 
 /////////////////////////////////////////////////////////////////////
 /// Structures to create and define a directed, unweighted graph ///
@@ -75,6 +77,14 @@ struct Partition
 typedef struct Partition PART;
 ////////////////////////////////////////////////////////////////////////
 
+struct storetype
+{
+	int node;
+	int type;
+};
+typedef struct storetype STORETYPE;
+/////////////////////////////////////////////////////////////////////////
+
 struct QueueOfBlocks
 {
     BLOCK* block;
@@ -84,7 +94,39 @@ typedef struct QueueOfBlocks QBLOCK;
 ///////////////////////////////////////////////////////////////////////////////
 ///////////////////////////////////////////////////////////////////////////////
 
-extern void PrintInNeighbors(Graph* graph, int node, int N)
+int cmp(const void *a, const void *b)
+{
+    STORETYPE *a1 = (STORETYPE *)a;
+    STORETYPE *a2 = (STORETYPE *)b;
+    if ((*a1).node > (*a2).node)
+        return -1;
+    else if ((*a1).node < (*a2).node)
+        return 1;
+    else
+        return 0;
+}
+
+STORETYPE* GETIN_ADJTYPE(Graph* graph, int node)
+{
+	int n_in = 0;	
+	NodeAdj* NODE;
+	for(NODE=graph->array[node].head_in; NODE!=NULL; NODE=NODE->next) n_in++;
+
+	int n_index = 0;
+	STORETYPE* in_neighbors = (STORETYPE*)malloc(n_in*sizeof(STORETYPE));
+	for(NODE=graph->array[node].head_in; NODE!=NULL; NODE=NODE->next)
+	{
+		in_neighbors[n_index].node = NODE->neighbor;
+		in_neighbors[n_index].type = NODE->type_link;
+		n_index++;
+	}
+	
+	qsort(in_neighbors, n_in, sizeof(in_neighbors[0]), cmp);
+	return in_neighbors; 
+}
+
+////////////////// VISUALIZATION UTILITIES ///////////////////
+extern void PrintInNeighbors(Graph* graph, int node)
 {
 	NodeAdj* Inode = graph->array[node].head_in;
 	printf("Node %d: ", node);
@@ -96,7 +138,7 @@ extern void PrintInNeighbors(Graph* graph, int node, int N)
 	printf("\n");
 }
 
[…]

### 2019-11-01 Code/utilsforfiber.h

@@ -143,45 +143,6 @@ int cmpfunc (const void * a, const void * b) {
    return ( *(int*)a - *(int*)b );
 }
 
-struct storetype
-{
-	int node;
-	int type;
-};
-typedef struct storetype STORETYPE;
-
-int cmp(const void *a, const void *b)
-{
-    STORETYPE *a1 = (STORETYPE *)a;
-    STORETYPE *a2 = (STORETYPE *)b;
-    if ((*a1).node > (*a2).node)
-        return -1;
-    else if ((*a1).node < (*a2).node)
-        return 1;
-    else
-        return 0;
-}
-
-extern STORETYPE* GET_INTYPENEIGH(Graph* graph, int node)
-{
-	int n_in = 0;	
-	NodeAdj* NODE;
-	for(NODE=graph->array[node].head_in; NODE!=NULL; NODE=NODE->next) n_in++;
-
-	int n_index = 0;
-	STORETYPE* in_neighbors = (STORETYPE*)malloc(n_in*sizeof(STORETYPE));
-	//int* in_neighbors = (int*)malloc(n_in*sizeof(int));
-	for(NODE=graph->array[node].head_in; NODE!=NULL; NODE=NODE->next)
-	{
-		in_neighbors[n_index].node = NODE->neighbor;
-		in_neighbors[n_index].type = NODE->type_link;
-		n_index++;
-	}
-	
-	qsort(in_neighbors, n_in, sizeof(in_neighbors[0]), cmp);
-	return in_neighbors; 
-}
-
 extern int* GET_INNEIGH(Graph* graph, int node)
 {
 	int n_in = 0;	

### 2019-11-03 Code/GraphPart.c
It works

@@ -1,178 +1,0 @@
-/*  The code given here has the aim to determine the minimal balanced color classes to identify
-    the fibration building blocks of a directed network. The theory concerning the graph fibration
-    morphism and its application on biological networks are detailed, respectively, mainly in the
-    paper of Boldi and Vigna (2001) and in the paper of Morone et. al. (2019, to be published). Concerning
-    the algorithm reproduced in this code, one should refer to the work of Cardon and Crochemore (1982).
-
-    The resulted fibers represent, for each fiber, the set of nodes that are isomorphic under a graph
-    fibration morphism, i. e., all nodes belonging to the same fiber has the same information input-tree.
-
-    -----------------------------------------------------------------------------------------------------
-
-    The code has one command line argument, requiring the common identifier for two files: one single-line file 
-	containing a integer number representing the number of nodes in the network, and a 'ARGedgelist.dat' file containing 
-	all the directed links between nodes (3 columns -> Pointing Node/ Pointed Node/ Type of regulation).
-
-    The result is stored in two arrays: 'nodecolor' and 'edgecolor'. Each array store the color of each
-    component (node or link) and, thus, gives all the information needed, together with the files, for the
-    base graph construction.
-
-    Author: Higor da S. Monteiro - Departament of Physics/Universidade Federal do Ceará (UFC)
-*/
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <math.h>
-#include <gsl/gsl_eigen.h>
-#include "graphdef.h"   	// Personal module containing helpful functions to handle with network data and other common operations.
-#define SEQSIZE 500     	// It's possible that the size of the string sequences should be larger for larger networks.
-
-int nfibers;
-
-struct aux
-{
-	int color;
-	int number;
-}
-typedef struct aux AUX;
-
-struct strseq
-{
-    int node;
-    Node* strseq;       
-};
-typedef struct strseq STRSEQ;
-
-// Comparison function to be used in string sorting operation.
[…]

### 2019-11-03 Code/fibrationf.h

@@ -305,14 +305,11 @@ int STABILITYCHECKER(PART** partition, BLOCK* Set, Graph* graph)
 
 ///////////////////////////////////////////////////////////////////////////////////////
 ////////////////// PREPROCESSING FUNCTIONS FOR REFINEMENT ALGORITHM ///////////////////
-extern void ENQUEUE_SOLITAIRE(PART** null_partition, QBLOCK** qhead, QBLOCK** qtail)
+extern void ENQUEUE_BLOCKS(PART** partition, QBLOCK** qhead, QBLOCK** qtail)
 {
-	PART* current_part = *null_partition;
-	while(current_part)
-	{
+	PART* current_part;
+	for(current_part=(*partition); current_part!=NULL; current_part=current_part->next)
 		enqueue_block(qhead, qtail, current_part->block);
-		current_part = current_part->next;
-	}
 }
 
 extern void InitiateBlock(PART** Null_Part, int node)
@@ -325,26 +322,108 @@ extern void InitiateBlock(PART** Null_Part, int node)
 	push_block(Null_Part, new_block);
 }
 
-extern void PREPROCESSING(BLOCK** P, BLOCK** NonP, PART** Null_Part, Graph* graph, int N)
-{
-	(*P)->size = 0;
-	(*NonP)->size = 0;
-	(*P)->index = 0;
-	(*NonP)->index = -1;
-	(*P)->head = NULL;
-	(*NonP)->head = NULL;    
+//extern void PREPROCESSING(BLOCK** P, BLOCK** NonP, PART** Null_Part, Graph* graph, int N)
+//{
+//	(*P)->size = 0;
+//	(*NonP)->size = 0;
+//	(*P)->index = 0;
+//	(*NonP)->index = -1;
+//	(*P)->head = NULL;
+//	(*NonP)->head = NULL;    
+//
+//	int n_in, i;
+//    for(i=0; i<N; i++)
+//    {
+//		n_in = GETNin(graph, i);
+//        if(n_in>0) add_to_block(P, i);
+//		else add_to_block(NonP, i);
+//    }
+//	// Define one block for each solitaire node and put in the 'Null_Part'.
+//	NODELIST* nodelist = (*NonP)->head;
+//	for(nodelist=(*NonP)->head; nodelist!=NULL; nodelist=nodelist->next)
+//        InitiateBlock(Null_Part, nodelist->data);
+//}
 
-	int n_in, i;
-    for(i=0; i<N; i++)
-    {
[…]

### 2019-11-03 Code/minimalfiber.c

@@ -63,30 +63,29 @@ void main(int argv, char** argc)
 	else nodename_bool = 0;
 	///////////////////////////////////////////////////////////////////////////////////////
 
-    // Creates the network for N nodes and defines its structure with the given 'edgelist.dat' file.
+    // Creates the network for N nodes and defines its structure with the given edgelist file.
 	int** edges;
+	int* components = (int*)malloc(N*sizeof(int));
 	Graph* graph = createGraph(N, nodename, nodename_bool);
-	edges = defineNetwork(edges, graph, net_edges);
+	edges = defineNetwork(edges, components, graph, net_edges);
 	///////////////////////////////////////////////////////////////////////////////////////
 
-	/////////////////////// COARSEST REFINEMENT PARTITION ALGORITHM ////////////////////////
+	/////////////////////// COARSEST REFINEMENT PARTITIONING ALGORITHM ////////////////////////
 	int i, j, k;
-           
-	// Put aside from the algorithm (index -1) all nodes that don't receive any information.    
-	BLOCK* P = (BLOCK*)malloc(sizeof(BLOCK));
-	BLOCK* NonP = (BLOCK*)malloc(sizeof(BLOCK));
 	
 	// Define the initial partition as one block containing all operating nodes. 
-	PART* null_partition = NULL;
-	PREPROCESSING(&P, &NonP, &null_partition, graph, N);
 	PART* partition = NULL;    
-	push_block(&partition, P);	// Push initial block to the partition.
-	
+	PART* null_partition = NULL;
+	PART* null_partition2 = NULL;
+	PREPROCESSING(&partition, &null_partition, &null_partition2, components, graph);
+
 	// Initialize the queue of blocks with the initial block above.
 	QBLOCK* qhead = NULL;
 	QBLOCK* qtail = NULL;
-	enqueue_block(&qhead, &qtail, P);
-	ENQUEUE_SOLITAIRE(&null_partition, &qhead, &qtail);
+	ENQUEUE_BLOCKS(&partition, &qhead, &qtail);
+	ENQUEUE_BLOCKS(&null_partition, &qhead, &qtail);
+	ENQUEUE_BLOCKS(&null_partition2, &qhead, &qtail);
+	//printAllPartition(null_partition2);
 
 	// Until L is empty, we procedure the splitting process.
 	BLOCK* CurrentSet;	
@@ -133,17 +132,21 @@ void main(int argv, char** argc)
 	}
[…]

### 2019-11-03 Code/structforfiber.h

@@ -13,6 +13,7 @@ struct Graph
 {
 	// each node has its adjancency list
 	int size;
+	int num_component;
 	struct adjList* array;
 };
 typedef struct Graph Graph;

### 2019-11-03 Code/utilsforfiber.h

@@ -1,6 +1,6 @@
 /*	In this module, I define all the functions that are, direct or indirectly, useful
 	for the main fibration routines needed to a correct implementation for the partition
-	refinement algorithm. Also, here I define my own functions to construct undirected 
+	refinement algorithm. Also, here I define my own functions to construct directed 
 	networks. All the handmade data structures used are defined in 'structforfiber.h'.
 
 	Author: Higor da S. Monteiro - Universidade Federal do Ceará
@@ -46,6 +46,9 @@ extern Graph* createGraph(int N, char* nodenames, int name_bool)
 
 	int nodeID;
 	char tempname[60];
+	/*	if 'name_bool' is one, then we read the file containing
+		the names of each node to assign it to each node in our 
+		constructed network.	*/
 	if(name_bool==1)
 	{
 		FILE* NAMES = fopen(nodenames, "r");
@@ -59,16 +62,62 @@ extern Graph* createGraph(int N, char* nodenames, int name_bool)
 	return graph;
 }
 
-void addEdges(int** edges, Graph* graph, int* regulator, int nE)
+/////////////////////////////////////////////////////////////////
+int findroot(int node, int* psite)
 {
-	int index, j, node1, node2, reg;
+	int root = node;
+	int cont = 0;
+	int path[100];                                  
+	while(psite[root]>=0)                     
+	{
+		path[cont++] = root;
+		root = psite[root];
+	}
+	if(psite[node]>=0) psite[node] = root;
+	while(cont) psite[path[--cont]] = root;
+	return root;
+}
+
+void merge(int node1, int root1, int node2, int root2, int* psite)
+{
+	if(psite[root1] <= psite[root2])
+	{
+		psite[root1] += psite[root2];
+		psite[root2] = root1;
+		psite[node2] = root1;
+	}
+	else
+	{
+		psite[root2] += psite[root1];
+		psite[root1] = root2;
+		psite[node1] = root2;
+	}
+}
+//////////////////////////////////////////////////////////////////
+
+/*	Here I not just add the proper edges to the network but I
+	dynamically defines its weakly connected components through
+	a percolation-like process using disjoint sets operations.	*/
+void addEdges(int** edges, int* components, Graph* graph, int* regulator, int nE)
+{
+	int i, j;
+	int root1, root2;
[…]

### 2019-11-04 Manuscript/main.tex
Finishing manuscript

@@
 More specifically, using the transcriptional regulatory network data from the \textit{Escherichia Coli} bacteria, I quantify the clusters of nodes in the network that synchronously process equivalent information, and then I classify these clusters, called fibers, based on its specific topological features.
-Here, to consistently present the obtained results, I briefly introduce the theory concerning the graph fibration morphism and its main definitions related to information processing symmetries.
-Then, I detail the computational methods adopted to the identification of the network fibers, presenting a slightly different algorithmic approach for the problem in hand, based on the general relational refinement partitioning algorithms described by Paige and Tarjan in 1987.
-After defining the implementation details of the graph refinement algorithm I lastly apply the method for trial network examples and then for the constructed genetic regulatory network of \textit{Escherichia Coli}, noticing a visible discrepancy between the results obtained by the methods described in this report and the results exhibited in the most recent literature given at \textit{Morone et.
+Here, to present the obtained results, I briefly introduce the theory concerning the graph fibration morphism and its main definitions related to information processing symmetries.
+Then, I detail the computational methods adopted to the identification of the network fibers, presenting the algorithmic approach for the problem in hand, based on the general relational refinement partitioning algorithms described by Paige and Tarjan in 1987.
+After defining the implementation details of the graph refinement algorithm I apply the method for trial network examples and then for the constructed genetic regulatory network of \textit{Escherichia Coli}, noticing the equivalence between the results obtained by the methods described in this report and the results exhibited in the most recent literature given at \textit{Morone et.
 al.} (2019).

### 2019-11-04 Code/fibrationf.h

@@ -33,7 +33,7 @@ extern double GET_EIGMAX(NODELIST* scc_nodes, Graph* graph)
     {
 		for(k=0; k<nn; k++)
 		{
-			int check = CHECKLINK(graph, temp_index[k], temp_index[j]); // A_{jk} = 1 if j -> k
+			int check = CHECKLINK(graph, temp_index[j], temp_index[k]); // A_{jk} = 1 if j -> k
 			if(check==1) temp_adjmatrix[k*nn + j] = 1.0;
 			else temp_adjmatrix[k*nn + j] = 0.0;
 		}

### 2019-11-04 Code/minimalfiber.c

@@ -136,11 +136,11 @@ void main(int argv, char** argc)
 	/* With gene names */ //printGeneGraphInFibers(graph, partition, nodefibers);
 	/* Without gene names */ //printGraphInFibers(graph, partition, nodefibers);
 	
-	/* Classification Info */ //ShowMainInfo(partition);
+	/* Classification Info */ ShowClassification(partition, 0);
 	/* Fiber blocks and classification info */ //ShowInfo(partition, 1);
 
 	/*	Show the number of non-trivial fibers	*/
-	printf("%d %d\n", nontrivial_fibers, total_nodes);
+	//printf("%d %d\n", nontrivial_fibers, total_nodes);
 	
 	//int node = atoi(argc[3]);
 	//PrintInNeighbors(graph, node);

### 2019-11-04 Manuscript/main.tex
Report

@@
 	{ Fortaleza, Ceará }\\
-	{ October, 25, 2019 }\\[0.75cm]
+	{ November, 05, 2019 }\\[0.75cm]
 	{\textbf{Abstract}}
@@
 
-\section{Brief Introduction}
+\section{Introduction}
 
-This statement requires citation \cite{fibration2019}; this one does too \cite{Cardon1982} \cite{Boldi2006} \cite{Tarjan1987} \cite{Stewart2006}.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aenean dictum lacus sem, ut varius ante dignissim ac.
-Sed a mi quis lectus feugiat aliquam.
-Nunc sed vulputate velit.
-Sed commodo metus vel felis semper, quis rutrum odio vulputate.
-Donec a elit porttitor, facilisis nisl sit amet, dignissim arcu.
-Vivamus accumsan pellentesque nulla at euismod.
-Duis porta rutrum sem, eu facilisis mi varius sed.
-Suspendisse potenti.
-Mauris rhoncus neque nisi, ut laoreet augue pretium luctus.
-Vestibulum sit amet luctus sem, luctus ultrices leo.
-Aenean vitae sem leo.
+Dynamical processes occurring in networks permit novel qualitative behaviors that are not directly measured in classical dynamical systems \cite{Stewart2006}.
+The main feature of these behaviors is the existence of verifiable partial synchronized states, where different elements in the system follow the same or correlated phase space trajectories.
+These synchronized states are fundamentally important for the study of dynamical phenomena in networks, being still more relevant for information-processing complex systems, in which synchrony is directly related to functionality.
+
+Besides the specific characteristics of the dynamics taking place on the network, it is possible to define states of partial synchrony by considering only the topological features of networks.
+To this, it is possible to define a natural graph partitioning where each element of it represents the set of nodes that process equivalent incoming information from the rest of the network and even from itself, implying that each of these nodes processes information synchronously.
+Furthermore, one of the important insights concerning these clusters of synchronized network elements is the direct association of symmetries groups with the resulted distribution of synchronization clusters, which can offer a precise procedure to identify and classify the information-processing building blocks of several networks in nature.
+
+However, recently some works has been recognizing that topological symmetries of the network structure, meaning neighborhood structure invariance under nodes permutation, are not actually necessary for the emergence of synchronization of node states.
+Thus, instead of very restrictive isomorphisms rules, the blocks of synchronized information processing obeys a more loose concept of symmetry represented by the rules of groupoids.
+More specifically, information flow in a directed network is maintaneid as invariant under a graph fibration morphism.
+A graph fibration is a transformation that keeps invariant the set of universal input-trees that group the network nodes into functional blocks called network fibers \cite{Boldi2006}, \cite{fibration2019}.
+
+The formal definition of an input-tree is explained in detail at \cite{fibration2019}, \cite{Boldi2006} and \cite{Boldi2002}.
+Here, I give just a direct and intuitive example through the examples showed at figures \ref{fig:ex}.
+To fully characterize the information flow directions in a directed network, we can define for each node in the network an input-tree containing all the information pathways that ends at the given node.
+Thus, if two different nodes have isomorphic input-trees, which means that they receives equivalent information from the network, they synchronize their dynamical states, exhibiting a correlated behavior for the network.
+Even more, if a group of nodes have isomorphic input-trees, then a graph fibration transformation reduces these nodes from network $G$ in one single node for a base network $G'$.
+This way, a fibration reduces the original network in a base network where each node of $G'$ represents a fiber block of $G$.
+In figure \ref{fig:ex} we can see a directed network formed just by three nodes.
+For each one, they differs only by the patterns of directed links, from which information can flow.
+\begin{figure}[h]
+	\centering
+	\subfloat[]{{\includegraphics[scale=0.4]{Figures/ex1.png}}}
+	\qquad
+	\subfloat[]{{\includegraphics[scale=0.4]{Figures/ex2.png}}}
+	\qquad
+	\subfloat[]{{\includegraphics[scale=0.4]{Figures/ex3.png}}}
+	\caption{First trial network example.
+Containing a total of $N = 17$ nodes and $M = 22$ arcs, the network has two weakly connected components, defined as the connected networks when we treat all the directed arcs as undirected edges.
+For each non-trivial fiber I give the same color for the nodes belonging to it.}
+	\label{fig:ex}
+\end{figure}
+
+As we can see in figure \ref{fig:ex}, in the first case both $Y$ and $Z$ receives information only from $X$, for which it is obvious that $Y$ and $Z$ process the same information and then the two nodes synchronize their states (again not considering the details of the dynamics).
+However, if we allow that $Y$ sends information to $Z$ along with $X$, then $Z$ do not process the same information than $Y$, since it receives information from $X$ and $Y$, while $Y$ receives only from $X$ (\ref{fig:ex}b).
+To get around this inconvenience, we can simply add an autorregulation loop for node $Y$, allowing that $Y$ and $Z$ synchronize again (\ref{fig:ex}c).
+
+All this discussion can be put on solid ground by considering the isomorphic relations between the input-trees of each node in the network.
+It is possible to note in figure (\ref{fig:inputex}a) and (\ref{fig:inputex}c) that the nodes $Y$ and $Z$ have isomorphic input-trees, which imply that the two nodes have synchronized states.
+Important to mention that because the addition of the autorregulation loop in the node $Y$, the input-tree that includes this loop becomes of infinite height, meaning the information loop flow in this directed link.
 
@@
 	\centering
-	\includegraphics[scale=0.4]{Figures/ex1.png}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.4]{Figures/ex2.png}
+	\subfloat[]{{\includegraphics[scale=0.32]{Figures/ex1input.png}}}
+	\qquad
+	\subfloat[]{{\includegraphics[scale=0.32]{Figures/ex2input.png}}}
+	\qquad
+	\subfloat[]{{\includegraphics[scale=0.32]{Figures/ex3input.png}}}
+	\caption{First trial network example.
+Containing a total of $N = 17$ nodes and $M = 22$ arcs, the network has two weakly connected components, defined as the connected networks when we treat all the directed arcs as undirected edges.
+For each non-trivial fiber I give the same color for the nodes belonging to it.}
+	\label{fig:inputex}
 \end{figure}
 
-Nullam semper quam at ante convallis posuere.
-Ut faucibus tellus ac massa luctus consectetur.
-Nulla pellentesque tortor et aliquam vehicula.
-Maecenas imperdiet euismod enim ut pharetra.
-Suspendisse pulvinar sapien vitae placerat pellentesque.
-Nulla facilisi.
-Aenean vitae nunc venenatis, vehicula neque in, congue ligula.
+In practice, to identify if two nodes belongs to the same network fiber, \textit{i.
+e.}, if two nodes have isomorphic input-trees is only necessary to check the first-layer of their input-tree, called input-set \cite{norris1995}, which means that if two nodes belong to the same fiber block they have the same number of incoming links from the same fibers nodes.
+That implies that is not necessary that incoming neighbors be the same nodes, being only necessary that the incoming fibers are the same.
 
-Pellentesque quis neque fringilla, varius ligula quis, malesuada dolor.
-Aenean malesuada urna porta, condimentum nisl sed, scelerisque nisi.
-Suspendisse ac orci quis massa porta dignissim.
-Morbi sollicitudin, felis eget tristique laoreet, ante lacus pretium lacus, nec ornare sem lorem a velit.
-Pellentesque eu erat congue, ullamcorper ante ut, tristique turpis.
-Nam sodales mi sed nisl tincidunt vestibulum.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.4]{Figures/ex1input.png}
-\end{figure}
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.4]{Figures/ex2input.png}
-\end{figure}
+At last, the identification of network fibration building blocks on biological regulatory networks is important because it allows the recognition of their information-processing building blocks, which is essential for the understanding of the functionalities intrisic to these regulatory network \cite{transistor2019}.
+Moreover, this approach can offer a persistent procedure to the study of biological function in networks comparing with methods based on statistical significance of common occurring subnetworks, like the one presented by the network motifs \cite{motifs2002}.
+The computational approach for a proper identification and classification of fibers in directed networks are explained below.
 
@@
 The network has $N = |V|$ nodes that can have connections with one another defined by the set $E$, which contains $M = |E|$ ordered pair of nodes, denoting the directed links between the network nodes.
-Considering the network, we can define a graph partition $\bar{P}$ over $V$ as a set of pairwise disjoints subsets of $V$ whose union is all $V$, that is
+Considering a network, we can define a graph partition $\bar{P}$ over $V$ as a set of pairwise disjoints subsets of $V$ whose union is all $V$, that is
 \begin{equation}
@@
 where $P_i$ are the elements of the partition $\bar{P}$, called blocks.
-Considering this, if we take an additional graph partition $\bar{Q}$ that has the property that all of its blocks are contained in a block of $\bar{P}$, we say that $\bar{Q}$ is a refinement partition of $\bar{P}$.
+If we take an additional graph partition $\bar{Q}$ that has the property that all of its blocks are contained in a block of $\bar{P}$, we say that $\bar{Q}$ is a refinement partition of $\bar{P}$.
+Moreover, for a block $B \in \bar{P}$, we say that the block $B$ is stable with respect a set $S$ if either all elements of $B$ connects with an element of $S$ or none element of $B$ points to any element of $S$.
 
-Moreover, for a block $B \in \bar{P}$, we say that the block $B$ is stable with respect with a set $S$ if either all elements of $B$ connects with an element of $S$ or none element of $B$ points to any element of $S$.
-The stability partition concept is central to the problem of relational coarsest refinement partitioning and can be easily extended to graph problems, where the coarsest graph partition problem is that of finding, for a given set of connections $E$ and an initial partition $\bar{P}$ over $V$, the coarsest stable refinement of $\bar{P}$, i.
-e., the minimal number of disjoint blocks subsets of $V$ that forms a stable refinement of $\bar{P}$.
+The stable partition concept is central to the problem of relational coarsest refinement partitioning and can be easily extended to graph problems, where the coarsest graph partition problem is that of finding, for a given set of directed links $E$ and an initial partition $\bar{P}$ over $V$, the coarsest stable refinement partition of $\bar{P}$, \textit{i.
+e.}, the minimal number of disjoint blocks subsets of $V$ that forms a stable refinement of $\bar{P}$.
 
@@
 \end{equation}
-where $E(\{x\})$ and $E^{-1}(\{x\})$ represents, respectively, the set of nodes that directly receives information from $x$, and the set of nodes that sends information, via a direct link, to $x$.
+where $E(\{x\})$ and $E^{-1}(\{x\})$ represents, respectively, the set of nodes that directly receives information from $x$, and the set of nodes that sends information, via a directed link, to $x$.
 
@@
 Since the finest partitioning possible is the one in which every node is itself a block, the refinement step may be proceeded at most $N-1$ times, guaranting that the algorithm terminates with the correct answer, since stability is inherited by the refinement process.
-However, to guarantees that the algorithm has a optimal runtime we have to find a efficient way to select the appropriate sets to the refinement step, without choosing repeated ones.
+However, to guarantee that the algorithm has an optimal runtime we have to find a efficient way to select the appropriate sets to the refinement step, without choosing repeated ones.
 Fortunately, this can be easily done for the construction of a input-tree stable partition.
@@
 where the number of splitted block must be larger than one to a proper splitting process take place.
-Then, for each unstable block $B \in \bar{P}$ all the splitted block, except the largest one, can be put at the back of a queue to be used ahead in the algorithm as a refinement set.
-This ensures that none repeated sets or union of repeated sets can be used during the algorithm exeecution.
+Then, for each unstable block $B \in \bar{P}$, all the splitted block, except the largest one, can be put at the back of a queue to be used ahead in the algorithm as a refinement set.
+This ensures that none repeated sets or union of repeated sets can be used during the algorithm execution.
 
-Finally, the complete algorithm to find the correct network fibers of a network $G(V, E)$ consists in initializing a graph partition $\bar{P}$ over all nodes from $V$ except the nodes that do not receive information from any other node, in which each one of these will be defined as isolated fibers already in the beginning of the algorithm.
-The partition $\bar{P}$ is defined as one block containing all the other nodes in the network.
-The algorithm maintains a queue $L$ of possible refinement sets, initially containing the single block of $\bar{P}$ and all the isolated blocks defined at the beginning.
-Then, we proceed as
-\begin{quotation}
-	\textbf{Coarsest Refinement Algorithm}: Remove from $L$ its first set $S$.
-Replace $\bar{P}$ by the \textit{I-split($S$, $\bar{P}$)}.
-Whenever a block $B \in \bar{P}$ splits into two or more nonempty blocks, add all but the largest to the back of $L$.
-\end{quotation}
-And this process is repeated until the queue $L$ is empty.
-At this point, the resulted partition $\bar{P}$ represents the coarsest input-tree stable partitioning of the network $G(V, E)$, where each block represents a network fiber with all its nodes having isomorphic input-trees.
-The figure \ref{fig:split} displays the splitting operation at the beginning of the refinement algorithm for a small network example.
-
-\begin{figure}
+\begin{figure}[t]
 	\centering
-	\includegraphics[scale=0.3]{Figures/test.png}
+	\includegraphics[scale=0.28]{Figures/split-function.png}
 	\caption{A refinement step for the split function.
@@
 
+Finally, the complete algorithm to find the correct network fibers of a network $G(V, E)$ consists in initializing a graph partition $\bar{P}$ over all nodes from $V$ except the nodes that do not receive any information from other node, in which each one of these will be defined as isolated fibers already in the beginning of the algorithm.
+Besides these solitaire nodes, we also identify the nodes that receive information only from themselves and put them in the queue as refinement sets, without isolating them from the main partition $\bar{P}$.
+This way, the partition $\bar{P}$ is defined as one block containing all the nodes that receive information, even if only from themselves.
+The algorithm maintains a queue $L$ of possible refinement sets, initially containing the single block of $\bar{P}$ and all the isolated blocks defined at the beginning.
+Then, we proceed as
+\begin{quotation}
+	\textbf{Coarsest Refinement Partitioning Algorithm}: Remove from $L$ its first set $S$.
+Replace $\bar{P}$ by the \textit{I-split($S$, $\bar{P}$)}.
+Whenever a block $B \in \bar{P}$ splits into two or more nonempty blocks, add all except the largest to the back of $L$.
+\end{quotation}
+And this process is repeated until the queue $L$ is empty.
+At this point, the resulted partition $\bar{P}$ represents the coarsest input-tree stable partitioning of the network $G(V, E)$, where each block represents a network fiber with all its nodes having isomorphic input-trees.
+The figure \ref{fig:split} displays the splitting operation at the beginning of the refinement algorithm for a small network example.
+
 % faltou o preprocessing.
@@
 
-Next, I apply the above algorithm for the genetic regulatory network of the \textit{Escherichia Coli} bacteria.
+Given the description above, next, I apply the above algorithm for the genetic regulatory network of the \textit{Escherichia Coli} bacteria.
 The obtention of this genetic network is through the transcriptional regulatory interaction data, where each gene is regulated by a transcription factor protein.
@@
 Together with the queue of blocks $L$, these constructions are the main data structures necessary for an efficient implementation of the refinement partitioning algorithm.
-At the beginning of the algorithm, we enqueue all the blocks of $\bar{P'}$ e $\bar{P''}$ to $L$ (order is not important for the output correctness).
-Then, we start the algorithm initializing a partition $\bar{Q} = \bar{P''}$ and by removing the first element set $S$ of $L$, and we apply the \textit{I-split($S$, $\bar{Q}$)} function to identify the input-tree unstable blocks of $\bar{Q}$ and to split them into input-tree stable blocks with respect to $S$.
+At the beginning of the algorithm, we enqueue all the blocks of $\bar{P'}$ e $\bar{P''}$ to $L$ (order is not important for the output correctness), where the nodes that receives information only from themselves, $E^{-1}(\{v\}) = \{v\}$, are pushed to $L$ as single-node refinement blocks.
+Then, we start the algorithm initializing a partition $\bar{Q} = \bar{P''}$ and by removing the first element set $S$ of $L$, to apply the \textit{I-split($S$, $\bar{Q}$)} function to identify the input-tree unstable blocks of $\bar{Q}$ and to split them into input-tree stable blocks with respect to $S$.
 After that, all the splitted blocks are pushed to the end of $L$, with exception the largest resulted blocks for each splitted block.
@@
 	\SetKwInOut{Input}{Input}
+	\SetKwInOut{Output}{Output}
 	\Input{A network $G(V, E)$}
+	\Output{The minimal fibration partition $\bar{Q}$ of $G(V,E)$}
 	%\KwResult{}
@@
 	Initialize $L$ as an empty queue\;
-	Initialize $\bar{P}$, $\bar{P'}$, $\bar{P''}$, $\bar{Q}$ as empty partitions\;
-	$B' = \{ \{ w \} \in V : |E^{-1}(\{w\})|=0 \}$\;
+	Initialize $\bar{P'}$, $\bar{P''}$, $\bar{Q}$ as empty partitions\;
+	$\forall w_i \in V \Rightarrow B'_{i} = \{ w_i : |E^{-1}(\{w_i\})|=0 \}$\;
+	$\forall v_i \in V \Rightarrow A_i = \{ v_i : E^{-1}(\{v_i\}) = \{v_i\} \}$\;
 	$B'' = \{ v \in V : |E^{-1}(\{v\})| \geq 1 \}$\;
-	\textit{push} all $B'$ to $\bar{P'}$\;
+	\textit{push} all $B'_{i}$ to $\bar{P'}$\;
 	\textit{push} $B''$ to $\bar{P''}$\;
 	\textit{enqueue} $B'' \in \bar{P''}$ to $L$\;
+	\textit{enqueue} all $A_i$ to $L$\;
 	\textit{enqueue} all blocks $B' \in \bar{P'}$ to $L$\;
@@
 The first example is showed at the figure \ref{fig:result1}.
-This network is disconnected, containing two main weakly connected components, and in addition contains only positive regulation between the interactions between the genes, showing the simpler case where the connections between nodes in a network are all of the same type.
+This network is disconnected, containing two main weakly connected components, and in addition contains only positive regulation for the interactions between the genes, showing the simpler case where the connections between nodes in a network are all of the same type.
 In this case, we find five non-trivial fibers, that is, fibers with size larger than one.
@@
 
-Labelling the resulted fiber distribution for the first example in figure \ref{fig:result1}, we obtain the following fibration classification for each fibratiion building block of the network containing more than one node:
+Labelling the resulted fiber distribution for the first example in figure \ref{fig:result1}, we obtain the following fibration classification for each fibration building block of the network containing more than one node:
 
@@
 If we consider the fiber $3$, besides the inner autoregulation loop we have a loop information going outside the fiber and going back through an external regulator inside the fiber $1$.
-In cases like this the branching ratio of the fiber has a fractal value represented by a golden ratio $\phi_d$ resulted by a cycle of information represented by a fibonacci sequence.
+In cases like this the branching ratio of the fiber has a fractal value given by a golden branch ratio $\phi_d$ resulted by a cycle of information represented by a fibonacci sequence.
 This way, fiber $3$ can be classified by the values $| \phi_d, \ell = 2 \rangle$ where the fiber has two external regulator nodes.
@@
 	\centering
-	\includegraphics[scale=0.3]{Figures/result2.png}
+	\includegraphics[scale=0.275]{Figures/result2.png}
 \end{figure}
@@
 	\centering
-	\includegraphics[scale=0.3]{Figures/result2-label.png}
+	\includegraphics[scale=0.275]{Figures/result2-label.png}
 \end{figure}
@@
 In the table X I provide the classification for each fibration building block obtained for the whole bacteria network, including, of course, the fibers presented in the figure \ref{fig:result3-1}.
-In total, I have found $84$ non-trivial fiber groups containing a total of $462$ nodes, obtaining a characteristic fiber statistics for the \textit{Escherichia Coli} network data.
+In total, I have found $92$ non-trivial fiber groups containing a total of $416$ nodes, obtaining a characteristic fiber statistics for the \textit{Escherichia Coli} network data.
 To guarantee the correctness of the fiber distribution found I calculated, after the refinement algorithm, the information received for each node inside the fibers and compares if each one process equivalent information.
 The result of this calculation is stored in the data file given at \url{https://github.com/higorsmonteiro/fiberblocks/blob/master/Data/fiberVerification.dat}, where for each node in a non-trivial fiber block I give the list of the nodes that sends information messages to the current node along with their fiber indexes and type of link values.
-Even though the algorithm implementation and the provided data above support the correctness of the results of this report, they shows a discrepancy comparing with the results exhibited at \cite{fibration2019} for the same regulatory network data.
+Thus, the results of this report show an equivalent fiber distribution over the network comparing with results exhibited at \cite{fibration2019} for the same regulatory network data.
+After the classification for each fiber is done, I notice that the $92$ fibers are reduced by one unit, because of the existence of a multilayered fiber compound by two fibers.
+This way, the number of fibers are consistent with \cite{fibration2019}.
 

### 2019-11-06 Manuscript/main.tex
going

@@
 
-% faltou o preprocessing.
-
-\subsection{Data preparation and algorithm implementation}
-
-Given the description above, next, I apply the above algorithm for the genetic regulatory network of the \textit{Escherichia Coli} bacteria.
-The obtention of this genetic network is through the transcriptional regulatory interaction data, where each gene is regulated by a transcription factor protein.
-Since a transcription factor in the cell is produced by a gene, it is possible to define directed relations between two genes if a gene is responsible for the production of a transcriptional factor, which regulates the other gene.
-Considering that a transcription factor can be either an activator(positive) or repressor(negative), or even behaves as both(dual), the directed links between genes can carry different types of information.
-Because of that, the partitioning algorithm must account for the type of message signals to construct appropriate stable input-trees for the network fibers.
-Therefore, for a proper application of the algorithm on the \textit{Escherichia Coli} genetic network, we label each node uniquely, either as numbers or string names, and also we do the same for each link with the type of connection between two genes.
-
-Given the regulatory directed network $G(V, E)$ to be partitioned in fibers, it is very important for the correctness of the algorithm that the nodes that do not receive any information, that is, the nodes that do not have any inward connections, be preprocessing as isolated blocks in a different partition.
-This means that the initial graph partition $\bar{P}$ must be divided in two different partitions $\bar{P'}$ e $\bar{P''}$, where the first one should contains all the single-node blocks containing the solitaire nodes $v$ for which $| E^{-1}(\{v\}) | = 0$, and the second contains at the beginning of the algorithm a single block containing all the other nodes $w$ in which $| E^{-1}(\{w\}) | \geq 1$.
-The importance of this preprocessing is to guarantee that solitaire nodes do not be put on the same fibers during the refinement steps, since for any subset $S \subseteq V$, the solitaire nodes satisfies the equality $| E^{-1}(\{v\}) \cap S | = 0$.
-Furthermore, even though the blocks of $\bar{P'}$ are used as refinement sets, $\bar{P'}$ is not used by the split function in any step.
-This way, the final graph partition of $G(V, E)$ is the union of $\bar{P'}$ and the result of the refinement partitioning of $\bar{P''}$, that is, the coarsest or minimal input-tree stable partition of $G$.
-
-After preprocessing the solitaire nodes, we have to define the data structures for the partition $\bar{Q}$ and its blocks $B$.
-We should define the implementation of a partition by a doubly-linked list of blocks, which allows that deletion of blocks be done in constante time $O(1)$ as long we have the block memory address during the procedure.
-A block is just a structure record containing indexing data along with a doubly-linked list containing all the nodes that belongs to it.
-Together with the queue of blocks $L$, these constructions are the main data structures necessary for an efficient implementation of the refinement partitioning algorithm.
-At the beginning of the algorithm, we enqueue all the blocks of $\bar{P'}$ e $\bar{P''}$ to $L$ (order is not important for the output correctness), where the nodes that receives information only from themselves, $E^{-1}(\{v\}) = \{v\}$, are pushed to $L$ as single-node refinement blocks.
-Then, we start the algorithm initializing a partition $\bar{Q} = \bar{P''}$ and by removing the first element set $S$ of $L$, to apply the \textit{I-split($S$, $\bar{Q}$)} function to identify the input-tree unstable blocks of $\bar{Q}$ and to split them into input-tree stable blocks with respect to $S$.
-After that, all the splitted blocks are pushed to the end of $L$, with exception the largest resulted blocks for each splitted block.
-As we have mentioned, the algorithm terminates when there is no more sets in $L$.
-This is the whole algorithm, even though the implementation of the \textit{I-split} function might not be so straightforward, since a given block $B$ can be splitted into an arbitrary number of blocks of different sizes.
-Considering this, I propose in the pseudocode \ref{alg:split} an efficient implementation construction to the splitting function.
-
 \begin{algorithm}[t]
@@
 
-In the algorithm \ref{alg:split} above, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output.
-Besides its list of nodes, a block $X$ should have another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$.
-This way, a node $w$ belonging to the block splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm \ref{alg:split}.
-In cases where the type of connections are non-trivial, i.
-e., there is more than one type of message signal, the attribute $X(E)$ can be replaced by a list $X(E(i))$ for each type $i$ of message presented in the network.
-For that situation, the conditional line $7$ must be verified for all types of connnections: $\exists \ X \in \bar{T} : | E_k^{-1}(\{w_i\})\cap S | = X(E(k))$.
+\subsection{Data preparation and algorithm implementation}
 
-Finally, considering all the discussion and implementation presented above, we can explicit the complete algorithm in just a few basic steps in algorithm \ref{alg:partitioning}.
+Given the description above, next, I apply the above algorithm for the genetic regulatory network of the \textit{Escherichia Coli} bacteria.
+The obtention of this genetic network is through the transcriptional regulatory interaction data, where each gene is regulated by a transcription factor protein.
+Since a transcription factor in the cell is produced by a gene, it is possible to define directed relations between two genes if a gene is responsible for the production of a transcriptional factor, which regulates the other gene.
+Considering that a transcription factor can be either an activator(positive) or repressor(negative), or even behaves as both(dual), the directed links between genes can carry different types of information.
+Because of that, the partitioning algorithm must account for the type of message signals to construct appropriate stable input-trees for the network fibers.
+Therefore, for a proper application of the algorithm on the \textit{Escherichia Coli} genetic network, we label each node uniquely, either as numbers or string names, and also we do the same for each link with the type of connection between two genes.
 
-A concrete implementation of the algorithm in a programming language is presented at the link \url{https://github.com/higorsmonteiro/fiberblocks} together with \textit{E.
-Coli} prepared data and another trial network examples.
-Further information about the application of the codes in other genetic regulatory network data can be found at the same link given.
+Given the regulatory directed network $G(V, E)$ to be partitioned in fibers, it is very important for the correctness of the algorithm that the nodes that do not receive any information, that is, the nodes that do not have any inward connections, be preprocessing as isolated blocks in a different partition.
+This means that the initial graph partition $\bar{P}$ must be divided in two different partitions $\bar{P'}$ e $\bar{P''}$, where the first one should contains all the single-node blocks containing the solitaire nodes $v$ for which $| E^{-1}(\{v\}) | = 0$, and the second contains at the beginning of the algorithm a single block containing all the other nodes $w$ in which $| E^{-1}(\{w\}) | \geq 1$.
+The importance of this preprocessing is to guarantee that solitaire nodes do not be put on the same fibers during the refinement steps, since for any subset $S \subseteq V$, the solitaire nodes satisfies the equality $| E^{-1}(\{v\}) \cap S | = 0$.
+Furthermore, even though the blocks of $\bar{P'}$ are used as refinement sets, $\bar{P'}$ is not used by the split function in any step.
+This way, the final graph partition of $G(V, E)$ is the union of $\bar{P'}$ and the result of the refinement partitioning of $\bar{P''}$, that is, the coarsest or minimal input-tree stable partition of $G$.
 
-\begin{algorithm}[h]
+After preprocessing the solitaire nodes, we have to define the data structures for the partition $\bar{Q}$ and its blocks $B$.
+We should define the implementation of a partition by a doubly-linked list of blocks, which allows that deletion of blocks be done in constante time $O(1)$ as long we have the block memory address during the procedure.
+A block is just a structure record containing indexing data along with a doubly-linked list containing all the nodes that belongs to it.
+Together with the queue of blocks $L$, these constructions are the main data structures necessary for an efficient implementation of the refinement partitioning algorithm.
+At the beginning of the algorithm, we enqueue all the blocks of $\bar{P'}$ e $\bar{P''}$ to $L$ (order is not important for the output correctness), where the nodes that receives information only from themselves, $E^{-1}(\{v\}) = \{v\}$, are pushed to $L$ as single-node refinement blocks.
+Then, we start the algorithm initializing a partition $\bar{Q} = \bar{P''}$ and by removing the first element set $S$ of $L$, to apply the \textit{I-split($S$, $\bar{Q}$)} function to identify the input-tree unstable blocks of $\bar{Q}$ and to split them into input-tree stable blocks with respect to $S$.
+After that, all the splitted blocks are pushed to the end of $L$, with exception the largest resulted blocks for each splitted block.
+As we have mentioned, the algorithm terminates when there is no more sets in $L$.
+This is the whole algorithm, even though the implementation of the \textit{I-split} function might not be so straightforward, since a given block $B$ can be splitted into an arbitrary number of blocks of different sizes.
+Considering this, I propose in the pseudocode \ref{alg:split} an efficient implementation construction to the splitting function.
+
+\begin{algorithm}[!t]
 	\SetAlgoLined
@@
 \end{algorithm}
+
+In the algorithm \ref{alg:split}, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output.
+Besides its list of nodes, a block $X$ should have another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$.
+This way, a node $w$ belonging to the block splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm \ref{alg:split}.
+In cases where the type of connections are non-trivial, i.
+e., there is more than one type of message signal, the attribute $X(E)$ can be replaced by a list $X(E(i))$ for each type $i$ of message presented in the network.
+For that situation, the conditional line $7$ must be verified for all types of connnections: $\exists \ X \in \bar{T} : | E_k^{-1}(\{w_i\})\cap S | = X(E(k))$.
+
+Finally, considering all the discussion and implementation presented above, we can explicit the complete algorithm in just a few basic steps in algorithm \ref{alg:partitioning}.
+
+A concrete implementation of the algorithm in a programming language is presented at the link \url{https://github.com/higorsmonteiro/fiberblocks} together with \textit{E.
+Coli} prepared data and another trial network examples.
+Further information about the application of the codes in other genetic regulatory network data can be found at the same link given.
+
+\subsection{Branching ratio determination}
+
+After the proper identification of the fibers over the network, we should classify each fiber according to two fundamental values: the fundamental class number $n$ and the subclass number $\ell$.
+The subclass value is easily obtained, since it represents the number of external nodes that directly regulates the fiber.
+The fundamental class, however, may be no so straightforward to calculate if one chooses an eigenvalue decomposition algorithm of the adjacency matrix $\mathbf{A}$ characteristic of the network.
+The value of $n$  is directly related to cycles of information in the network, quantifying the loops of the fibers.
+At the same time, $n$ is also the branching ratio of the fiber input-tree, where the ratio is defined by the number of nodes $a_{j+1}$ belonging to a given height level $j+1$ of the input-tree and the number of nodes $a_j$ at the below height $j$ for large enough $j \rightarrow \infty$.
+This way, the branching ratio is defined as
+\begin{equation}
+	n = \lim _{j \rightarrow \infty}\bigg(\dfrac{a_{j+1}}{a_j}\bigg)
+\end{equation}
+where $n$ can be either an integer branching ratio or a golden fibonacci ratio resulted by longer loop pathways with size $d \geq 2$.
+
+Concerning that, here I propose an efficient and simple method to calculate the value of $n$ by counting the number of nodes in each height level of the input-tree of a given node.
+For infinite input-trees, \textit{i.
+e.}, for fibers with loops, the algorithm performs the calculation in each tree level until a determined precision is reached, defined by a small value $\delta < 1$.
+The aim of the algorithm is, for each step, build two following layers of the input-tree in order to calculate directly the value of $n$ by counting the number of nodes $a_j$ and $a_{j+1}$ presented in each of these layers.
+We define $n_j$ as the ratio $\frac{a_{j+1}}{a_j}$.
+The algorithm will stop when $|n_j - n_{j-1}| < \delta$.
+
+The implementation of the algorithm is quite simple, making use of only one type of data structures: stacks.
+The algorithm consists of two steps, the first one being the verification of the existence of loops on the input-tree, from which only if this verification is true we go to the second step.
+The existence of loops in the input-tree implies an infinite tree.
+After that, starting from the root node $v$ of the input-tree, we find its nearest incoming neighbors $E^{-1}(\{v\})$ and store them in a first stack $S_1$, representing this way the first layer of the input-tree, from which we can obtain the value of its size $a_1$.
+Next, we pop each element of $S_1$ and get their incoming neighbors $E^{-1}(\{pop(S_1)\})$ and store them in $S_2$ until $S_1$ is empty.
+Then, $S_2$ will store the second layer of the input-tree, from which we get its $a_2$, allowing the calculation of $n_2$.
+Since at this time $S_1$ is empty, we get the incoming neighbors of each element of $S_2$ and stores in $S_1$, and this process is repeated, exchanging $S_1$ e $S_2$ as incoming neighbors supplier and deposit.
+This way, we can calculate indefinetely the values of $n_j$ until the precision is good enough.
+Of course, the precision $\delta$ will be only useful for fibonacci fibers, since integer branching ratio fibers will satisfy the precision right way, since $n_3 = n_2$ for these fibers.
+The algorithm pseudocode implementation is given in \ref{alg:branchratio}.
+
+\begin{algorithm}[!b]
+	\SetAlgoLined
+	\SetKwInOut{Input}{Input}
+    \SetKwInOut{Output}{Output}
+	\Input{A node $v \in V$ for a network $G(V, E)$}
+    \Output{$n$ representing the branching ratio of the node $v$ input-tree}
+    Initialize $\mathbf{s_1}$ and $\mathbf{s_2}$ as empty stacks\;
+	Initialize $\mathbf{Sup}$, $\mathbf{Depot}$ and $\mathbf{Aux}$ as stack pointers\;
+	\eIf{\text{checkloop(v)} $=$ TRUE}
+	{
+		$n_j, n_{j+1} \leftarrow 0.0$\;
+		push($\mathbf{s_1}$, v)\;
+		$\mathbf{Sup} \leftarrow \mathbf{s_1}$\;
+		$\mathbf{Depot}$ $\leftarrow$ $\mathbf{s_2}$\;
+		\While{$| n_{j+1} - n_j | > \delta$ \textbf{or} $n_{j+1} = 0$ }
+		{
+			$a_j \leftarrow |\mathbf{Sup}|$\;
+			$n_j \leftarrow n_{j+1}$\;
+			\While{ $|\mathbf{Sup}| \neq 0$}
+			{
+				$u \leftarrow $ pop($\mathbf{Sup}$)\;
+				$\forall w \in E^{-1}(\{u\}) \Rightarrow$ push($\mathbf{Depot}$, $w$)\;
+			}
+			$a_{j+1} \leftarrow |\mathbf{Depot}|$\;
+			$n_{j+1} \leftarrow \bigg(\dfrac{a_{j+1}}{a_j}\bigg)$\;
+			$\mathbf{Aux} \leftarrow \mathbf{Depot}$\;
+			$\mathbf{Depot} \leftarrow \mathbf{Sup}$\;
+			$\mathbf{Sup} \leftarrow \mathbf{Aux}$\;
+		}
+	}
+	{
+		$n_{j+1} \leftarrow 0$\;
+	}
+	$n \leftarrow n_{j+1}$\;
+	\caption{Input-tree branching ratio determination}
+	\label{alg:branchratio}
+\end{algorithm}
+
+The checkloop($v$) function can be easily implemented through a Depth-First Search or Breadth-First Search algorithm for the node $v$ to find its strongly connected component.
+This means that starting from the root node $v$, the algorithm traverse only the neighbors that points to the current node.
+Therefore, the algorithm presented above has a linear runtime complexity with the size of the tree.
+Its worst-case scenario is modulated by the $\delta$ precision factor only for fibonacci fibers, since these fibers are represented by fractal $n = \phi_d$ values, where $d$ is the size of the information cycle.
 

### 2019-11-06 Code/fibrationf.h

@@ -17,6 +17,87 @@
 #include "structforfiber.h"
 #define SENTINEL -96
 
+int CHECKLOOP(int root, Graph* graph)
+{
+	int i;
+	NODELIST* scc_nodes = NULL;
+	KOSAJARU(&scc_nodes, root, graph);
+	int size = GetListSize(scc_nodes);
+	if(size>1) return 1;	// The 'root' input-tree is infinite.
+	else
+	{
+		int n_in = GETNin(graph, root);
+		int* neighbors = GET_INNEIGH(graph, root);
+		for(i=0; i<n_in; i++) if(neighbors[i]==root) return 1;
+		return 0; // The 'root' does not have self-loops.
+	} 
+}
+
+extern double BRANCH_RATIO(BLOCK* block, Graph* graph, double delta)
+{
+	int i, j;
+	int a_before, a_after;
+	double n, n_before, n_after;
+	PART* current_part;
+	
+	STACK* s1 = NULL;
+	STACK* s2 = NULL;
+	STACK* aux = NULL;
+	STACK* sup = NULL;
+	STACK* depot = NULL;
+	int v = block->head->data;
+
+	int bool_inputloop = CHECKLOOP(v, graph);
+	if(bool_inputloop==1)
+	{
+		n_before = 0.000;
+		n_after = 0.000;
+		push(&s1, v);
+		sup = s1;
+		depot = s2;
+		int control = 0;
+		while(fabs(n_after-n_before)>delta || n_after<0.001)
+		{
+			control++;
+			if(control>8) break;
+			a_before = STACKSIZE(sup);
+			n_before = n_after;
+			while(sup)
+			{
+				int node = pop(&sup);
+				int n_in = GETNin(graph, node);
+				int* neigh = GET_INNEIGH(graph, node);
+				for(i=0; i<n_in; i++) push(&depot, neigh[i]);
+				free(neigh);
+			}
+			a_after = STACKSIZE(depot);
+			n_after = (1.0*a_after)/(a_before);
+			printf("%d\n", a_after);
+			aux = depot;
+			depot = sup; // empty
+			sup = aux;
+
+		}
+	}
+	else
+	{
+		n_after = 0.0;
+	}
+	return n_after;
+}
+
+extern void DEF_FUNDAMENTAL(PART** partition, Graph* graph)
+{
+	double nloop;
+	PART* current_part;
+	NODELIST* nodelist;
[…]

### 2019-11-06 Code/minimalfiber.c

@@ -114,7 +114,8 @@ void main(int argv, char** argc)
 	CALCULATE_REGULATORS(&partition, graph);
 	CALCULATE_REGULATORS(&null_partition, graph);
 	// Calculates branch ratio number for each fiber block.
-	DEF_BRANCH_RATIO(&partition, graph);
+	DEF_FUNDAMENTAL(&partition, graph);
+	//DEF_BRANCH_RATIO(&partition, graph);
 	//////////////////////////////////////////////////////////////////////////////////////////
 	//////////////////////////////////////////////////////////////////////
 	
@@ -136,8 +137,8 @@ void main(int argv, char** argc)
 	/* With gene names */ //printGeneGraphInFibers(graph, partition, nodefibers);
 	/* Without gene names */ //printGraphInFibers(graph, partition, nodefibers);
 	
-	/* Classification Info */ ShowClassification(partition, 0);
-	/* Fiber blocks and classification info */ //ShowInfo(partition, 1);
+	/* Classification Info */ //ShowClassification(partition, 0);
+	/* Fiber blocks and classification info */ //ShowInfo(partition, 0);
 
 	/*	Show the number of non-trivial fibers	*/
 	//printf("%d %d\n", nontrivial_fibers, total_nodes);
@@ -146,6 +147,7 @@ void main(int argv, char** argc)
 	//PrintInNeighbors(graph, node);
 	//PrintOutNeighbors(graph, node);
 	//int n = GETNin(graph, node);
+
 	//printf("%d\n", n);
 	/////////////////////////////////////////////////////////////////////////////
 

### 2019-11-06 Code/utilsforfiber.h

@@ -283,7 +283,7 @@ extern int IDENTIFY_SOLITAIRE(Graph* graph, int node)
 ////////////////////////////////
 ////// STACK OPERATIONS ///////
 // To insert an element in the stack.
-extern void dopush(STACK** top, int node)
+extern void push(STACK** top, int node)
 {
 	STACK *ptr;
 	ptr = (STACK*)malloc(sizeof(STACK));
@@ -301,7 +301,7 @@ extern void dopush(STACK** top, int node)
 }
 
 // To delete an element in the STACK.
-extern int dopop(STACK** top)
+extern int pop(STACK** top)
 {
 	int v;
 	STACK *ptr;
@@ -313,6 +313,14 @@ extern int dopop(STACK** top)
 		free(ptr);
 	}
 	return v;
+}
+
+extern int STACKSIZE(STACK* top)
+{
+	int size = 0;
+	STACK* current;
+	for(current=top; current!=NULL; current=current->next) size++;
+	return size;
 }
 ////////////////////////////////////////////////////////
 ////////////////////////////////////////////////////////
@@ -426,24 +434,24 @@ extern void KOSAJARU(NODELIST** nodes_in_scc, int root, Graph* graph)
 
 	// DFS process in the network starting from the root node.
 	STACK* nodetocheck = NULL;
-	dopush(&nodetocheck, root);
+	push(&nodetocheck, root);
 	while(nodetocheck)
 	{
-		v = dopop(&nodetocheck);
+		v = pop(&nodetocheck);
 		if(visited[v]==0)
 		{
 			visited[v] = 1;
 			int n = GETNout(graph, v);
 			int* neigh_out = GET_OUTNEIGH(graph, v);
-			for(j=0; j<n; j++) dopush(&nodetocheck, neigh_out[j]);
+			for(j=0; j<n; j++) push(&nodetocheck, neigh_out[j]);
 			free(neigh_out);
 		}
 	}
 	// DFS process in the transpose network from the root node.
-	dopush(&nodetocheck, root);
+	push(&nodetocheck, root);
 	while(nodetocheck)
 	{
-		v = dopop(&nodetocheck);
+		v = pop(&nodetocheck);
 		if(visited[v]==1)
 		{
 			int check = doublycheck_element(*nodes_in_scc, v);
[…]

### 2019-11-06 Code/fibrationf.h
Progress

@@ -33,57 +33,87 @@ int CHECKLOOP(int root, Graph* graph)
 	} 
 }
 
-extern double BRANCH_RATIO(BLOCK* block, Graph* graph, double delta)
+
+int FIBERNODE_FOR_BRANCHING(PART* current_part, Graph* graph)
+{
+	NODELIST* nodelist;
+	NODELIST* regulators;
+	NODELIST* strong_component = NULL;
+
+	for(nodelist=current_part->block->head; nodelist!=NULL; nodelist=nodelist->next)
+	{
+		KOSAJARU(&strong_component, nodelist->data, graph);
+		for(regulators=current_part->regulators; regulators!=NULL; regulators=regulators->next)
+		{
+			int verify_reg_in_strong = doublycheck_element(strong_component, regulators->data);
+			if(verify_reg_in_strong==1) return nodelist->data;
+		}
+	}
+	return -1;
+}
+
+extern double BRANCH_RATIO(PART* block_info, Graph* graph, double delta)
 {
 	int i, j;
-	int a_before, a_after;
-	double n, n_before, n_after;
+	double n, n_j;
+	int a_top, a_bottom;
 	PART* current_part;
 	
+	/////////////////////
 	STACK* s1 = NULL;
 	STACK* s2 = NULL;
 	STACK* aux = NULL;
 	STACK* sup = NULL;
 	STACK* depot = NULL;
-	int v = block->head->data;
+	/////////////////////
 
+	int v = FIBERNODE_FOR_BRANCHING(block_info, graph);
+	int v = block_info->block->head->data;
+	printf("node %d\n", v);
 	int bool_inputloop = CHECKLOOP(v, graph);
+	NODELIST* scc;
+	KOSAJARU(&scc, v, graph);
+	printf("SCC: ");
+	printList(scc);
+	printf("\n");
+
+
 	if(bool_inputloop==1)
 	{
-		n_before = 0.000;
-		n_after = 0.000;
+		int ffseq_size = 0;
 		push(&s1, v);
 		sup = s1;
 		depot = s2;
-		int control = 0;
-		while(fabs(n_after-n_before)>delta || n_after<0.001)
+		while(ffseq_size<8)
 		{
-			control++;
-			if(control>8) break;
-			a_before = STACKSIZE(sup);
-			n_before = n_after;
+			ffseq_size++;
+			a_top = STACKSIZE(sup);
 			while(sup)
 			{
 				int node = pop(&sup);
[…]

### 2019-11-06 Code/minimalfiber.c

@@ -137,7 +137,7 @@ void main(int argv, char** argc)
 	/* With gene names */ //printGeneGraphInFibers(graph, partition, nodefibers);
 	/* Without gene names */ //printGraphInFibers(graph, partition, nodefibers);
 	
-	/* Classification Info */ //ShowClassification(partition, 0);
+	/* Classification Info */ ShowClassification(partition, 0);
 	/* Fiber blocks and classification info */ //ShowInfo(partition, 0);
 
 	/*	Show the number of non-trivial fibers	*/

### 2019-11-06 Code/utilsforfiber.h

@@ -256,11 +256,12 @@ extern int NinREG(Graph* graph, int node, int type)
 	return n_in;	
 }
 
-extern int CHECKLINK(Graph* graph, int pointing_node, int pointed_node)
+
+extern int CHECK_REGULATION(Graph* graph, int regulator, int regulated)
 {
 	NodeAdj* Node;
-	for(Node=graph->array[pointing_node].head_out; Node!=NULL; Node=Node->next)
-		if(Node->neighbor==pointed_node) return 1;
+	for(Node=(graph->array[regulator].head_out); Node!=NULL; Node=Node->next)
+		if(Node->neighbor==regulated) return 1;
 	return 0;
 }
 

### 2019-11-08 Manuscript/main.tex
Progress
Finishing

--- 2019-11-04 Manuscript/main.tex
@@
 \end{algorithm}
+
+In the algorithm \ref{alg:split}, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output.
+Besides its list of nodes, a block $X$ should have another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$.
+This way, a node $w$ belonging to the block splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm \ref{alg:split}.
+In cases where the type of connections are non-trivial, i.
+e., there is more than one type of message signal, the attribute $X(E)$ can be replaced by a list $X(E(i))$ for each type $i$ of message presented in the network.
+For that situation, the conditional line $7$ must be verified for all types of connnections: $\exists \ X \in \bar{T} : | E_k^{-1}(\{w_i\})\cap S | = X(E(k))$.
+
+Finally, considering all the discussion and implementation presented above, we can explicit the complete algorithm in just a few basic steps in algorithm \ref{alg:partitioning}.
+
+A concrete implementation of the algorithm in a programming language is presented at the link \url{https://github.com/higorsmonteiro/fiberblocks} together with \textit{E.
+Coli} prepared data and another trial network examples.
+Further information about the application of the codes in other genetic regulatory network data can be found at the same link given.
+
+\subsection{Input-tree branching ratio}
+
+After the proper identification of the fibers over the network, we should classify each one in accordance with two fundamental numbers: the fundamental class number $n$ and the subclass number $\ell$.
+The subclass value is easily obtained, since it represents the number of external nodes that directly regulates the fiber (all the fiber nodes).
+However, the fundamental class, or input-tree branching ratio, may be not so straightforward to calculate by a direct fiber neighborhood verification, since it involves the quantification of cycles of information that leaves a fiber and goes back to it.
+Fortunately, the value of $n$ can be obtained if one chooses an eigenvalue decomposition algorithm of the adjacency matrix $\mathbf{A}$ characteristic of the appropriate strongly connected component that includes the fiber.
+This way, $n$ is given by the largest eigenvalue $\lambda _{max}$ of the subnetwork containing the loop of the information coming out of the fiber.
+At the same time, $n$ is also the branching ratio of the fiber input-tree, where the ratio is defined by the number of nodes $Q_{j+1}$ belonging to a given layer level $j+1$ of the input-tree and the number of nodes $Q_j$ at the previous layer level $j$ for large enough $j \rightarrow \infty$.
+By this, the branching ratio is defined as
+\begin{equation}
+	n = \lim _{j \rightarrow \infty}\bigg(\dfrac{Q_{j+1}}{Q_j}\bigg)
+\end{equation}
+where $n$ can be either an integer branching ratio or a golden fibonacci ratio $\varphi_d$ resulted by external loop pathways with size $d \geq 2$.
+
+Concerning the definition above, an alternative approach to obtain the fundamental class number is by a direct construction of the input-tree fiber until a reasonable depth is reached.
+Here I propose a simple method to calculate the value of $n$ by counting the number of nodes $Q_j$ in each layer level $j$ of the input-tree of a given fiber node.
+For infinite input-trees, \textit{i.
+e.}, fibers containing inside or external loops, we use the fast convergence for both the integer and fibonacci ratios to let the limit depth of the input-tree fixed by a value $\delta$.
+For integer branching ratio, the value of $n$ is obtained exactly even for a small number of layers, while for fractal golden ratio the rate of convergence of $n$ to $\varphi_d$ is exponential, requiring also small number of layers for reasonable values of $\varphi_d$.
+The aim of the algorithm is, for each step, to build two following layers of the input-tree to calculate directly the value of $n$ by counting the number of nodes $Q_j$ and $Q_{j+1}$ presented in each of these layers.
+We define $n_j$ as the ratio $\frac{Q_{j+1}}{Q_j}$, and the algorithm stop when the the layer $j+1$ is equal to $\delta$.
+
+The algorithm consists of two steps, the first one being the verification of the existence of loops on the input-tree, from which only if it is true the algorithm goes to the second step.
+The existence of loops in the input-tree implies an infinite tree.
+For this, there are two cases possible: inside cycles of information, implying integer branching ratio $n$, and fibonacci cycles of information that leaves the fiber and then returns to it.
+This can be easily verified by identifying the strongly connected components that includes nodes of the fiber.
+If the strongly connected component contains only fiber nodes, then the branching is integer, otherwise is fractal.
+The constrast between these two cases is important for the correct construction of the input-tree, since for fibonacci cycles the algorithm must guarantee that only the nodes $w \in \Lambda$ belonging to the shortest cycle path and, of course, the nodes of the fiber will be placed on the input-tree, thus guaranting the correct $\varphi_d$ value.
+
+The implementation of the algorithm is quite simple, making use of only stacks to store the input-tree layers.
+Starting from the root node $v$ of the input-tree of the fiber $V_i$ and defined $\Lambda$ for the case of fibonacci cycles, we find its nearest incoming neighbors $E^{-1}(\{v\}) \in \Lambda$ and $E^{-1}(\{v\}) \in V_i$ and store them in a first stack $S_1$, representing this way the second layer $j = 1$ of the input-tree, from which we can obtain the value of its size $Q_1$.
+Next, we pop each element of $S_1$ and get their incoming neighbors $E^{-1}(\{v \leftarrow pop(S_1)\})$ and store them in $S_2$ until $S_1$ is empty.
+Then, $S_2$ will store the second layer $j = 2$ of the input-tree, from which $Q_2$ is obtained, allowing the calculation of $n_2$.
+Since at this time $S_1$ is empty, the incoming neighbors of each element of $S_2$ are stored in $S_1$ until $S_2$ is empty, and this process is repeated, exchanging $S_1$ e $S_2$ as incoming neighbors supplier and deposit in each loop step.
+This repeating exchange can be implemented with the help of stacks pointers to represent, in each algorithm loop, the supplier and deposit stacks.
+This way, we can calculate the values of $n_j$ until the limit depth $j+1 > \delta$ is reached.
+The algorithm pseudocode implementation is given in \ref{alg:branchratio}.
+
+The algorithm \ref{alg:branchratio} assumes that the given node $v$ is part of a strongly connected component, even for the trivial case containing only $v$ connected to itself, because this warrant that $n \neq 0$.
+This can be easily verified implementing a Depth-First Search or Breadth-First Search on the network and its tranpose starting at node $v$ to find its strongly connected component, which takes linear time with the size of the strongly connected component.
+Then, for components containing only fiber nodes the algorithm obtain the correct integer $n$ for small $\delta$ limit tree depth, running linearly with $|E^{-1}(\{V_{SCC}\}) \in \Lambda|$.
+For component containing outsider nodes, then we define $\Lambda$ containing the nodes in the shortest loop \ref{fig:branch} and apply the above algorithm.
+Of course, for fibonacci loops, determining the size $s$ of the shortest loop already gives indirectly the information $\varphi_s$ needed, being necessary only to define previously a table with the relations $s \rightarrow \varphi_s$.
+
+\begin{algorithm}[!h]
+	\SetAlgoLined
+	\SetKwInOut{Input}{Input}
+    \SetKwInOut{Output}{Output}
+	\Input{A node $v \in V$ for a network $G(V, E)$}
+    \Output{$n$ representing the branching ratio of the node $v$ input-tree}
+    Initialize $\mathbf{s_1}$ and $\mathbf{s_2}$ as empty stacks\;
+	Initialize $\mathbf{Sup}$, $\mathbf{Depot}$ and $\mathbf{Aux}$ as stack pointers\;
+	$j \leftarrow 0$\;
+	push($\mathbf{s_1}$, $v$)\;
+	$\mathbf{Sup} \leftarrow \mathbf{s_1}$\;
+	$\mathbf{Depot}$ $\leftarrow$ $\mathbf{s_2}$\;
+	\While{$j+1 \leq \delta$ }
+	{
+		$a_j \leftarrow |\mathbf{Sup}|$\;
+		\While{ $|\mathbf{Sup}| \neq 0$}
+		{
+			$u \leftarrow $ pop($\mathbf{Sup}$)\;
+			\If{$w \in \Lambda : \forall w \in E^{-1}(\{u\})$}
+			{
+				push($\mathbf{Depot}$, $w$)\;
+			}
+		}
+		$a_{j+1} \leftarrow |\mathbf{Depot}|$\;
+		$n_{j+1} \leftarrow \bigg(\dfrac{a_{j+1}}{a_j}\bigg)$\;
+		$\mathbf{Aux} \leftarrow \mathbf{Depot}$\;
+		$\mathbf{Depot} \leftarrow \mathbf{Sup}$\;
+		$\mathbf{Sup} \leftarrow \mathbf{Aux}$\;
+		$j \leftarrow j + 1$\;
+	}
+	\caption{Input-tree branching ratio determination}
+	\label{alg:branchratio}
+\end{algorithm}
+
+The approach given represents an alternative and direct method to obtain the fundamental class number $n$ and, even though not the most convenient, can improve the runtime of the classification comparing with spectral decomposition methods, for which the fastest algorithm runs in quadratic time with the size of the subnetwork used.
+However, I am aware that the improvements may not affect significantly the perfomance of the algorithm, since the average size of the subnetworks used for the calculations are generally very small.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.32]{Figures/input.png}
+\end{figure}
 
@@
 Then, by labelling each fiber with an index or color we can then construct the fibration building blocks through the calculation of the fundamental class number $n$ and through the subclass number $\ell$.
-Again, a fibration building block is defined as the nodes belonging to a fiber and all the $\ell$ external nodes that directly regulates at least one node of the current fiber.
-With that, we calculate the fundamental class number $n_k$ of the fiber $k$ by building the adjacency matrix $\mathbf{A}^{k}$ of its fibration building block and then calculating the largest eigenvalue of it.
+Again, a fibration building block is defined as the nodes belonging to a fiber and all the $\ell$ external nodes that directly regulates all nodes of the current fiber.
+With that, I calculated the fundamental class number $n_k$ of the fiber $k$ by applying the algorithm described in \ref{alg:branchratio} over the strongly connected component of the fiber node that sends information to at least one of its regulators.
 The value of $n$ quantifies the information cycles of the fibration building blocks and it can be either represent integer branching ratios or fractal golden ration of their input-tree topology class.
@@
 If we consider the fiber $3$, besides the inner autoregulation loop we have a loop information going outside the fiber and going back through an external regulator inside the fiber $1$.
-In cases like this the branching ratio of the fiber has a fractal value given by a golden branch ratio $\phi_d$ resulted by a cycle of information represented by a fibonacci sequence.
-This way, fiber $3$ can be classified by the values $| \phi_d, \ell = 2 \rangle$ where the fiber has two external regulator nodes.
+In cases like that one the branching ratio of the fiber has a fractal value given by a golden branch ratio $\varphi_d$ resulted by a cycle of information represented by a fibonacci sequence.
+This way, fiber $3$ can be classified by the values $| \varphi_d, \ell = 2 \rangle$ where the fiber has two external regulator nodes.
 The fibration classification for the non-trivial fibers is showed in the table \ref{tab:r2}.
@@
 Thus, the results of this report show an equivalent fiber distribution over the network comparing with results exhibited at \cite{fibration2019} for the same regulatory network data.
-After the classification for each fiber is done, I notice that the $92$ fibers are reduced by one unit, because of the existence of a multilayered fiber compound by two fibers.
-This way, the number of fibers are consistent with \cite{fibration2019}.
+Even though the table IV an V of \cite{fibration2019} show a total number of $91$ fibers and the total number of $414$ of nodes inside non-trivial fibers, the authors \href{https://docs.google.com/spreadsheets/d/1-RG5vR_EGNPqQcnJU8q3ky1OpWi3OjTh5Uo-Xa0PjOc/edit#gid=1973910256}{spreadsheet} reports the total of $416$ nodes, a mismatch which is caused in this report by the presence of a additional fiber of size two and classified as $| 1.6181..., 7 \rangle$ containing the genes \textit{marR} e \textit{marA}.
+This way, the number of nodes in fibers and the genes inside each one are consistent with the results showed in \cite{fibration2019}.
 
-The statistics concerning the fundamental class number and the external regulators of each fibration block on the network is given in the table X, showing \textcolor{red}{describe the pattern of the statistics of the table that concerns the bacteria fiber statistics}.
+The statistics concerning the fundamental class number and the external regulators of each fibration block on the network is given in the table \ref{tab:fiberstats}, showing the additional fiber not reported in \cite{fibration2019}.
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}[b]{lc}\hline
+		Structure Fiber & Amount in E. Coli  \\ \hline
+		$| n = 0, \ell = 1 \rangle$ & 45 \\
+		$| n = 0, \ell = 2 \rangle$ & 13 \\
+		$| n = 0, \ell = 3 \rangle$ & 3 \\ 
+		$| n = 1, \ell = 0 \rangle$ & 13 \\
+		$| n = 1, \ell = 1 \rangle$ & 8 \\
+		$| n = 2, \ell = 1 \rangle$ & 3 \\
+		$| n = 2, \ell = 1 \rangle$ & 1 \\ 
+		$| n = 1.3802..., \ell = 1 \rangle$ & 1 \\ 
+		$| n = 1.4655..., \ell = 1 \rangle$ & 1 \\  
+		$| n = 1.6181..., \ell = 2 \rangle$ & 1 \\ 
+		$| n = 1.6181..., \ell = 7 \rangle$ & 1 \\ 
+		\hline
+		\textbf{Total number of building blocks} & 92 \\
+		\hline
+		\textbf{Total number of nodes inside fibers} & 416 \\
+		\hline
+	  \end{tabular}
+	  \caption{tab:fiberstats}
+	  \label{tab:fiberstats}
+\end{table}
 

### 2019-11-08 Code/fibrationf.h

@@ -12,7 +12,6 @@
 #include <string.h>
 #include <math.h>
 ///////////////////
-#include <gsl/gsl_eigen.h>
 #include "utilsforfiber.h"
 #include "structforfiber.h"
 #define SENTINEL -96
@@ -33,23 +32,79 @@ int CHECKLOOP(int root, Graph* graph)
 	} 
 }
 
-
+// The node that has the largest strong connected component.
 int FIBERNODE_FOR_BRANCHING(PART* current_part, Graph* graph)
 {
 	NODELIST* nodelist;
 	NODELIST* regulators;
 	NODELIST* strong_component = NULL;
 
+	int size;
+	int nodeindex = current_part->block->head->data;
+	int max = -1;
+	// Pass through all nodes in fiber.
 	for(nodelist=current_part->block->head; nodelist!=NULL; nodelist=nodelist->next)
 	{
 		KOSAJARU(&strong_component, nodelist->data, graph);
-		for(regulators=current_part->regulators; regulators!=NULL; regulators=regulators->next)
+		size = GetListSize(strong_component);
+		if(size==1)
 		{
-			int verify_reg_in_strong = doublycheck_element(strong_component, regulators->data);
-			if(verify_reg_in_strong==1) return nodelist->data;
+			int check = CHECKLOOP(nodelist->data, graph);
+			if(check==1 && size>max)
+			{
+				nodeindex = nodelist->data;
+				max = size;
+			}
 		}
+		else if(size>max)
+		{
+			nodeindex = nodelist->data;
+			max = size;
+		}
+		deleteList(&strong_component);
 	}
-	return -1;
+	return nodeindex;
+}
+
+extern int OUTPUT_TREE(int root, int wanted, NODELIST* scc, Graph* graph)
+{
+	if(root==wanted) return 0;
+	int i, j;
+	
+	/////////////////////
+	STACK* s1 = NULL;
+	STACK* s2 = NULL;
+	STACK* aux = NULL;
+	STACK* sup = NULL;
+	STACK* depot = NULL;
+	/////////////////////
+	
+	int height = 0;
+	int node_bool = 0;
+	push(&s1, root);
+	sup = s1;
+	depot = s2;
+	while(node_bool==0)
+	{
+		height++;
+		while(sup)
+		{
+			int node = pop(&sup);
+			int n_in = GETNout(graph, node);
[…]

### 2019-11-08 Code/minimalfiber.c

@@ -37,7 +37,7 @@
 #include <string.h>
 #include <math.h>
 // Used fot the calculation of the eigenvalues for each fibration block adjacency matrix.
-#include <gsl/gsl_eigen.h>
+//#include <gsl/gsl_eigen.h>
 // Separated personal constructed modules for graph data and graph fibration specific functions.
 #include "fibrationf.h"
 #include "utilsforfiber.h"
@@ -137,8 +137,8 @@ void main(int argv, char** argc)
 	/* With gene names */ //printGeneGraphInFibers(graph, partition, nodefibers);
 	/* Without gene names */ //printGraphInFibers(graph, partition, nodefibers);
 	
-	/* Classification Info */ ShowClassification(partition, 0);
-	/* Fiber blocks and classification info */ //ShowInfo(partition, 0);
+	/* Classification Info */ //ShowClassification(partition, 0);
+	/* Fiber blocks and classification info */ ShowInfo(partition, 0);
 
 	/*	Show the number of non-trivial fibers	*/
 	//printf("%d %d\n", nontrivial_fibers, total_nodes);

### 2019-11-08 Code/structforfiber.h

@@ -176,7 +176,7 @@ extern void printGraphInFibers(Graph* graph, PART* partition, int* nodefiber)
 	for(current_part=partition; current_part!=NULL; current_part=current_part->next)
 	{
 		if(current_part->block->size==1) continue;
-		printf("INSIDE FIBER %d WITH SIZE %d:\n", current_part->block->index, current_part->block->size);
+		printf("FIBER %d WITH SIZE %d -> | %.4lf, %d >:\n", current_part->block->index, current_part->block->size, current_part->fundamental_number, current_part->number_regulators);
 		for(nodelist=current_part->block->head; nodelist!=NULL; nodelist=nodelist->next)
 		{
 			n = GETNin(graph, nodelist->data);
@@ -199,7 +199,7 @@ extern void printGeneGraphInFibers(Graph* graph, PART* partition, int* nodefiber
 	for(current_part=partition; current_part!=NULL; current_part=current_part->next)
 	{
 		if(current_part->block->size==1) continue;
-		printf("INSIDE FIBER %d WITH SIZE %d:\n", current_part->block->index, current_part->block->size);
+		printf("FIBER %d WITH SIZE %d -> | %.4lf, %d >:\n", current_part->block->index, current_part->block->size, current_part->fundamental_number, current_part->number_regulators);
 		for(nodelist=current_part->block->head; nodelist!=NULL; nodelist=nodelist->next)
 		{
 			printf("NODE %s receives from fiber(node,type): ", graph->array[nodelist->data].gene_name);
@@ -318,4 +318,7 @@ void ShowInfo(PART* partition, int mode)
 		}
 	}
 }
+
+
+
 #endif

### 2019-11-08 Code/utilsforfiber.h

@@ -551,6 +551,29 @@ void freePart(PART** head_ref)
 	}
 }
 
+extern void deleteList(NODELIST** head)
+{
+	NODELIST* ptr = *head; 
+    NODELIST* next; 
+  
+    while (ptr != NULL) { 
+        next = ptr->next; 
+        deleteNode(head, ptr); 
+        ptr = next; 
+    } 
+}
+
+extern int subsetlist(NODELIST* inside, NODELIST* whole)
+{
+	NODELIST* nodelist;
+	for(nodelist=inside; nodelist!=NULL; nodelist=nodelist->next)
+	{
+		int check = doublycheck_element(whole, nodelist->data);
+		if(check==0) return -1;
+	}
+	return 1;
+}
+
 extern void push_block(PART** head, BLOCK* insertion)
 {
     PART* new_node = (PART*)malloc(sizeof(PART));

### 2019-11-08 Manuscript/main.tex
finishing manuscript

@@
 	\subfloat[]{{\includegraphics[scale=0.4]{Figures/ex3.png}}}
-	\caption{First trial network example.
-Containing a total of $N = 17$ nodes and $M = 22$ arcs, the network has two weakly connected components, defined as the connected networks when we treat all the directed arcs as undirected edges.
-For each non-trivial fiber I give the same color for the nodes belonging to it.}
+	\caption{The patterns of directed connections can influence the collective dynamical states of the network nodes through synchronization.
+Considering only the topology, we say that two nodes in a information-processing network synchronize their states if they process equivalent information.
+Since $Y$ and $Z$ receive same information from the same nodes in (a) e (c), they synchronize, different from the case (b), where all nodes have different dynamical states.}
 	\label{fig:ex}
@@
 	\subfloat[]{{\includegraphics[scale=0.32]{Figures/ex3input.png}}}
-	\caption{First trial network example.
-Containing a total of $N = 17$ nodes and $M = 22$ arcs, the network has two weakly connected components, defined as the connected networks when we treat all the directed arcs as undirected edges.
-For each non-trivial fiber I give the same color for the nodes belonging to it.}
+	\caption{Nodes in a network that have isomorphic input-tree share the same dynamical states.
+(a) e (c) shows symmetrical input-tree for nodes $Y$ e $Z$, where due to the addition of the autoregulation loop in (c), their input-trees become infinite.}
 	\label{fig:inputex}
@@
 
-The algorithm \ref{alg:branchratio} assumes that the given node $v$ is part of a strongly connected component, even for the trivial case containing only $v$ connected to itself, because this warrant that $n \neq 0$.
+The algorithm \ref{alg:branchratio} assumes that the given node $v$ is part of a strongly connected component, even for the trivial case containing only $v$ connected to itself, because this warrants that $n \neq 0$.
 This can be easily verified implementing a Depth-First Search or Breadth-First Search on the network and its tranpose starting at node $v$ to find its strongly connected component, which takes linear time with the size of the strongly connected component.
@@
 	\includegraphics[scale=0.32]{Figures/input.png}
+	\caption{Example of fibration building block containing more than one cycle.
+Building the fiber input-tree with all the three nodes from the strongly connected component gives a wrong branching ratio $n$, while considering only the nodes in the shortest cycle gives the right branching ratio $\varphi_2$.}
+	\label{fig:branch}
 \end{figure}
@@
       4 & $| 0, 1 \rangle$ \\
-      5 & $| 0, 2 \rangle$ \\ \hline
+      5 & $| 1, 2 \rangle$ \\ \hline
 	\end{tabular}
@@
 
-%\begin{figure}[H]
-%	\centering
-%	\subfloat[]{{\includegraphics[scale=0.25]{Figures/result2.png}}}
-%	\qquad
-%	\subfloat[]{{\includegraphics[scale=0.25]{Figures/result2-label.png}}}
-%	\caption{First trial network example.
-Containing a total of $N = 17$ nodes and $M = 22$ arcs, the network has two weakly connected %components, defined as the connected networks when we treat all the directed arcs as undirected edges.
-For each non-trivial fiber I %give the same color for the nodes belonging to it.}
-%	\label{fig:result2}
-%\end{figure}
+Before applying the algorithm for the whole \textit{Escherichia Coli} network, I chose, for the finality of visualization and testing, to apply first the algorithm for a weakly connected component of the \textit{E.
+Coli} network.
+The same network is showed at the supplementary information of \cite{fibration2019}.
+The fiber distribution found is consistent with the one presented at \cite{fibration2019}, presenting the total of fifteen non-trivial fiber groups as shown in the figure \ref{fig:result3-1}.
 
@@
 \end{figure}
-
 \begin{figure}[H]
@@
 	Fiber & $| n, \ell \rangle$  \\ \hline
-	1 & $| 0, 1 \rangle$ \\
-	2 & $| 0, 1 \rangle$ \\
-	3 & $| 0, 1 \rangle$ \\ 
+	1 & $| 1.6181..., 1 \rangle$ \\
+	2 & $| 1, 0 \rangle$ \\
+	3 & $| 1.6181..., 2 \rangle$ \\ 
 	4 & $| 0, 1 \rangle$ \\
-	5 & $| 0, 2 \rangle$ \\
-	6 & $| 0, 2 \rangle$ \\ \hline
+	5 & $| 0, 1 \rangle$ \\
+	6 & $| 0, 1 \rangle$ \\ \hline
   \end{tabular}
@@
 
-Before applying the algorithm for the whole \textit{Escherichia Coli} network, I chose, for the finality of visualization and testing, to apply first the algorithm for a weakly connected component of the \textit{E.
-Coli} network.
-The same network is showed at the supplementary information of \cite{fibration2019}.
-The fiber distribution found is consistent with the one presented at \cite{fibration2019}, presenting the total of fifteen non-trivial fiber groups as shown in the figure \ref{fig:result3-1}.
+The connected component showed at the figure \ref{fig:result3} is a subset representation of the nodes of the regulatory network of the \textit{Escherichia Coli} bacteria and the resulted fibers shows just a portion of the whole fibers pattern.
+In the table X I provide the classification for each fibration building block obtained for the whole bacteria network, including, of course, the fibers presented in the figure \ref{fig:result3-1}.
+In total, I have found $92$ non-trivial fiber groups containing a total of $416$ nodes, obtaining a characteristic fiber statistics for the \textit{Escherichia Coli} network data.
+To guarantee the correctness of the fiber distribution found I calculated, after the refinement algorithm, the information received for each node inside the fibers and compares if each one process equivalent information.
+The result of this calculation is stored in the data file given at \url{https://github.com/higorsmonteiro/fiberblocks/blob/master/Data/Results/DefinitiveFiber.dat}, where for each node in a non-trivial fiber block I give the list of the nodes that sends information messages to the current node along with their fiber indexes and type of link values.
+Thus, the results of this report show an equivalent fiber distribution over the network comparing with results exhibited at \cite{fibration2019} for the same regulatory network data.
+Even though the table IV an V of \cite{fibration2019} show a total number of $91$ fibers and the total number of $414$ of nodes inside non-trivial fibers, the authors \href{https://docs.google.com/spreadsheets/d/1-RG5vR_EGNPqQcnJU8q3ky1OpWi3OjTh5Uo-Xa0PjOc/edit#gid=1973910256}{spreadsheet} reports the total of $416$ nodes, a mismatch which is caused in this report by the presence of a additional fiber of size two, classified as $| 1.6181..., 7 \rangle$ containing the genes \textit{marR} e \textit{marA}.
+This way, the number of nodes in fibers and the genes inside each one are consistent with the results showed in \cite{fibration2019}.
 
@@
 	\centering
-	\includegraphics[scale=0.27]{Figures/result3.png}
+	\includegraphics[scale=0.23]{Figures/result3.png}
 	\caption{}
@@
 	\centering
-	\includegraphics[scale=0.27]{Figures/result3-1.png}
+	\includegraphics[scale=0.23]{Figures/result3-1.png}
 	\caption{}
@@
 \end{figure}
-
-The connected component showed at the figure \ref{fig:result3} is a subset representation of the nodes of the regulatory network of the \textit{Escherichia Coli} bacteria and the resulted fibers shows just a portion of the whole fibers pattern.
-In the table X I provide the classification for each fibration building block obtained for the whole bacteria network, including, of course, the fibers presented in the figure \ref{fig:result3-1}.
-In total, I have found $92$ non-trivial fiber groups containing a total of $416$ nodes, obtaining a characteristic fiber statistics for the \textit{Escherichia Coli} network data.
-To guarantee the correctness of the fiber distribution found I calculated, after the refinement algorithm, the information received for each node inside the fibers and compares if each one process equivalent information.
-The result of this calculation is stored in the data file given at \url{https://github.com/higorsmonteiro/fiberblocks/blob/master/Data/fiberVerification.dat}, where for each node in a non-trivial fiber block I give the list of the nodes that sends information messages to the current node along with their fiber indexes and type of link values.
-Thus, the results of this report show an equivalent fiber distribution over the network comparing with results exhibited at \cite{fibration2019} for the same regulatory network data.
-Even though the table IV an V of \cite{fibration2019} show a total number of $91$ fibers and the total number of $414$ of nodes inside non-trivial fibers, the authors \href{https://docs.google.com/spreadsheets/d/1-RG5vR_EGNPqQcnJU8q3ky1OpWi3OjTh5Uo-Xa0PjOc/edit#gid=1973910256}{spreadsheet} reports the total of $416$ nodes, a mismatch which is caused in this report by the presence of a additional fiber of size two and classified as $| 1.6181..., 7 \rangle$ containing the genes \textit{marR} e \textit{marA}.
-This way, the number of nodes in fibers and the genes inside each one are consistent with the results showed in \cite{fibration2019}.
 
@@
 	  \end{tabular}
-	  \caption{tab:fiberstats}
+	  \caption{Fibration building blocks statistics of the \textit{Escherechia Coli} genetic regulatory network. The indexation accounts for trivial fibers also.}
 	  \label{tab:fiberstats}
+\end{table}
+
+\centering
+\begin{table}[b]
+	\centering
+\begin{tabular}{r|r|r|r}
+\hline
+Fiber ID &  Fiber Size &  $n$ or $\varphi_d$ &  $\ell$ \\ \hline
+4 &          12 &             0.0000 &          1 \\        5 &           9 &             1.4655 &          1 \\       10 &           2 &             0.0000 &          1 \\       11 &           2 &             0.0000 &          1 \\       12 &           2 &             0.0000 &          1 \\       13 &           4 &             0.0000 &          1 \\       15 &           2 &             0.0000 &          2 \\       19 &           2 &             0.0000 &          1 \\       20 &           7 &             0.0000 &          1 \\       21 &           2 &             0.0000 &          1 \\       23 &           2 &             1.3802 &          1 \\       25 &           6 &             0.0000 &          1 \\       26 &           2 &             0.0000 &          1 \\       29 &           4 &             0.0000 &          1 \\       30 &           9 &             0.0000 &          1 \\       35 &           2 &             0.0000 &          1 \\       41 &           4 &             0.0000 &          1 \\       43 &          24 &             0.0000 &          1 \\       46 &          11 &             0.0000 &          1 \\       48 &           7 &             0.0000 &          1 \\       49 &           3 &             0.0000 &          1 \\       53 &           2 &             0.0000 &          1 \\       54 &           5 &             0.0000 &          1 \\       55 &           4 &             0.0000 &          1 \\       56 &           3 &             0.0000 &          1 \\       58 &           2 &             0.0000 &          2 \\       66 &           4 &             0.0000 &          2 \\       67 &          13 &             0.0000 &          1 \\       70 &           2 &             0.0000 &          1 \\       71 &          28 &             0.0000 &          1 \\       73 &           4 &             0.0000 &          3 \\       74 &           3 &             0.0000 &          2 \\       75 &           4 &             0.0000 &          1 \\       78 &           4 &             1.0000 &          1 \\       80 &           3 &             0.0000 &          2 \\       83 &           2 &             1.0000 &          1 \\       84 &           2 &             1.6181 &          2 \\       92 &           4 &             0.0000 &          1 \\
+\end{tabular}
+\end{table}
+
+\begin{table}[b]
+	\centering
+	\begin{tabular}{r|r|r|r}
+
+		Fiber ID &  Fiber Size &  $n$ or $\varphi_d$ &  $\ell$ \\ \hline
+		110 &           2 &             0.0000 &          2 \\      114 &           2 &             0.0000 &          2 \\      117 &           2 &             0.0000 &          2 \\      120 &           2 &             0.0000 &          2 \\      128 &           2 &             0.0000 &          3 \\      132 &           3 &             0.0000 &          1 \\      135 &           5 &             0.0000 &          3 \\      137 &           2 &             2.0000 &          1 \\      145 &           2 &             1.0000 &          1 \\      153 &           4 &             1.0000 &          1 \\      181 &           2 &             0.0000 &          1 \\      187 &           8 &             0.0000 &          1 \\      198 &           2 &             1.0000 &          1 \\      208 &           2 &             1.0000 &          2 \\      225 &           2 &             0.0000 &          2 \\      246 &           2 &             1.0000 &          1 \\      249 &           3 &             1.0000 &          1 \\      257 &           3 &             1.0000 &          0 \\      269 &           2 &             0.0000 &          2 \\      277 &           2 &             2.0000 &          0 \\      278 &           9 &             0.0000 &          1 \\      281 &          11 &             1.0000 &          0 \\      284 &           3 &             0.0000 &          1 \\      299 &          26 &             1.0000 &          0 \\      305 &           3 &             1.0000 &          0 \\      311 &           2 &             0.0000 &          2 \\      312 &           5 &             1.0000 &          0 \\      313 &           2 &             1.0000 &          1 \\      319 &           5 &             0.0000 &          1 \\      322 &          16 &             1.0000 &          0 \\      324 &           3 &             1.0000 &          0 \\      330 &           9 &             1.0000 &          0 \\      331 &           2 &             1.0000 &          0 \\      342 &           3 &             0.0000 &          1 \\      350 &           3 &             0.0000 &          1 \\      353 &           2 &             0.0000 &          1 \\      356 &           2 &             0.0000 &          1 \\
+	\end{tabular}
+\end{table}
+
+\begin{table}[b]
+	\centering
+	\begin{tabular}{r|r|r|r}
+
+		Fiber ID &  Fiber Size &  $n$ or $\varphi_d$ &  $\ell$ \\ \hline
+				 359 &           2 &             0.0000 &          1 \\      364 &           5 &             0.0000 &          1 \\      373 &          12 &             0.0000 &          1 \\      380 &           2 &             0.0000 &          1 \\      395 &           2 &             0.0000 &          1 \\      433 &           3 &             1.0000 &          2 \\      434 &           2 &             1.0000 &          2 \\      440 &           2 &             0.0000 &          2 \\      449 &           2 &             0.0000 &          1 \\      476 &           2 &             1.6181 &          7 \\      481 &           3 &             0.0000 &          1 \\      495 &           2 &             1.0000 &          0 \\      497 &           2 &             1.0000 &          0 \\      498 &           2 &             1.0000 &          0 \\      500 &           2 &             0.0000 &          1 \\      503 &           2 &             0.0000 &          1 \\      505 &           2 &             1.0000 &          0 \\
+				 \hline
+	\end{tabular}
+	\caption{Size and classification of all non-trivial fibers over the \textit{Escherichia Coli} genetic regulatory network.}
 \end{table}

### 2019-11-08 Code/fibrationf.h

@@ -183,7 +183,7 @@ extern double BRANCH_RATIO(PART* block_info, Graph* graph, double delta)
 				cyclesize = height1+height2;
 			}
 		}
-		printf("%d\n", cyclesize);
+		//printf("%d\n", cyclesize);
 		
 		switch(cyclesize)
 		{

### 2019-11-08 Code/minimalfiber.c

@@ -137,7 +137,7 @@ void main(int argv, char** argc)
 	/* With gene names */ //printGeneGraphInFibers(graph, partition, nodefibers);
 	/* Without gene names */ //printGraphInFibers(graph, partition, nodefibers);
 	
-	/* Classification Info */ //ShowClassification(partition, 0);
+	/* Classification Info */ //ShowClassification1(partition, 0);
 	/* Fiber blocks and classification info */ ShowInfo(partition, 0);
 
 	/*	Show the number of non-trivial fibers	*/

### 2019-11-08 Code/structforfiber.h

@@ -301,6 +301,23 @@ void ShowClassification(PART* partition, int mode)
 	}
 }
 
+void ShowClassification1(PART* partition, int mode)
+{
+	PART* current_part;
+	for(current_part=partition; current_part!=NULL; current_part=current_part->next)
+	{
+		if(current_part->block->size>1)
+		{
+			printf("%d,%d,%lf,%d\n", current_part->block->index, current_part->block->size, current_part->fundamental_number, current_part->number_regulators);
+			//printBlock(current_part->block);
+		}
+		else if(mode==1)
+		{
+			printf("Fiber %d: Size %d - n %lf - l %d\n", current_part->block->index, current_part->block->size, current_part->fundamental_number, current_part->number_regulators);
+		}
+	}
+}
+
 void ShowInfo(PART* partition, int mode)
 {
 	PART* current_part;

### 2019-11-10 Code/fibrationf.h
last modifications

@@ -3,8 +3,9 @@
 
 /*  
     The code here represents the central module for the implementation of the coarsest
-    refinement graph partitioning algorithm, containing the functions used in the main
-    code. The necessary comments are given at the beginning of each function (to do).
+    refinement graph partitioning algorithm for input-tree stability, containing the 
+    functions used in the main code. The necessary comments are given at the beginning of 
+    each function (to do).
  */
 
 #include <stdio.h>
@@ -16,7 +17,15 @@
 #include "structforfiber.h"
 #define SENTINEL -96
 
-int CHECKLOOP(int root, Graph* graph)
+/////////////////////////////////////////////////////////////////////////
+/////////////////////// FIBRATION CLASSIFICATION ////////////////////////
+/////////////////////////////////////////////////////////////////////////
+
+
+//########## BRANCHING RATIO DETERMINATION ############//
+
+/*	Verify if the input-tree of 'root' is infinite (1) or not (0).	*/
+extern int INFINITE_INTREE(int root, Graph* graph)
 {
 	int i;
 	NODELIST* scc_nodes = NULL;
@@ -32,74 +41,86 @@ int CHECKLOOP(int root, Graph* graph)
 	} 
 }
 
-// The node that has the largest strong connected component.
-int FIBERNODE_FOR_BRANCHING(PART* current_part, Graph* graph)
+/*	Given a fiber V_i, the function returns the node that belongs to V_i that
+	should be used for the branching ratio determination.	*/
+extern int FIBERNODE_FOR_BRANCHING(PART* fiber, Graph* graph)
 {
 	NODELIST* nodelist;
 	NODELIST* regulators;
 	NODELIST* strong_component = NULL;
 
-	int size;
-	int nodeindex = current_part->block->head->data;
 	int max = -1;
-	// Pass through all nodes in fiber.
-	for(nodelist=current_part->block->head; nodelist!=NULL; nodelist=nodelist->next)
+	int verf, size;
+	int fibernode = fiber->block->head->data;
+
+	/*	For each node in fiber, defines its strongly connected component(SCC)
[…]

### 2019-11-10 Code/main.c

@@ -28,7 +28,7 @@
 
 	Author: Higor da S. Monteiro
 	Email: higor.monteiro@fisica.ufc.br
-	Complex System Lab (Prof. José Soares de Andrade Jr.)
+	Complex System Lab (Prof. J. S. de Andrade Jr.)
 	Departament of Physics/Universidade Federal do Ceará (UFC) - Fortaleza, Ceará.
 */
 
@@ -71,7 +71,6 @@ void main(int argv, char** argc)
 	///////////////////////////////////////////////////////////////////////////////////////
 
 	/////////////////////// COARSEST REFINEMENT PARTITIONING ALGORITHM ////////////////////////
-	int i, j, k;
 	
 	// Define the initial partition as one block containing all operating nodes. 
 	PART* partition = NULL;    
@@ -114,12 +113,13 @@ void main(int argv, char** argc)
 	CALCULATE_REGULATORS(&partition, graph);
 	CALCULATE_REGULATORS(&null_partition, graph);
 	// Calculates branch ratio number for each fiber block.
-	DEF_FUNDAMENTAL(&partition, graph);
+	CALC_BRANCHING(&partition, graph);
 	//DEF_BRANCH_RATIO(&partition, graph);
 	//////////////////////////////////////////////////////////////////////////////////////////
 	//////////////////////////////////////////////////////////////////////
 	
 	////// 'nodefibers' directly relates nodes with their fiber index ///////
+	int i, j, k;
 	NODELIST* nodelist;	
 	int total_nodes = 0;	// Number of nodes inside non-trivial fibers.
 	int* nodefibers = (int*)malloc(N*sizeof(int));
@@ -138,16 +138,15 @@ void main(int argv, char** argc)
 	/* Without gene names */ //printGraphInFibers(graph, partition, nodefibers);
 	
 	/* Classification Info */ //ShowClassification1(partition, 0);
-	/* Fiber blocks and classification info */ ShowInfo(partition, 0);
+	/* Fiber blocks and classification info */ //ShowInfo(partition, 0);
 
 	/*	Show the number of non-trivial fibers	*/
 	//printf("%d %d\n", nontrivial_fibers, total_nodes);
 	
-	//int node = atoi(argc[3]);
-	//PrintInNeighbors(graph, node);
-	//PrintOutNeighbors(graph, node);
-	//int n = GETNin(graph, node);
-
+	int node = atoi(argc[3]);
+	PrintInNeighbors(graph, node);
[…]

### 2019-11-10 Code/structforfiber.h

@@ -130,7 +130,7 @@ STORETYPE* GETIN_ADJTYPE(Graph* graph, int node)
 extern void PrintInNeighbors(Graph* graph, int node)
 {
 	NodeAdj* Inode = graph->array[node].head_in;
-	printf("Node %d: ", node);
+	printf("Node %d receives from: ", node);
 	while(Inode)
 	{
 		printf("%d(type:%d) ", Inode->neighbor, Inode->type_link);
@@ -142,7 +142,7 @@ extern void PrintInNeighbors(Graph* graph, int node)
 extern void PrintOutNeighbors(Graph* graph, int node)
 {
 	NodeAdj* Inode = graph->array[node].head_out;
-	printf("Node %d: ", node);
+	printf("Node %d points to: ", node);
 	while(Inode)
 	{
 		printf("%d ", Inode->neighbor);
